### 2018-07-06 article.tex
Results.

\documentclass[pmlr]{jmlr}
\input{_head}
%TODO: Max 14 pages
%TODO: No personal information or reference to the authors should be introduced in the submitted paper.
%TODO: Submissions will be evaluated concerning their technical quality, relevance, significance, originality and clarity.

\title
[Short Title]
{
	The undersampling ensemble approach to highly imbalanced data classification%\titlebreak
}

\begin{document}

\maketitle

\begin{abstract}
This is the abstract for this article.
\end{abstract}
\begin{keywords}
classification, classifier ensemble, undersampling, imbalanced data
\end{keywords}

%%%
%%% Introduction
%%%
\section{Introduction}
\label{sec:intro}

This is a sample article that uses the \textsf{jmlr} class with
the \texttt{wcp} class option.  Please follow the guidelines in
this sample document as it can help to reduce complications when
combining the articles into a book. Please avoid using obsolete
commands, such as \verb|\rm|, and obsolete packages, such as
\textsf{epsfig}.\footnote{See
\url{http://www.ctan.org/pkg/l2tabu}}

Please also ensure that your document will compile with PDF\LaTeX.
If you have an error message that's puzzling you, first check for it
at the UK TUG FAQ
\url{http://www.tex.ac.uk/cgi-bin/texfaq2html?label=man-latex}.  If
that doesn't help, create a minimal working example (see
\url{http://theoval.cmp.uea.ac.uk/~nlct/latex/minexample/}) and post
to somewhere like TeX on StackExchange
(\url{http://tex.stackexchange.com/}) or the LaTeX Community Forum
(\url{http://www.latex-community.org/forum/}).

\begin{note}
This is an numbered theorem-like environment that was defined in
this document's preamble.
\end{note}

\subsection{Sub-sections}

Sub-sections are produced using \verb|\subsection|.

\subsubsection{Sub-sub-sections}

Sub-sub-sections are produced using \verb|\subsubsection|.

\paragraph{Sub-sub-sub-sections}

Sub-sub-sub-sections are produced using \verb|\paragraph|.
These are unnumbered with a running head.

\subparagraph{Sub-sub-sub-sub-sections}

Sub-sub-sub-sub-sections are produced using \verb|\subparagraph|.
These are unnumbered with a running head.

\section{Cross-Referencing}

Always use \verb|\label| and \verb|\ref| (or one of the commands
described below) when cross-referencing.  For example, the next
section is Section~\ref{sec:math}. The \textsf{jmlr} class
provides some convenient cross-referencing commands:
\verb|\sectionref|, \verb|\equationref|, \verb|\tableref|,
\verb|\figureref|, \verb|\algorithmref|, \verb|\theoremref|,
\verb|\lemmaref|, \verb|\remarkref|, \verb|\corollaryref|,
\verb|\definitionref|, \verb|\conjectureref|, \verb|\axiomref|,
\verb|\exampleref| and \verb|\appendixref|. The argument of these
commands may either be a single label or a comma-separated list
of labels. Examples:

Referencing sections: \sectionref{sec:math} or
\sectionref{sec:intro,sec:math} or
\sectionref{sec:intro,sec:math,sec:tables,sec:figures}.

Referencing equations: \equationref{eq:trigrule} or
\equationref{eq:trigrule,eq:df} or
\equationref{eq:trigrule,eq:f,eq:df,eq:y}.

Referencing tables: \tableref{tab:operatornames} or
\tableref{tab:operatornames,tab:example} or
\tableref{tab:operatornames,tab:example,tab:example-booktabs}.

Referencing figures: \figureref{fig:nodes} or
\figureref{fig:nodes,fig:teximage} or
\figureref{fig:nodes,fig:teximage,fig:subfigex} or
\figureref{fig:circle,fig:square}.

Referencing algorithms: \algorithmref{alg:gauss} or
\algorithmref{alg:gauss,alg:moore} or
\algorithmref{alg:gauss,alg:moore,alg:net}.

Referencing theorem-like environments: \theoremref{thm:eigenpow},
\lemmaref{lem:sample}, \remarkref{rem:sample}, 
\corollaryref{cor:sample}, \definitionref{def:sample},
\conjectureref{con:sample}, \axiomref{ax:sample} and
\exampleref{ex:sample}.

Referencing appendices: \appendixref{apd:first} or
\appendixref{apd:first,apd:second}.

\section{Equations}
\label{sec:math}

The \textsf{jmlr} class loads the \textsf{amsmath} package, so
you can use any of the commands and environments defined there.
(See the \textsf{amsmath} documentation for further
details.\footnote{Either \texttt{texdoc amsmath} or
\url{http://www.ctan.org/pkg/amsmath}})

Unnumbered single-lined equations should be displayed using
\verb|\[| and \verb|\]|. For example:
\[E = m c^2\]
Numbered single-line equations should be displayed using the
\texttt{equation} environment. For example:
\begin{equation}\label{eq:trigrule}
\cos^2\theta + \sin^2\theta \equiv 1
\end{equation}
This can be referenced using \verb|\label| and \verb|\equationref|.
For example, \equationref{eq:trigrule}.

Multi-lined numbered equations should be displayed using the
\texttt{align} environment.\footnote{For reasons why you 
shouldn't use the obsolete \texttt{eqnarray} environment, see
Lars Madsen, \emph{Avoid eqnarray!} TUGboat 33(1):21--25, 2012.} For example:
\begin{align}
f(x) &= x^2 + x\label{eq:f}\\
f'(x) &= 2x + 1\label{eq:df}
\end{align}
Unnumbered multi-lined equations should be displayed using the
\texttt{align*} environment. For example:
\begin{align*}
f(x) &= (x+1)(x-1)\\
&= x^2 - 1
\end{align*}
If you want to mix numbered with unnumbered lines use the
align environment and suppress unwanted line numbers with
\verb|\nonumber|. For example:
\begin{align}
y &= x^2 + 3x - 2x + 1\nonumber\\
&= x^2 + x + 1\label{eq:y}
\end{align}
An equation that is too long to fit on a single line can be
displayed using the \texttt{split} environment. 
Text can be embedded in an equation using \verb|\text| or
\verb|\intertext| (as used in \theoremref{thm:eigenpow}).
See the \textsf{amsmath} documentation for further details.

\subsection{Operator Names}
\label{sec:op}

Predefined operator names are listed in \tableref{tab:operatornames}.
For additional operators, either use \verb|\operatorname|,
for example $\operatorname{var}(X)$ or declare it with
\verb|\DeclareMathOperator|, for example
\begin{verbatim}
\DeclareMathOperator{\var}{var}
\end{verbatim}
and then use this new command. If you want limits that go above and
below the operator (like \verb|\sum|) use the starred versions
(\verb|\operatorname*| or \verb|\DeclareMathOperator*|).

\begin{table}[htbp]
\floatconts
  {tab:operatornames}%
  {\caption{Predefined Operator Names (taken from 
   \textsf{amsmath} documentation)}}%
  {%
\begin{tabular}{rlrlrlrl}
\cs{arccos} & $\arccos$ &  \cs{deg} & $\deg$ &  \cs{lg} & $\lg$ &  \cs{projlim} & $\projlim$ \\
\cs{arcsin} & $\arcsin$ &  \cs{det} & $\det$ &  \cs{lim} & $\lim$ &  \cs{sec} & $\sec$ \\
\cs{arctan} & $\arctan$ &  \cs{dim} & $\dim$ &  \cs{liminf} & $\liminf$ &  \cs{sin} & $\sin$ \\
\cs{arg} & $\arg$ &  \cs{exp} & $\exp$ &  \cs{limsup} & $\limsup$ &  \cs{sinh} & $\sinh$ \\
\cs{cos} & $\cos$ &  \cs{gcd} & $\gcd$ &  \cs{ln} & $\ln$ &  \cs{sup} & $\sup$ \\
\cs{cosh} & $\cosh$ &  \cs{hom} & $\hom$ &  \cs{log} & $\log$ &  \cs{tan} & $\tan$ \\
\cs{cot} & $\cot$ &  \cs{inf} & $\inf$ &  \cs{max} & $\max$ &  \cs{tanh} & $\tanh$ \\
\cs{coth} & $\coth$ &  \cs{injlim} & $\injlim$ &  \cs{min} & $\min$ \\
\cs{csc} & $\csc$ &  \cs{ker} & $\ker$ &  \cs{Pr} & $\Pr$
\end{tabular}\par
\begin{tabular}{rlrl}
\cs{varlimsup} & $\varlimsup$ 
& \cs{varinjlim} & $\varinjlim$\\
\cs{varliminf} & $\varliminf$ 
& \cs{varprojlim} & $\varprojlim$
\end{tabular}
}
\end{table}

\section{Vectors and Sets}
\label{sec:vec}

Vectors should be typeset using \cs{vec}. For example $\vec{x}$.
The \textsf{jmlr} class also provides \cs{set} to typeset a
set. For example $\set{S}$.

\section{Floats}
\label{sec:floats}

Floats, such as figures, tables and algorithms, are moving
objects and are supposed to float to the nearest convenient
location. Please don't force them to go in a particular place. In
general it's best to use the \texttt{htbp} specifier and don't
put the figure or table in the middle of a paragraph (that is
make sure there's a paragraph break above and below the float).
Floats are supposed to have a little extra space above and below
them to make them stand out from the rest of the text. This extra
spacing is put in automatically and shouldn't need modifying.

To ensure consistency, please \emph{don't} try changing the format of the caption by doing
something like:
\begin{verbatim}
\caption{\textit{A Sample Caption.}}
\end{verbatim}
or
\begin{verbatim}
\caption{\em A Sample Caption.}
\end{verbatim}
You can, of course, change the font for individual words or 
phrases, for example:
\begin{verbatim}
\caption{A Sample Caption With Some \emph{Emphasized Words}.}
\end{verbatim}

\subsection{Tables}
\label{sec:tables}

Tables should go in the \texttt{table} environment. Within this
environment use \verb|\floatconts| (defined by \textsf{jmlr})
to set the caption correctly and center the table contents.

\begin{table}[htbp]
 % The first argument is the label.
 % The caption goes in the second argument, and the table contents
 % go in the third argument.
\floatconts
  {tab:example}%
  {\caption{An Example Table}}%
  {\begin{tabular}{ll}
  \bfseries Dataset & \bfseries Result\\
  Data1 & 0.12345\\
  Data2 & 0.67890\\
  Data3 & 0.54321\\
  Data4 & 0.09876
  \end{tabular}}
\end{table}

If you want horizontal rules you can use the \textsf{booktabs}
package which provides the commands \verb|\toprule|, 
\verb|\midrule| and \verb|\bottomrule|. For example, see
\tableref{tab:example-booktabs}.

\begin{table}[hbtp]
\floatconts
  {tab:example-booktabs}
  {\caption{A Table With Horizontal Lines}}
  {\begin{tabular}{ll}
  \toprule
  \bfseries Dataset & \bfseries Result\\
  \midrule
  Data1 & 0.12345\\
  Data2 & 0.67890\\
  Data3 & 0.54321\\
  Data4 & 0.09876\\
  \bottomrule
  \end{tabular}}
\end{table}

If you want vertical lines as well, you can't use the
\textsf{booktabs} commands as there'll be some unwanted gaps.
Instead you can use \LaTeX's \verb|\hline|, but the rows may
appear a bit cramped.  You can add extra space above or below a
row using \verb|\abovestrut| and \verb|\belowstrut|. For example,
see \tableref{tab:example-hline}.

\begin{table}[htbp]
\floatconts
  {tab:example-hline}
  {\caption{A Table With Horizontal and Vertical Lines}}%
  {%
    \begin{tabular}{|l|l|}
    \hline
    \abovestrut{2.2ex}\bfseries Dataset & \bfseries Result\\\hline
    \abovestrut{2.2ex}Data1 & 0.12345\\
    Data2 & 0.67890\\
    Data3 & 0.54321\\
    \belowstrut{0.2ex}Data4 & 0.09876\\\hline
    \end{tabular}
  }
\end{table}

If you want to align numbers on their decimal point, you can
use the \textsf{siunitx} package. For example, see
\tableref{tab:example-siunitx}. For further details see the
\textsf{siunitx} documentation\footnote{Either \texttt{texdoc
siunitx} or \url{http://www.ctan.org/pkg/siunitx}}.

\begin{table}[htbp]
\floatconts
  {tab:example-siunitx}
  {\caption{A Table With Numbers Aligned on the Decimal Point}}
  {\begin{tabular}{lS[tabformat=3.5]}
  \bfseries Dataset & {\bfseries Result}\\
  Data1 & 0.12345\\
  Data2 & 10.6789\\
  Data3 & 50.543\\
  Data4 & 200.09876
  \end{tabular}}
\end{table}

If the table is too wide, you can adjust the inter-column
spacing by changing the value of \verb|\tabcolsep|. For
example:
\begin{verbatim}
\setlength{\tabcolsep}{3pt}
\end{verbatim}
If the table is very wide but not very long, you can use the
\texttt{sidewaystable} environment defined in the
\textsf{rotating} package (so use \verb|\usepackage{rotating}|).
If the table is too long to fit on a page, you should use the
\texttt{longtable} environment defined in the \textsf{longtable}
package (so use \verb|\usepackage{longtable}|).

\subsection{Figures}
\label{sec:figures}

Figures should go in the \texttt{figure} environment. Within this
environment, use \verb|\floatconts| to correctly position the
caption and center the image. Use \verb|\includegraphics|
for external graphics files but omit the file extension. Do not
use \verb|\epsfig| or \verb|\psfig|. If you want to scale the
image, it's better to use a fraction of the line width rather
than an explicit length. For example, see \figureref{fig:nodes}.

\begin{figure}[htbp]
 % Caption and label go in the first argument and the figure contents
 % go in the second argument
\floatconts
  {fig:nodes}
  {\caption{Example Image}}
  {\includegraphics[width=0.5\linewidth]{images/nodes}}
\end{figure}

If your image is made up of \LaTeX\ code (for example, commands
provided by the \textsf{pgf} package) you can include it using
\cs{includeteximage} (defined by the \textsf{jmlr} class). This
can be scaled and rotated in the same way as \cs{includegraphics}.
For example, see \figureref{fig:teximage}.

\begin{figure}[htbp]
\floatconts
  {fig:teximage}
  {\caption{Image Created Using \LaTeX\ Code}}
  {\includeteximage[angle=45]{images/teximage}}
\end{figure}

If the figure is too wide to fit on the page, you can use the
\texttt{sidewaysfigure} environment defined in the
\textsf{rotating} package.

Don't use \verb|\graphicspath|. If the images are contained in
a subdirectory, specify this when you include the image, for
example \verb|\includegraphics{figures/mypic}|.

\subsubsection{Sub-Figures}
\label{sec:subfigures}

\begin{sidewaystable}
\scriptsize
\centering
\setlength{\tabcolsep}{3.5pt}
\def\arraystretch{1.15}
\begin{tabular}{@{}|ccccc|ccccc||ccccc|ccccc||ccc|r|}\hline%

\multicolumn{10}{|c||}{\multirow{2}{*}{\bfseries Without oversampled set}} &
\multicolumn{10}{ c||}{\multirow{2}{*}{\bfseries With oversampled set}} &
\multirow{5}{*}{\rotatebox[origin=c]{-90}{\bfseries OS}} &
\multirow{5}{*}{\rotatebox[origin=c]{-90}{\bfseries US}} &
\multirow{5}{*}{\rotatebox[origin=c]{-90}{\bfseries Full}} &
\multirow{5}{*}{\rotatebox[origin=c]{-90}{\bfseries Dataset}}

\\
\multicolumn{10}{|c||}{}&
\multicolumn{10}{c||}{}&
\multicolumn{3}{c|}{}&

	 \\

	\multicolumn{5}{|c|}{\bfseries All members} &
	\multicolumn{5}{c||}{\bfseries Reduced members} &
	\multicolumn{5}{c|}{\bfseries All members} &
	\multicolumn{5}{c||}{\bfseries Reduced members} 
	& & & & \\

	\multirow{2}{*}{\rotatebox[origin=c]{-90}{\textsc{reg}}} &
	\multirow{2}{*}{\rotatebox[origin=c]{-90}{\textsc{wei}}} &
	\multirow{2}{*}{\rotatebox[origin=c]{-90}{\textsc{con}}} &
	\multirow{2}{*}{\rotatebox[origin=c]{-90}{\textsc{nor}}} &
	\multirow{2}{*}{\rotatebox[origin=c]{-90}{\textsc{nc}}} &

	\multirow{2}{*}{\rotatebox[origin=c]{-90}{\textsc{reg}}} &
	\multirow{2}{*}{\rotatebox[origin=c]{-90}{\textsc{wei}}} &
	\multirow{2}{*}{\rotatebox[origin=c]{-90}{\textsc{con}}} &
	\multirow{2}{*}{\rotatebox[origin=c]{-90}{\textsc{nor}}} &
	\multirow{2}{*}{\rotatebox[origin=c]{-90}{\textsc{nc}}} &

	\multirow{2}{*}{\rotatebox[origin=c]{-90}{\textsc{reg}}} &
	\multirow{2}{*}{\rotatebox[origin=c]{-90}{\textsc{wei}}} &
	\multirow{2}{*}{\rotatebox[origin=c]{-90}{\textsc{con}}} &
	\multirow{2}{*}{\rotatebox[origin=c]{-90}{\textsc{nor}}} &
	\multirow{2}{*}{\rotatebox[origin=c]{-90}{\textsc{nc}}} &

	\multirow{2}{*}{\rotatebox[origin=c]{-90}{\textsc{reg}}} &
	\multirow{2}{*}{\rotatebox[origin=c]{-90}{\textsc{wei}}} &
	\multirow{2}{*}{\rotatebox[origin=c]{-90}{\textsc{con}}} &
	\multirow{2}{*}{\rotatebox[origin=c]{-90}{\textsc{nor}}} &
	\multirow{2}{*}{\rotatebox[origin=c]{-90}{\textsc{nc}}}

	& & & &

	\\

	&&&&&&&&&&&&&&&&&&&&&&&
	\\\hline\hline

	\csvreader[head to column names,
	           late after line=\csvifoddrow{\\}{\\\rowcolor{gray!10!white}},
	           late after last line = \\\hline]
	{results/GNB.csv}{}%
	{

	\ereg & \ewei & \ecwei & \enwei & \encwei &
	\eregr & \eweir & \ecweir & \enweir & \encweir &
	\eregos & \eweios & \ecweios & \enweios & \encweios & 
	\eregros & \eweiros & \ecweiros & \enweiros & \encweiros &
	\os & \us & \reg &

	\multicolumn{1}{l|}{\emph{\dataset}}

	}%
\end{tabular}
\caption{Balanced accuracy scores obtained using \textsc{gnb} as a base classifier}
\end{sidewaystable}

\begin{sidewaystable}
\scriptsize
\centering
\setlength{\tabcolsep}{3.5pt}
\def\arraystretch{1.15}
\begin{tabular}{@{}|ccccc|ccccc||ccccc|ccccc||ccc|r|}\hline%

\multicolumn{10}{|c||}{\multirow{2}{*}{\bfseries Without oversampled set}} &
\multicolumn{10}{ c||}{\multirow{2}{*}{\bfseries With oversampled set}} &
\multirow{5}{*}{\rotatebox[origin=c]{-90}{\bfseries OS}} &
\multirow{5}{*}{\rotatebox[origin=c]{-90}{\bfseries US}} &
\multirow{5}{*}{\rotatebox[origin=c]{-90}{\bfseries Full}} &
\multirow{5}{*}{\rotatebox[origin=c]{-90}{\bfseries Dataset}}

\\
\multicolumn{10}{|c||}{}&
\multicolumn{10}{c||}{}&
\multicolumn{3}{c|}{}&

	 \\

	\multicolumn{5}{|c|}{\bfseries All members} &
	\multicolumn{5}{c||}{\bfseries Reduced members} &
	\multicolumn{5}{c|}{\bfseries All members} &
	\multicolumn{5}{c||}{\bfseries Reduced members} 
	& & & & \\

	\multirow{2}{*}{\rotatebox[origin=c]{-90}{\textsc{reg}}} &
	\multirow{2}{*}{\rotatebox[origin=c]{-90}{\textsc{wei}}} &
	\multirow{2}{*}{\rotatebox[origin=c]{-90}{\textsc{con}}} &
	\multirow{2}{*}{\rotatebox[origin=c]{-90}{\textsc{nor}}} &
	\multirow{2}{*}{\rotatebox[origin=c]{-90}{\textsc{nc}}} &

	\multirow{2}{*}{\rotatebox[origin=c]{-90}{\textsc{reg}}} &
	\multirow{2}{*}{\rotatebox[origin=c]{-90}{\textsc{wei}}} &
	\multirow{2}{*}{\rotatebox[origin=c]{-90}{\textsc{con}}} &
	\multirow{2}{*}{\rotatebox[origin=c]{-90}{\textsc{nor}}} &
	\multirow{2}{*}{\rotatebox[origin=c]{-90}{\textsc{nc}}} &

	\multirow{2}{*}{\rotatebox[origin=c]{-90}{\textsc{reg}}} &
	\multirow{2}{*}{\rotatebox[origin=c]{-90}{\textsc{wei}}} &
	\multirow{2}{*}{\rotatebox[origin=c]{-90}{\textsc{con}}} &
	\multirow{2}{*}{\rotatebox[origin=c]{-90}{\textsc{nor}}} &
	\multirow{2}{*}{\rotatebox[origin=c]{-90}{\textsc{nc}}} &

	\multirow{2}{*}{\rotatebox[origin=c]{-90}{\textsc{reg}}} &
	\multirow{2}{*}{\rotatebox[origin=c]{-90}{\textsc{wei}}} &
	\multirow{2}{*}{\rotatebox[origin=c]{-90}{\textsc{con}}} &
	\multirow{2}{*}{\rotatebox[origin=c]{-90}{\textsc{nor}}} &
	\multirow{2}{*}{\rotatebox[origin=c]{-90}{\textsc{nc}}}

	& & & &

	\\

	&&&&&&&&&&&&&&&&&&&&&&&
	\\\hline\hline

	\csvreader[head to column names,
	           late after line=\csvifoddrow{\\}{\\\rowcolor{gray!10!white}},
	           late after last line = \\\hline]
	{results/kNN.csv}{}%
	{

	\ereg & \ewei & \ecwei & \enwei & \encwei &
	\eregr & \eweir & \ecweir & \enweir & \encweir &
	\eregos & \eweios & \ecweios & \enweios & \encweios & 
	\eregros & \eweiros & \ecweiros & \enweiros & \encweiros &
	\os & \us & \reg &

	\multicolumn{1}{l|}{\emph{\dataset}}

	}%
\end{tabular}
\caption{Balanced accuracy scores obtained using \textsc{knn} as a base classifier}
\end{sidewaystable}

\begin{sidewaystable}
\scriptsize
\centering
\setlength{\tabcolsep}{3.5pt}
\def\arraystretch{1.15}
\begin{tabular}{@{}|ccccc|ccccc||ccccc|ccccc||ccc|r|}\hline%

\multicolumn{10}{|c||}{\multirow{2}{*}{\bfseries Without oversampled set}} &
\multicolumn{10}{ c||}{\multirow{2}{*}{\bfseries With oversampled set}} &
\multirow{5}{*}{\rotatebox[origin=c]{-90}{\bfseries OS}} &
\multirow{5}{*}{\rotatebox[origin=c]{-90}{\bfseries US}} &
\multirow{5}{*}{\rotatebox[origin=c]{-90}{\bfseries Full}} &
\multirow{5}{*}{\rotatebox[origin=c]{-90}{\bfseries Dataset}}

\\
\multicolumn{10}{|c||}{}&
\multicolumn{10}{c||}{}&
\multicolumn{3}{c|}{}&

	 \\

	\multicolumn{5}{|c|}{\bfseries All members} &
	\multicolumn{5}{c||}{\bfseries Reduced members} &
	\multicolumn{5}{c|}{\bfseries All members} &
	\multicolumn{5}{c||}{\bfseries Reduced members} 
	& & & & \\

	\multirow{2}{*}{\rotatebox[origin=c]{-90}{\textsc{reg}}} &
	\multirow{2}{*}{\rotatebox[origin=c]{-90}{\textsc{wei}}} &
	\multirow{2}{*}{\rotatebox[origin=c]{-90}{\textsc{con}}} &
	\multirow{2}{*}{\rotatebox[origin=c]{-90}{\textsc{nor}}} &
	\multirow{2}{*}{\rotatebox[origin=c]{-90}{\textsc{nc}}} &

	\multirow{2}{*}{\rotatebox[origin=c]{-90}{\textsc{reg}}} &
	\multirow{2}{*}{\rotatebox[origin=c]{-90}{\textsc{wei}}} &
	\multirow{2}{*}{\rotatebox[origin=c]{-90}{\textsc{con}}} &
	\multirow{2}{*}{\rotatebox[origin=c]{-90}{\textsc{nor}}} &
	\multirow{2}{*}{\rotatebox[origin=c]{-90}{\textsc{nc}}} &

	\multirow{2}{*}{\rotatebox[origin=c]{-90}{\textsc{reg}}} &
	\multirow{2}{*}{\rotatebox[origin=c]{-90}{\textsc{wei}}} &
	\multirow{2}{*}{\rotatebox[origin=c]{-90}{\textsc{con}}} &
	\multirow{2}{*}{\rotatebox[origin=c]{-90}{\textsc{nor}}} &
	\multirow{2}{*}{\rotatebox[origin=c]{-90}{\textsc{nc}}} &

	\multirow{2}{*}{\rotatebox[origin=c]{-90}{\textsc{reg}}} &
	\multirow{2}{*}{\rotatebox[origin=c]{-90}{\textsc{wei}}} &
	\multirow{2}{*}{\rotatebox[origin=c]{-90}{\textsc{con}}} &
	\multirow{2}{*}{\rotatebox[origin=c]{-90}{\textsc{nor}}} &
	\multirow{2}{*}{\rotatebox[origin=c]{-90}{\textsc{nc}}}

	& & & &

	\\

	&&&&&&&&&&&&&&&&&&&&&&&
	\\\hline\hline

	\csvreader[head to column names,
	           late after line=\csvifoddrow{\\}{\\\rowcolor{gray!10!white}},
	           late after last line = \\\hline]
	{results/DTC.csv}{}%
	{

	\ereg & \ewei & \ecwei & \enwei & \encwei &
	\eregr & \eweir & \ecweir & \enweir & \encweir &
	\eregos & \eweios & \ecweios & \enweios & \encweios & 
	\eregros & \eweiros & \ecweiros & \enweiros & \encweiros &
	\os & \us & \reg &

	\multicolumn{1}{l|}{\emph{\dataset}}

	}%
\end{tabular}
\caption{Balanced accuracy scores obtained using \textsc{dtc} as a base classifier}
\end{sidewaystable}

Sub-figures can be created using \verb|\subfigure|, which is
defined by the \textsf{jmlr} class. The optional argument allows
you to provide a subcaption. The label should be placed in the
mandatory argument of \verb|\subfigure|. You can reference the
entire figure, for example \figureref{fig:subfigex}, or you can
reference part of the figure using \verb|\figureref|, for example
\figureref{fig:circle}. Alternatively you can reference the
subfigure using \verb|\subfigref|, for example
\subfigref{fig:circle,fig:square} in \figureref{fig:subfigex}.

\begin{figure}[htbp]
\floatconts
  {fig:subfigex}
  {\caption{An Example With Sub-Figures.}}
  {%
    \subfigure[A Circle]{\label{fig:circle}%
      \includegraphics[width=0.2\linewidth]{images/circle}}%
    \qquad
    \subfigure[A Square]{\label{fig:square}%
      \includegraphics[width=0.2\linewidth]{images/square}}
  }
\end{figure}

By default, the sub-figures are aligned on the baseline.
This can be changed using the second optional argument
of \verb|\subfigure|. This may be \texttt{t} (top), \texttt{c}
(centered) or \texttt{b} (bottom). For example, the subfigures
\subfigref{fig:circle2,fig:square2} in \figureref{fig:subfigex2}
both have \verb|[c]| as the second optional argument.

\begin{figure}[htbp]
\floatconts
  {fig:subfigex2}
  {\caption{Another Example With Sub-Figures.}}
  {%
    \subfigure[A Small Circle][c]{\label{fig:circle2}%
      \includegraphics[width=0.1\linewidth]{images/circle}}%
    \qquad
    \subfigure[A Square][c]{\label{fig:square2}%
      \includegraphics[width=0.2\linewidth]{images/square}}
  }
\end{figure}

\subsection{Sub-Tables}
\label{sec:subtables}
There is an analogous command \verb|\subtable| for sub-tables.
It has the same syntax as \verb|\subfigure| described above.
You can reference the table using \verb|\tableref|, for example
\tableref{tab:subtabex} or you can reference part of the table,
for example \tableref{tab:ab}. Alternatively you can reference the
subtable using \verb|\subtabref|, for example
\subtabref{tab:ab,tab:cd} in \tableref{tab:subtabex}.

\begin{table}[htbp]
\floatconts
 {tab:subtabex}
 {\caption{An Example With Sub-Tables}}
 {%
   \subtable{%
     \label{tab:ab}%
     \begin{tabular}{cc}
     \bfseries A & \bfseries B\\
     1 & 2
     \end{tabular}
   }\qquad
   \subtable{%
     \label{tab:cd}%
     \begin{tabular}{cc}
     \bfseries C & \bfseries D\\
     3 & 4\\
     5 & 6
     \end{tabular}
   }
 }
\end{table}

By default, the sub-tables are aligned on the top.
This can be changed using the second optional argument
of \verb|\subtable|. This may be \texttt{t} (top), \texttt{c}
(centered) or \texttt{b} (bottom). For example, the sub-tables
\subtabref{tab:ab2,tab:cd2} in \tableref{tab:subtabex2}
both have \verb|[c]| as the second optional argument.

\begin{table}[htbp]
\floatconts
 {tab:subtabex2}
 {\caption{Another Example With Sub-Tables}}
 {%
   \subtable[][c]{%
     \label{tab:ab2}%
     \begin{tabular}{cc}
     \bfseries A & \bfseries B\\
     1 & 2
     \end{tabular}
   }\qquad
   \subtable[][c]{%
     \label{tab:cd2}%
     \begin{tabular}{cc}
     \bfseries C & \bfseries D\\
     3 & 4\\
     5 & 6
     \end{tabular}
   }
 }
\end{table}

\subsection{Algorithms}
\label{sec:algorithms}

Enumerated textual algorithms can be displayed using the
\texttt{algorithm} environment. Within this environment, use
use an \texttt{enumerate} or nested \texttt{enumerate} environments.
For example, see \algorithmref{alg:gauss}. Note that algorithms
float like figures and tables.

\begin{algorithm}[htbp]
\floatconts
{alg:gauss}% label
{\caption{The Gauss-Seidel Algorithm}}
{% contents
\begin{enumerate}
  \item For $k=1$ to maximum number of iterations
    \begin{enumerate}
      \item For $i=1$ to $n$
        \begin{enumerate}
        \item $x_i^{(k)} = 
          \frac{b_i - \sum_{j=1}^{i-1}a_{ij}x_j^{(k)}
          - \sum_{j=i+1}^{n}a_{ij}x_j^{(k-1)}}{a_{ii}}$
        \item If $\|\vec{x}^{(k)}-\vec{x}^{(k-1)} < \epsilon\|$,
          where $\epsilon$ is a specified stopping criteria, stop.
      \end{enumerate}
    \end{enumerate}
\end{enumerate}
}
\end{algorithm}

You can use \verb|\caption| and \verb|\label| without using
\verb|\floatconts| (as in \algorithmref{alg:moore}).

If you'd rather have the same numbering throughout the algorithm
but still want the convenient indentation of nested 
\texttt{enumerate} environments, you can use the
\texttt{enumerate*} environment provided by the \textsf{jmlr}
class. For example, see \algorithmref{alg:moore}.

\begin{algorithm}
\caption{Moore's Shortest Path}\label{alg:moore}
Given a connected graph $G$, where the length of each edge is 1:
\begin{enumerate*}
  \item Set the label of vertex $s$ to 0
  \item Set $i=0$
  \begin{enumerate*}
    \item \label{step:locate}Locate all unlabelled vertices 
          adjacent to a vertex labelled $i$ and label them $i+1$
    \item If vertex $t$ has been labelled,
    \begin{enumerate*}
      \item[] the shortest path can be found by backtracking, and 
      the length is given by the label of $t$.
    \end{enumerate*}
    otherwise
    \begin{enumerate*}
      \item[] increment $i$ and return to step~\ref{step:locate}
    \end{enumerate*}
  \end{enumerate*}
\end{enumerate*}
\end{algorithm}

Pseudo code can be displayed using the \texttt{algorithm2e}
environment. This is defined by the \textsf{algorithm2e} package
(which is automatically loaded) so check the \textsf{algorithm2e}
documentation for further details.\footnote{Either \texttt{texdoc
algorithm2e} or \url{http://www.ctan.org/pkg/algorithm2e}}
For an example, see \algorithmref{alg:net}.

\begin{algorithm2e}
\caption{Computing Net Activation}
\label{alg:net}
 % older versions of algorithm2e have \dontprintsemicolon instead
 % of the following:
 %\DontPrintSemicolon
 % older versions of algorithm2e have \linesnumbered instead of the
 % following:
 %\LinesNumbered
\KwIn{$x_1, \ldots, x_n, w_1, \ldots, w_n$}
\KwOut{$y$, the net activation}
$y\leftarrow 0$\;
\For{$i\leftarrow 1$ \KwTo $n$}{
  $y \leftarrow y + w_i*x_i$\;
}
\end{algorithm2e}

\section{Description Lists}

The \textsf{jmlr} class also provides a description-like 
environment called \texttt{altdescription}. This has an
argument that should be the widest label in the list. Compare:
\begin{description}
\item[add] A method that adds two variables.
\item[differentiate] A method that differentiates a function.
\end{description}
with
\begin{altdescription}{differentiate}
\item[add] A method that adds two variables.
\item[differentiate] A method that differentiates a function.
\end{altdescription}

\section{Theorems, Lemmas etc}
\label{sec:theorems}

The following theorem-like environments are predefined by
the \textsf{jmlr} class: \texttt{theorem}, \texttt{example},
\texttt{lemma}, \texttt{proposition}, \texttt{remark}, 
\texttt{corollary}, \texttt{definition}, \texttt{conjecture}
and \texttt{axiom}. You can use the \texttt{proof} environment
to display the proof if need be, as in \theoremref{thm:eigenpow}.

\begin{theorem}[Eigenvalue Powers]\label{thm:eigenpow}
If $\lambda$ is an eigenvalue of $\vec{B}$ with eigenvector
$\vec{\xi}$, then $\lambda^n$ is an eigenvalue of $\vec{B}^n$
with eigenvector $\vec{\xi}$.
\begin{proof}
Let $\lambda$ be an eigenvalue of $\vec{B}$ with eigenvector
$\xi$, then
\begin{align*}
\vec{B}\vec{\xi} &= \lambda\vec{\xi}
\intertext{premultiply by $\vec{B}$:}
\vec{B}\vec{B}\vec{\xi} &= \vec{B}\lambda\vec{\xi}\\
\Rightarrow \vec{B}^2\vec{\xi} &= \lambda\vec{B}\vec{\xi}\\
&= \lambda\lambda\vec{\xi}\qquad
\text{since }\vec{B}\vec{\xi}=\lambda\vec{\xi}\\
&= \lambda^2\vec{\xi}
\end{align*}
Therefore true for $n=2$. Now assume true for $n=k$:
\begin{align*}
\vec{B}^k\vec{\xi} &= \lambda^k\vec{\xi}
\intertext{premultiply by $\vec{B}$:}
\vec{B}\vec{B}^k\vec{\xi} &= \vec{B}\lambda^k\vec{\xi}\\
\Rightarrow \vec{B}^{k+1}\vec{\xi} &= \lambda^k\vec{B}\vec{\xi}\\
&= \lambda^k\lambda\vec{\xi}\qquad
\text{since }\vec{B}\vec{\xi}=\lambda\vec{\xi}\\
&= \lambda^{k+1}\vec{\xi}
\end{align*}
Therefore true for $n=k+1$. Therefore, by induction, true for all
$n$.
\end{proof}
\end{theorem}

\begin{lemma}[A Sample Lemma]\label{lem:sample}
This is a lemma.
\end{lemma}

\begin{remark}[A Sample Remark]\label{rem:sample}
This is a remark.
\end{remark}

\begin{corollary}[A Sample Corollary]\label{cor:sample}
This is a corollary.
\end{corollary}

\begin{definition}[A Sample Definition]\label{def:sample}
This is a definition.
\end{definition}

\begin{conjecture}[A Sample Conjecture]\label{con:sample}
This is a conjecture.
\end{conjecture}

\begin{axiom}[A Sample Axiom]\label{ax:sample}
This is an axiom.
\end{axiom}

\begin{example}[An Example]\label{ex:sample}
This is an example.
\end{example}

\section{Color vs Grayscale}
\label{sec:color}

It's helpful if authors supply grayscale versions of their
images in the event that the article is to be incorporated into
a black and white printed book. With external PDF, PNG or JPG
graphic files, you just need to supply a grayscale version of the
file. For example, if the file is called \texttt{myimage.png},
then the gray version should be \texttt{myimage-gray.png} or
\texttt{myimage-gray.pdf} or \texttt{myimage-gray.jpg}. You don't
need to modify your code. The \textsf{jmlr} class checks for
the existence of the grayscale version if it is print mode 
(provided you have used \verb|\includegraphics| and haven't
specified the file extension).

You can use \verb|\ifprint| to determine which mode you are in.
For example, in \figureref{fig:nodes}, the 
\ifprint{dark gray}{purple} ellipse represents an input and the
\ifprint{light gray}{yellow} ellipse represents an output.
Another example: {\ifprint{\bfseries}{\color{red}}important text!}

You can use the class option \texttt{gray} to see how the
document will appear in gray scale mode. \textcolor{blue}{Colored
text} will automatically be converted to gray scale.

The \textsf{jmlr} class loads the \textsf{xcolor}
package, so you can also define your own colors. For example:
\ifprint
  {\definecolor{myred}{gray}{0.5}}%
  {\definecolor{myred}{rgb}{0.5,0,0}}%
\textcolor{myred}{XYZ}.

The \textsf{xcolor} class is loaded with the \texttt{x11names}
option, so you can use any of the x11 predefined colors (listed
in the \textsf{xcolor} documentation\footnote{either 
\texttt{texdoc xcolor} or \url{http://www.ctan.org/pkg/xcolor}}).

\section{Citations and Bibliography}
\label{sec:cite}

The \textsf{jmlr} class automatically loads \textsf{natbib}.
This sample file has the citations defined in the accompanying
BibTeX file \texttt{jmlr-sample.bib}. For a parenthetical
citation use \verb|\citep|. For example
\citep{guyon-elisseeff-03}. For a textual citation use
\verb|\citet|. For example \citet{guyon2007causalreport}.
Both commands may take a comma-separated list, for example
\citet{guyon-elisseeff-03,guyon2007causalreport}.

These commands have optional arguments and have a starred
version. See the \textsf{natbib} documentation for further
details.\footnote{Either \texttt{texdoc natbib} or
\url{http://www.ctan.org/pkg/natbib}}

The bibliography is displayed using \verb|\bibliography|.

\acks{Acknowledgements go here.}

\bibliography{bibliography}

\appendix

\section{First Appendix}\label{apd:first}

This is the first appendix.

\section{Second Appendix}\label{apd:second}

This is the second appendix.

\end{document}

### 2018-07-06 method.py

@@ -13,26 +13,24 @@ class UndersampledEnsemble():
         self.dbname = dbname
         self.clfs = []
 
-    def fit(self, X, y):
-        #print("Fit")
+    def fit(self, X_train, y_train):
         # Save X and y
-        self.X = X
-        self.y = y
+        self.X_train = X_train
+        self.y_train = y_train
 
         # Firstly we analyze the training set to find majority class and to
         # establish the imbalance ratio
-        classes, c_counts = np.unique(y, return_counts=True)
+        self.classes, c_counts = np.unique(y_train, return_counts=True)
         majority_c = 0 if c_counts[0] > c_counts[1] else 1
         minority_c = 1 - majority_c
 
-        min_idx = np.where(y == minority_c)[0]
-        maj_idx = np.where(y == majority_c)[0]
-
-        imbalance_ratio = c_counts[majority_c] / c_counts[minority_c]
+        min_idx = np.where(y_train == minority_c)[0]
+        maj_idx = np.where(y_train == majority_c)[0]
 
         # K is the imbalanced ratio round to int, being also a number of
         # ensemble members.
-        self.k = int(imbalance_ratio)
+        imbalance_ratio = c_counts[majority_c] / c_counts[minority_c]
+        self.k = int(np.around(imbalance_ratio))
         self.k = self.k if self.k > 2 else 2
 
         # We use k to KFold division of majority class
@@ -40,38 +38,37 @@ class UndersampledEnsemble():
         kf = model_selection.KFold(n_splits=self.k, shuffle=True)
         for _, index in kf.split(maj_idx):
             fold_idx = np.concatenate([min_idx, maj_idx[index]])
-            X_train, y_train = X[fold_idx], y[fold_idx]
+            X_train_f, y_train_f = X_train[fold_idx], y_train[fold_idx]
 
             clf = base.clone(self.base_clf)
-            clf.fit(X_train, y_train)
+            clf.fit(X_train_f, y_train_f)
             self.clfs.append(clf)
 
         # Add OS
         clf = base.clone(self.base_clf)
         os = over_sampling.RandomOverSampler()
-        X_os, y_os = os.fit_sample(X, y)
+        X_os, y_os = os.fit_sample(self.X_train, self.y_train)
         clf.fit(X_os, y_os)
         self.clfs.append(clf)
 
-
         # Calculate weights as balanced accuracy on whole set
[…]

### 2018-07-06 process.py

@@ -1,7 +1,12 @@
+"""
+Ensemble of imbalance ratio folded undersampling experiments.
+"""
+import csv
 import helper as h
+from scipy import stats
+from tqdm import tqdm
 import numpy as np
 import method as m
-import csv
 from sklearn import svm, base, neighbors, metrics, naive_bayes, tree, neural_network
 from imblearn import under_sampling, over_sampling, ensemble
 
@@ -9,109 +14,179 @@ from imblearn import under_sampling, over_sampling, ensemble
 base_clfs = {
     #"SVC" : svm.SVC(probability=True, gamma='scale'),
     "GNB" : naive_bayes.GaussianNB(),
-    #"kNN" : neighbors.KNeighborsClassifier(),
-    #"DTC" : tree.DecisionTreeClassifier(),
+    "kNN" : neighbors.KNeighborsClassifier(),
+    "DTC" : tree.DecisionTreeClassifier(),
     #"MLP" : neural_network.MLPClassifier(),
 }
 datasets = h.datasets_for_groups([
     "imb_IRhigherThan9p1",
     "imb_IRhigherThan9p2",
-    "imb_IRlowerThan9",
+    #"imb_IRlowerThan9",
 ])
+header = ['dataset',
+          'reg','regd',
+          'us','usd',
+          'os','osd',
+          'ereg','eregd',
+          'ewei','eweid',
+          'ecwei','ecweid',
+          'enwei','enweid',
+          'encwei','encweid',
+          'eregr','eregrd',
+          'eweir','eweird',
+          'ecweir','ecweird',
+          'enweir','enweird',
+          'encweir','encweird',
+            'eregos','eregosd',
+            'eweios','eweiosd',
+            'ecweios','ecweiosd',
+            'enweios','enweiosd',
+            'encweios','encweiosd',
+            'eregros','eregrosd',
+            'eweiros','eweirosd',
+            'ecweiros','ecweirosd',
+            'enweiros','enweirosd',
+            'encweiros','encweirosd'
+]
+versions = 20
 
-for bclf in base_clfs:
-    print(bclf)
+for bclf in tqdm(base_clfs):
     base_clf = base_clfs[bclf]
-    with open('results/%s.csv' % bclf, 'w') as csvfile:
-        writer = csv.writer(csvfile, delimiter=',')
-        writer.writerow(['dataset','reg','regd','us','usd','os','osd',
-                             'ens','ensd','wens','wensd','cwens','cwensd'])
[…]

### 2018-07-08 article.tex
Scheme.

@@
 \title
-[Short Title]
+[Fusers in homogenous ensemble of undersampled majority class]
 {
-	The undersampling ensemble approach to highly imbalanced data classification%\titlebreak
+	Fusers in homogenous ensemble of undersampled majority class for highly imbalanced data classification%\titlebreak
 }
@@
 
-This is a sample article that uses the \textsf{jmlr} class with
-the \texttt{wcp} class option.  Please follow the guidelines in
-this sample document as it can help to reduce complications when
-combining the articles into a book. Please avoid using obsolete
-commands, such as \verb|\rm|, and obsolete packages, such as
-\textsf{epsfig}.\footnote{See
-\url{http://www.ctan.org/pkg/l2tabu}}
+Additionally, in incremental learning, if the majority-class objects outnumber greatly the minority class, the latter can be completely ignored \cite{He:2009}.
+The aforementioned issues are reasons why most existing classification methods for imbalanced data are restricted to the \textit{offline} learning only, i.e., a case where the entire data set is provided prior to the analysis.
 
-Please also ensure that your document will compile with PDF\LaTeX.
-If you have an error message that's puzzling you, first check for it
-at the UK TUG FAQ
-\url{http://www.tex.ac.uk/cgi-bin/texfaq2html?label=man-latex}.  If
-that doesn't help, create a minimal working example (see
-\url{http://theoval.cmp.uea.ac.uk/~nlct/latex/minexample/}) and post
-to somewhere like TeX on StackExchange
-(\url{http://tex.stackexchange.com/}) or the LaTeX Community Forum
-(\url{http://www.latex-community.org/forum/}).
+Most of the classification algorithms assume that there are no significant disproportions among instances from different classes.
+Nevertheless, in many practical tasks, we may observe that instances from one class (so-called \textit{majority class}) significantly outnumber the objects from remaining classes (\textit{minority class}).
+Most of traditional classifiers have a bias in favor of the majority class although more often the minority class is more interesting, because misidentification of an instance belonging to it is usually much more expensive than assigning an instance from majority class to minority one.
+A good example is an undetected fraud that would be more expensive than the cost of additional analysis of a correct transaction classified as fraudless transaction.
+Such a problem is known as imbalanced data classification \cite{Sun:2009,Wang:2017}, where an unequal number of instances from the examined classes plays a key role during the classifier learning.
+Various approaches have been proposed in the literature to tackle this challenging difficulty embedded in the nature of data.
+Usually, the researchers are focusing on maximizing the correct minority class classification.
+At the same time, performance on the majority class cannot be neglected.
 
-\begin{note}
-This is an numbered theorem-like environment that was defined in
-this document's preamble.
-\end{note}
+\begin{figure}[!h]
+\floatconts
+  {fig:east}
+  {\caption{Easy separable imbalance dataset}}
+  {\includegraphics[clip=true, trim = 11 11 11 11, width=0.25\linewidth]{figures/easy}}
+\end{figure}
 
-\subsection{Sub-sections}
+In this project we will focus on binary imbalanced problems, because this setup is the one most frequently studied in the literature and most commonly meet in practical problems, e.g.,\textit{fault detection} or \textit{spam filtering}.
+Therefore, another important issue is proposing an appropriate quality measure that would be adequate for imbalanced data classification \cite{Elazmeh:2006}.
 
-Sub-sections are produced using \verb|\subsection|.
+In case of imbalanced data classification the disproportion between the different classes is not the sole issue of learning difficulties.
+One may easily came up with an example where the instance distributions from different classes are well-separated, as depicted in Fig.\ref{fig:easy}.
 
-\subsubsection{Sub-sub-sections}
+Proposing a efficient classifier for such a task is not a challenge.
+Unfortunately, instances from the minority class often form clusters of an unknown structure that are scattered \cite{Napierala:2012}.
+Additional complication comes from the fact that during learning, the number of intactness from the minority class may be not sufficient enough for the learning algorithm to acquire the appropriate generalization level, which in effect can cause \emph{overfitting} \cite{Chen:2008}.
+All those problems are a focus of intense research \cite{Chawla:2002,Bunkhumpornpat:2009,Kubat:1997}.
 
-Sub-sub-sections are produced using \verb|\subsubsection|.
+Methods for imbalanced data classification can be divided into three main groups \cite{Lopez:2012}.
 
-\paragraph{Sub-sub-sub-sections}
+\begin{figure}[!h]
+\floatconts
+  {fig:subfigex}
+  {\caption{Examples of data preprocessing methods.}}
+  {%
+    \subfigure[Original dataset]{\label{fig:circle}%
+    \includegraphics[clip=true, width=.25\linewidth,
+    				 trim = 11 141 141 11]
+    {figures/preprocessing}}%
+    \qquad
+    \subfigure[\textsc{smote}]{\label{fig:circle}%
+    \includegraphics[clip=true, width=.25\linewidth,
+    				 trim = 141 141 11 11]
+    {figures/preprocessing}}%
 
-Sub-sub-sub-sections are produced using \verb|\paragraph|.
-These are unnumbered with a running head.
+    \subfigure[\textsc{adasyn}]{\label{fig:circle}%
+    \includegraphics[clip=true, width=.25\linewidth,
+    				 trim = 11 11 141 141]
+    {figures/preprocessing}}%
+    \qquad
+    \subfigure[Undersampling]{\label{fig:circle}%
+    \includegraphics[clip=true, width=.25\linewidth,
+    				 trim = 141 11 11 141]
+    {figures/preprocessing}}%
+  }
+\end{figure}
 
-\subparagraph{Sub-sub-sub-sub-sections}
+\noindent\textbf{ Data preprocessing methods}.
+This approach focuses on reducing the number of objects in majority class (\emph{undersampling}) or generating new objects of the minority class (\textit{oversampling}).
+The difference between \emph{under-} and \emph{oversampling} is presented in Fig.
+\ref{fig:over-under}.
 
-Sub-sub-sub-sub-sections are produced using \verb|\subparagraph|.
-These are unnumbered with a running head.
-
-\section{Cross-Referencing}
-
-Always use \verb|\label| and \verb|\ref| (or one of the commands
-described below) when cross-referencing.  For example, the next
-section is Section~\ref{sec:math}. The \textsf{jmlr} class
-provides some convenient cross-referencing commands:
-\verb|\sectionref|, \verb|\equationref|, \verb|\tableref|,
-\verb|\figureref|, \verb|\algorithmref|, \verb|\theoremref|,
-\verb|\lemmaref|, \verb|\remarkref|, \verb|\corollaryref|,
-\verb|\definitionref|, \verb|\conjectureref|, \verb|\axiomref|,
-\verb|\exampleref| and \verb|\appendixref|. The argument of these
-commands may either be a single label or a comma-separated list
-of labels. Examples:
-
-Referencing sections: \sectionref{sec:math} or
-\sectionref{sec:intro,sec:math} or
-\sectionref{sec:intro,sec:math,sec:tables,sec:figures}.
-
-Referencing equations: \equationref{eq:trigrule} or
-\equationref{eq:trigrule,eq:df} or
-\equationref{eq:trigrule,eq:f,eq:df,eq:y}.
-
-Referencing tables: \tableref{tab:operatornames} or
-\tableref{tab:operatornames,tab:example} or
-\tableref{tab:operatornames,tab:example,tab:example-booktabs}.
-
-Referencing figures: \figureref{fig:nodes} or
-\figureref{fig:nodes,fig:teximage} or
-\figureref{fig:nodes,fig:teximage,fig:subfigex} or
-\figureref{fig:circle,fig:square}.
-
-Referencing algorithms: \algorithmref{alg:gauss} or
-\algorithmref{alg:gauss,alg:moore} or
-\algorithmref{alg:gauss,alg:moore,alg:net}.
-
-Referencing theorem-like environments: \theoremref{thm:eigenpow},
-\lemmaref{lem:sample}, \remarkref{rem:sample}, 
-\corollaryref{cor:sample}, \definitionref{def:sample},
-\conjectureref{con:sample}, \axiomref{ax:sample} and
-\exampleref{ex:sample}.
-
-Referencing appendices: \appendixref{apd:first} or
-\appendixref{apd:first,apd:second}.
-
-\section{Equations}
-\label{sec:math}
-
-The \textsf{jmlr} class loads the \textsf{amsmath} package, so
-you can use any of the commands and environments defined there.
-(See the \textsf{amsmath} documentation for further
-details.\footnote{Either \texttt{texdoc amsmath} or
-\url{http://www.ctan.org/pkg/amsmath}})
-
-Unnumbered single-lined equations should be displayed using
-\verb|\[| and \verb|\]|. For example:
-\[E = m c^2\]
-Numbered single-line equations should be displayed using the
-\texttt{equation} environment. For example:
-\begin{equation}\label{eq:trigrule}
-\cos^2\theta + \sin^2\theta \equiv 1
-\end{equation}
-This can be referenced using \verb|\label| and \verb|\equationref|.
-For example, \equationref{eq:trigrule}.
-
-Multi-lined numbered equations should be displayed using the
-\texttt{align} environment.\footnote{For reasons why you 
-shouldn't use the obsolete \texttt{eqnarray} environment, see
-Lars Madsen, \emph{Avoid eqnarray!} TUGboat 33(1):21--25, 2012.} For example:
-\begin{align}
-f(x) &= x^2 + x\label{eq:f}\\
-f'(x) &= 2x + 1\label{eq:df}
-\end{align}
-Unnumbered multi-lined equations should be displayed using the
-\texttt{align*} environment. For example:
-\begin{align*}
-f(x) &= (x+1)(x-1)\\
-&= x^2 - 1
-\end{align*}
-If you want to mix numbered with unnumbered lines use the
-align environment and suppress unwanted line numbers with
-\verb|\nonumber|. For example:
-\begin{align}
-y &= x^2 + 3x - 2x + 1\nonumber\\
-&= x^2 + x + 1\label{eq:y}
-\end{align}
-An equation that is too long to fit on a single line can be
-displayed using the \texttt{split} environment. 
-Text can be embedded in an equation using \verb|\text| or
-\verb|\intertext| (as used in \theoremref{thm:eigenpow}).
-See the \textsf{amsmath} documentation for further details.
-
-\subsection{Operator Names}
-\label{sec:op}
-
-Predefined operator names are listed in \tableref{tab:operatornames}.
-For additional operators, either use \verb|\operatorname|,
-for example $\operatorname{var}(X)$ or declare it with
-\verb|\DeclareMathOperator|, for example
-\begin{verbatim}
-\DeclareMathOperator{\var}{var}
-\end{verbatim}
-and then use this new command. If you want limits that go above and
-below the operator (like \verb|\sum|) use the starred versions
-(\verb|\operatorname*| or \verb|\DeclareMathOperator*|).
-
-\begin{table}[htbp]
-\floatconts
-  {tab:operatornames}%
-  {\caption{Predefined Operator Names (taken from 
-   \textsf{amsmath} documentation)}}%
-  {%
-\begin{tabular}{rlrlrlrl}
-\cs{arccos} & $\arccos$ &  \cs{deg} & $\deg$ &  \cs{lg} & $\lg$ &  \cs{projlim} & $\projlim$ \\
-\cs{arcsin} & $\arcsin$ &  \cs{det} & $\det$ &  \cs{lim} & $\lim$ &  \cs{sec} & $\sec$ \\
-\cs{arctan} & $\arctan$ &  \cs{dim} & $\dim$ &  \cs{liminf} & $\liminf$ &  \cs{sin} & $\sin$ \\
-\cs{arg} & $\arg$ &  \cs{exp} & $\exp$ &  \cs{limsup} & $\limsup$ &  \cs{sinh} & $\sinh$ \\
-\cs{cos} & $\cos$ &  \cs{gcd} & $\gcd$ &  \cs{ln} & $\ln$ &  \cs{sup} & $\sup$ \\
-\cs{cosh} & $\cosh$ &  \cs{hom} & $\hom$ &  \cs{log} & $\log$ &  \cs{tan} & $\tan$ \\
-\cs{cot} & $\cot$ &  \cs{inf} & $\inf$ &  \cs{max} & $\max$ &  \cs{tanh} & $\tanh$ \\
-\cs{coth} & $\coth$ &  \cs{injlim} & $\injlim$ &  \cs{min} & $\min$ \\
-\cs{csc} & $\csc$ &  \cs{ker} & $\ker$ &  \cs{Pr} & $\Pr$
-\end{tabular}\par
-\begin{tabular}{rlrl}
-\cs{varlimsup} & $\varlimsup$ 
-& \cs{varinjlim} & $\varinjlim$\\
-\cs{varliminf} & $\varliminf$ 
-& \cs{varprojlim} & $\varprojlim$
-\end{tabular}
-}
-\end{table}
-
-\section{Vectors and Sets}
-\label{sec:vec}
-
-Vectors should be typeset using \cs{vec}. For example $\vec{x}$.
-The \textsf{jmlr} class also provides \cs{set} to typeset a
-set. For example $\set{S}$.
-
-\section{Floats}
-\label{sec:floats}
-
-Floats, such as figures, tables and algorithms, are moving
-objects and are supposed to float to the nearest convenient
-location. Please don't force them to go in a particular place. In
-general it's best to use the \texttt{htbp} specifier and don't
-put the figure or table in the middle of a paragraph (that is
-make sure there's a paragraph break above and below the float).
-Floats are supposed to have a little extra space above and below
-them to make them stand out from the rest of the text. This extra
-spacing is put in automatically and shouldn't need modifying.
-
-To ensure consistency, please \emph{don't} try changing the format of the caption by doing
-something like:
-\begin{verbatim}
-\caption{\textit{A Sample Caption.}}
-\end{verbatim}
-or
-\begin{verbatim}
-\caption{\em A Sample Caption.}
-\end{verbatim}
-You can, of course, change the font for individual words or 
-phrases, for example:
-\begin{verbatim}
-\caption{A Sample Caption With Some \emph{Emphasized Words}.}
-\end{verbatim}
-
-\subsection{Tables}
-\label{sec:tables}
-
-Tables should go in the \texttt{table} environment. Within this
-environment use \verb|\floatconts| (defined by \textsf{jmlr})
-to set the caption correctly and center the table contents.
-
-\begin{table}[htbp]
- % The first argument is the label.
- % The caption goes in the second argument, and the table contents
- % go in the third argument.
-\floatconts
-  {tab:example}%
-  {\caption{An Example Table}}%
-  {\begin{tabular}{ll}
-  \bfseries Dataset & \bfseries Result\\
-  Data1 & 0.12345\\
-  Data2 & 0.67890\\
-  Data3 & 0.54321\\
-  Data4 & 0.09876
-  \end{tabular}}
-\end{table}
-
-If you want horizontal rules you can use the \textsf{booktabs}
-package which provides the commands \verb|\toprule|, 
-\verb|\midrule| and \verb|\bottomrule|. For example, see
-\tableref{tab:example-booktabs}.
-
-\begin{table}[hbtp]
-\floatconts
-  {tab:example-booktabs}
-  {\caption{A Table With Horizontal Lines}}
-  {\begin{tabular}{ll}
-  \toprule
-  \bfseries Dataset & \bfseries Result\\
-  \midrule
-  Data1 & 0.12345\\
-  Data2 & 0.67890\\
-  Data3 & 0.54321\\
-  Data4 & 0.09876\\
-  \bottomrule
-  \end{tabular}}
-\end{table}
-
-If you want vertical lines as well, you can't use the
-\textsf{booktabs} commands as there'll be some unwanted gaps.
-Instead you can use \LaTeX's \verb|\hline|, but the rows may
-appear a bit cramped.  You can add extra space above or below a
-row using \verb|\abovestrut| and \verb|\belowstrut|. For example,
-see \tableref{tab:example-hline}.
-
-\begin{table}[htbp]
-\floatconts
-  {tab:example-hline}
-  {\caption{A Table With Horizontal and Vertical Lines}}%
-  {%
-    \begin{tabular}{|l|l|}
-    \hline
-    \abovestrut{2.2ex}\bfseries Dataset & \bfseries Result\\\hline
-    \abovestrut{2.2ex}Data1 & 0.12345\\
-    Data2 & 0.67890\\
-    Data3 & 0.54321\\
-    \belowstrut{0.2ex}Data4 & 0.09876\\\hline
-    \end{tabular}
-  }
-\end{table}
-
-If you want to align numbers on their decimal point, you can
-use the \textsf{siunitx} package. For example, see
-\tableref{tab:example-siunitx}. For further details see the
-\textsf{siunitx} documentation\footnote{Either \texttt{texdoc
-siunitx} or \url{http://www.ctan.org/pkg/siunitx}}.
-
-\begin{table}[htbp]
-\floatconts
-  {tab:example-siunitx}
-  {\caption{A Table With Numbers Aligned on the Decimal Point}}
-  {\begin{tabular}{lS[tabformat=3.5]}
-  \bfseries Dataset & {\bfseries Result}\\
-  Data1 & 0.12345\\
-  Data2 & 10.6789\\
-  Data3 & 50.543\\
-  Data4 & 200.09876
-  \end{tabular}}
-\end{table}
-
-If the table is too wide, you can adjust the inter-column
-spacing by changing the value of \verb|\tabcolsep|. For
-example:
-\begin{verbatim}
-\setlength{\tabcolsep}{3pt}
-\end{verbatim}
-If the table is very wide but not very long, you can use the
-\texttt{sidewaystable} environment defined in the
-\textsf{rotating} package (so use \verb|\usepackage{rotating}|).
-If the table is too long to fit on a page, you should use the
-\texttt{longtable} environment defined in the \textsf{longtable}
-package (so use \verb|\usepackage{longtable}|).
-
-\subsection{Figures}
-\label{sec:figures}
-
-Figures should go in the \texttt{figure} environment. Within this
-environment, use \verb|\floatconts| to correctly position the
-caption and center the image. Use \verb|\includegraphics|
-for external graphics files but omit the file extension. Do not
-use \verb|\epsfig| or \verb|\psfig|. If you want to scale the
-image, it's better to use a fraction of the line width rather
-than an explicit length. For example, see \figureref{fig:nodes}.
+These mechanisms have the objective of balancing the quantity of instances from considered classes.
+For oversampling, new instances are random copies of existing ones or are generated in a guided manner.
+The most popular method is \textsc{smote} \cite{Cha2002} algorithm, which creates new instances on a basis of existing ones by slightly modifying the values of their attributes.
+As a result, new artificial examples that are in compliance with the minority class distribution are generated.
+Other oversampling methods are \textsc{adasyn} \cite{He:2008}, in which a difficulty of an object for the classifying model is considered or \textsc{ramob}oost \cite{Chen:2010}.
+Unfortunately, methods such as \textsc{smote} may lead to changes in the characteristic of the minority class and in result to \emph{overfitting} the classifier, what was shown in Fig.
+\ref{fig:wrong_smote}.
 
 \begin{figure}[htbp]
- % Caption and label go in the first argument and the figure contents
- % go in the second argument
 \floatconts
-  {fig:nodes}
-  {\caption{Example Image}}
-  {\includegraphics[width=0.5\linewidth]{images/nodes}}
+  {fig:subfigex}
+  {\caption{Example of wrong \textsc{smote} oversampling.}}
+  {%
+    \subfigure[Original dataset]{\label{fig:circle}%
+    \includegraphics[clip=true, width=.25\linewidth,
+    				 trim = 11 11 141 11]
+    {figures/wrong_smote}}%
+    \qquad
+    \subfigure[\textsc{smote}]{\label{fig:circle}%
+    \includegraphics[clip=true, width=.25\linewidth,
+    				 trim = 141 11 11 11]
+    {figures/wrong_smote}}%
+  }
 \end{figure}
 
-If your image is made up of \LaTeX\ code (for example, commands
-provided by the \textsf{pgf} package) you can include it using
-\cs{includeteximage} (defined by the \textsf{jmlr} class). This
-can be scaled and rotated in the same way as \cs{includegraphics}.
-For example, see \figureref{fig:teximage}.
+W WYPADKU UNDERSAMPLINGU NIE WYSTEPUJE RYZYKO NIESŁUSZNEGO ROZSZERZENIA PRZESTRZENI WZORCÓW KLASY MNIEJSZOŚCIOWEJ, CO MA MIEJSCE W CHOĆBY SMOTE.
+
+Several modifications of \textsc{smote} have been proposed that are able to identify the instances to be copied in a more intelligent fashion such as \emph{Borderline}\textsc{smote} \cite{Han:2005}.
+It generates new instances from the minority class close to the decision border.
+\emph{Safe-Level} \textsc{smote} \citep{Bunkhumpornpat:2009} and \textsc{ln}-\textsc{smote} \cite{Maciejewski:2011} reduce the probability of generating synthetic instances of the minority class in areas where the predominant objects are that of the majority class.
+It is worth noticing that our team proposed two novel solutions to this problem: \textsc{rbo} \cite{koziarski2017radial} and \textsc{ccr} that enforce instances from the majority-class to be relocated from the areas where the minority-class instances are present \cite{Koziarski:2017amcs}.
+Methods of \emph{undersampling} are built around the idea of randomly removing the instances from the majority-class or removing them from the areas in such way that the  quality of the classifier is not disrupted using neighbor analysis.%\todo{W opisie metod przetwarzania wstępnego skupiamy się chyba wyłącznie na \emph{oversamplingu}.}\todo{Nie uwzględniłem czystego losowego \emph{oversamplingu}, bo skoro powtarza istniejące już obiekty, to ilustracja byłaby bezsensowna.}
+
+%\begin{figure}[hbt]
+%\centering
+%\includegraphics[width=.9\linewidth]{figures/smote}
+%\caption{Example of oversampling using \textsc{smote}}
+%\end{figure}
+
+\noindent\textbf{ Inbuilt mechanisms.} In this approach existing classification algorithms are adapted for imbalanced problems ensuring balanced accuracy for instances from both classes.
+Two of the most popular areas of research of this methods are using one-class classification  \cite{Japkowicz:1995}, usually known as learning without counterexamples, where the goal is to learn the minority class decision areas and because of the frequently assumed regular, closed shape of the decision borders is adequate to the clusters created by minority classes \cite{Krawczyk:2014ins}.
+The disproportion between the number of instances in classes is then omitted.
+Another approach is the (\textit{cost sensitive}) classification, where the algorithm takes into account the asymmetrical loss function that assigns a higher cost to a misclassification of an instance form a minority class \cite{Krawczyk:2014,Lopez:2012,He:2009,Zhou:2006}.
+Unfortunately such methods can cause a reverse bias towards the minority class.
+Worth noting are methods based on ensemble classification \cite{Wozniak:2014}, like \emph{\textsc{smote}Boost} \cite{Chawla:2003} and \emph{AdaBoost.NC} \cite{Wang:2010}%, or \emph{Multi-objective Genetic Programing Ensemble} \cite{Bhowan:2013}.
+
+\noindent\textbf{Hybrid methods.} They combine the advantages of methods using data pre-processing with the classification methods.
+The most popular category is the hybridisation of \emph{under-} and \emph{oversampling} with ensemble classifiers \cite{Galar:2012}.
+This approach allows the data to be independently  processed for each of the base model.
+Algorithms formed on modifications of \emph{Bagging} and \emph{Boosting} \cite{Chawla:2003} enjoy wide popularity.
+
+The main contributions of this work are:
+
+%%%
+%%% Introduction
+%%%
+\section{Homogenous ensemble based on undersampling the majority class}
+\label{sec:intro}
+
+Zaawansowane metody oversamplingu nie są możliwe do zastosowania przy sytuacji, gdzie w zbiorze uczącym znajduje się zaledwie kilka wzorców.
+
+Idea k-foldowego podziału klasy większościowej. Wyznaczanie wartości k jako zaokrąglonego IR. Atut w postaci wykorzystania wszystkich wzorców, gdzie tworzymy komitet k zbalansowanych zbiorów.
 
@@
   {fig:teximage}
-  {\caption{Image Created Using \LaTeX\ Code}}
-  {\includeteximage[angle=45]{images/teximage}}
+  {\caption{Scheme of using k-Fold division in ensemble construction}}
+  {\includeteximage[angle=0]{figures/ensemble_scheme}}
 \end{figure}
 
-If the figure is too wide to fit on the page, you can use the
-\texttt{sidewaysfigure} environment defined in the
-\textsf{rotating} package.
+Wyliczanie wag. Accuracy się nie sprawdzi, więc BAC.
 
-Don't use \verb|\graphicspath|. If the images are contained in
-a subdirectory, specify this when you include the image, for
-example \verb|\includegraphics{figures/mypic}|.
+Jeśli klasyfikujemy nie jeden wzorzec, a wiele, wagi mogą być też dla pojedynczych próbek, dla podbicia, a więc pojawia się KONTRAST.
+Mamy takie ładne ilustracje z badań, dodajmy rysunek chociaż jeden poglądowo.
 
-\subsubsection{Sub-Figures}
-\label{sec:subfigures}
+\begin{figure}[!h]
+\floatconts
+  {fig:subfigex}
+  {\caption{Rysunek.}}
+  {%
+    \subfigure[O jaki ładny]{\label{fig:circle}%
+    \includegraphics[width=.5\linewidth, trim = 0 100 0 100,clip=true]
+    {figures/ecoli-0-1_vs_2-3-5}}%
+    \subfigure[A ten brzydki]{\label{fig:circle}%
+    \includegraphics[width=.5\linewidth, trim = 0 100 0 100,clip=true]
+    {figures/ecoli-0-3-4-6_vs_5}}%
+  }
+\end{figure}
+
+Potencjał kontrastu dla danych strumieniowych.
+
+Proponowane metody decyzyjne.
+
+\begin{itemize}
+	\item - akumulacja wsparć,
+	\item - akumulacja ważona po członkach komitetu, gdzie waga to BAC dla zbioru uczącego,
+	\item - akumulacja ważona po wzorcach, przez kontrast,
+	\item - akumulacja znormalizowanych wag członków,
+	\item - iloczyn znormalizowanych wag i kontrastu
+\end{itemize}
+
+Duża skala niezbalansowania to duża wielkość komitetu (ilustracja zależności na wykresie). Przyda się więc przycinanie (pruning).
+
+Wyjaśnienie podejścia do pruningu.
+Wyliczamy wzajemną zależność statystyczną (Wilcoxonem) pomiędzy wsparciami członków i grupujemy -- omijając kwestię 1z2 2z3 ale nie 1z3 -- je uśredniając wsparcia w obrębie grupy.
+Uśredniamy też wagi i tworzymy tak dwupoziomowy system fuzji (potrzebna ilustracja).
+
+Pruning też jest w kontekście klasyfikacji wielu wzorców na raz.
+
+Wyjaśnienie kwestii wspomnianej wcześniej i uzasadnienie pominięcia jej analizy.
+
+%%%
+%%% Introduction
+%%%
+\section{Experiment design}
+\label{sec:intro}
+
+Wybrane zbiory danych.
+
+Wykorzystane klasyfikatory bazowe.
+Wyjaśnienie dlaczego odrzuciliśmy MLP (brak konwergencji na bardzo niewielkich zbiorach) i SVC (nie jest on naturalnie probabilistyczny, a jego probabilistyczna interpretacja jest silnie zakłamana przy niewielkich zbiorach danych).
+Stąd bierzemy GNB, kNN i DT, przy domyślnych parametrach z sklearn.
+
+Powównawczo uczenie na pełnym zbiorze i zbiorach po pojedynczym under i oversamplingu.
+
+Undersampling, ze względu na niestabilność, powtórzony pięciokrotnie na każdym foldzie.
+
+Zastosowana metoda podziału -- wymuszone przez KEEL k-fold CV (z k=5).
+
+Zastosowana miara jakości -- zbalansowana dokładność, wymierna w niezbalansowanych danych.
+
+Zastosowana analiza statystyczna -- parowa zależność pomiędzy klasyfikatorem z najwyższym rezultatem a pozostałymi w postaci testu Wilcoxona.
+
+Przygotowane oprogramowanie ze wskazaniem repozytorium.
+
+%%%
+%%% Introduction
+%%%
+\section{Experimental evaluation}
+\label{sec:intro}
+
+Przedstawienie tabel.
 
 \begin{sidewaystable}
-\scriptsize
-\centering
-\setlength{\tabcolsep}{3.5pt}
-\def\arraystretch{1.15}
-\begin{tabular}{@{}|ccccc|ccccc||ccccc|ccccc||ccc|r|}\hline%
-
-\multicolumn{10}{|c||}{\multirow{2}{*}{\bfseries Without oversampled set}} &
-\multicolumn{10}{ c||}{\multirow{2}{*}{\bfseries With oversampled set}} &
-\multirow{5}{*}{\rotatebox[origin=c]{-90}{\bfseries OS}} &
-\multirow{5}{*}{\rotatebox[origin=c]{-90}{\bfseries US}} &
-\multirow{5}{*}{\rotatebox[origin=c]{-90}{\bfseries Full}} &
-\multirow{5}{*}{\rotatebox[origin=c]{-90}{\bfseries Dataset}}
-
-\\
-\multicolumn{10}{|c||}{}&
-\multicolumn{10}{c||}{}&
-\multicolumn{3}{c|}{}&
-
-	 \\
-
-	\multicolumn{5}{|c|}{\bfseries All members} &
-	\multicolumn{5}{c||}{\bfseries Reduced members} &
-	\multicolumn{5}{c|}{\bfseries All members} &
-	\multicolumn{5}{c||}{\bfseries Reduced members} 
-	& & & & \\
-
-	\multirow{2}{*}{\rotatebox[origin=c]{-90}{\textsc{reg}}} &
-	\multirow{2}{*}{\rotatebox[origin=c]{-90}{\textsc{wei}}} &
-	\multirow{2}{*}{\rotatebox[origin=c]{-90}{\textsc{con}}} &
-	\multirow{2}{*}{\rotatebox[origin=c]{-90}{\textsc{nor}}} &
-	\multirow{2}{*}{\rotatebox[origin=c]{-90}{\textsc{nc}}} &
-
-	\multirow{2}{*}{\rotatebox[origin=c]{-90}{\textsc{reg}}} &
-	\multirow{2}{*}{\rotatebox[origin=c]{-90}{\textsc{wei}}} &
-	\multirow{2}{*}{\rotatebox[origin=c]{-90}{\textsc{con}}} &
-	\multirow{2}{*}{\rotatebox[origin=c]{-90}{\textsc{nor}}} &
-	\multirow{2}{*}{\rotatebox[origin=c]{-90}{\textsc{nc}}} &
-
-	\multirow{2}{*}{\rotatebox[origin=c]{-90}{\textsc{reg}}} &
-	\multirow{2}{*}{\rotatebox[origin=c]{-90}{\textsc{wei}}} &
-	\multirow{2}{*}{\rotatebox[origin=c]{-90}{\textsc{con}}} &
-	\multirow{2}{*}{\rotatebox[origin=c]{-90}{\textsc{nor}}} &
-	\multirow{2}{*}{\rotatebox[origin=c]{-90}{\textsc{nc}}} &
-
-	\multirow{2}{*}{\rotatebox[origin=c]{-90}{\textsc{reg}}} &
-	\multirow{2}{*}{\rotatebox[origin=c]{-90}{\textsc{wei}}} &
-	\multirow{2}{*}{\rotatebox[origin=c]{-90}{\textsc{con}}} &
-	\multirow{2}{*}{\rotatebox[origin=c]{-90}{\textsc{nor}}} &
-	\multirow{2}{*}{\rotatebox[origin=c]{-90}{\textsc{nc}}}
-
-	& & & &
-
-	\\
-
-	&&&&&&&&&&&&&&&&&&&&&&&
-	\\\hline\hline
-
-	\csvreader[head to column names,
-	           late after line=\csvifoddrow{\\}{\\\rowcolor{gray!10!white}},
-	           late after last line = \\\hline]
-	{results/GNB.csv}{}%
-	{
-
-	\ereg & \ewei & \ecwei & \enwei & \encwei &
-	\eregr & \eweir & \ecweir & \enweir & \encweir &
-	\eregos & \eweios & \ecweios & \enweios & \encweios & 
-	\eregros & \eweiros & \ecweiros & \enweiros & \encweiros &
-	\os & \us & \reg &
-
-	\multicolumn{1}{l|}{\emph{\dataset}}
-
-	}%
-\end{tabular}
-\caption{Balanced accuracy scores obtained using \textsc{gnb} as a base classifier}
+	\restable{GNB}{\textsc{gnb}}
 \end{sidewaystable}
@@
 \begin{sidewaystable}
-\scriptsize
-\centering
-\setlength{\tabcolsep}{3.5pt}
-\def\arraystretch{1.15}
-\begin{tabular}{@{}|ccccc|ccccc||ccccc|ccccc||ccc|r|}\hline%
-
-\multicolumn{10}{|c||}{\multirow{2}{*}{\bfseries Without oversampled set}} &
-\multicolumn{10}{ c||}{\multirow{2}{*}{\bfseries With oversampled set}} &
-\multirow{5}{*}{\rotatebox[origin=c]{-90}{\bfseries OS}} &
-\multirow{5}{*}{\rotatebox[origin=c]{-90}{\bfseries US}} &
-\multirow{5}{*}{\rotatebox[origin=c]{-90}{\bfseries Full}} &
-\multirow{5}{*}{\rotatebox[origin=c]{-90}{\bfseries Dataset}}
-
-\\
-\multicolumn{10}{|c||}{}&
-\multicolumn{10}{c||}{}&
-\multicolumn{3}{c|}{}&
-
-	 \\
-
-	\multicolumn{5}{|c|}{\bfseries All members} &
-	\multicolumn{5}{c||}{\bfseries Reduced members} &
-	\multicolumn{5}{c|}{\bfseries All members} &
-	\multicolumn{5}{c||}{\bfseries Reduced members} 
-	& & & & \\
-
-	\multirow{2}{*}{\rotatebox[origin=c]{-90}{\textsc{reg}}} &
-	\multirow{2}{*}{\rotatebox[origin=c]{-90}{\textsc{wei}}} &
-	\multirow{2}{*}{\rotatebox[origin=c]{-90}{\textsc{con}}} &
-	\multirow{2}{*}{\rotatebox[origin=c]{-90}{\textsc{nor}}} &
-	\multirow{2}{*}{\rotatebox[origin=c]{-90}{\textsc{nc}}} &
-
-	\multirow{2}{*}{\rotatebox[origin=c]{-90}{\textsc{reg}}} &
-	\multirow{2}{*}{\rotatebox[origin=c]{-90}{\textsc{wei}}} &
-	\multirow{2}{*}{\rotatebox[origin=c]{-90}{\textsc{con}}} &
-	\multirow{2}{*}{\rotatebox[origin=c]{-90}{\textsc{nor}}} &
-	\multirow{2}{*}{\rotatebox[origin=c]{-90}{\textsc{nc}}} &
-
-	\multirow{2}{*}{\rotatebox[origin=c]{-90}{\textsc{reg}}} &
-	\multirow{2}{*}{\rotatebox[origin=c]{-90}{\textsc{wei}}} &
-	\multirow{2}{*}{\rotatebox[origin=c]{-90}{\textsc{con}}} &
-	\multirow{2}{*}{\rotatebox[origin=c]{-90}{\textsc{nor}}} &
-	\multirow{2}{*}{\rotatebox[origin=c]{-90}{\textsc{nc}}} &
-
-	\multirow{2}{*}{\rotatebox[origin=c]{-90}{\textsc{reg}}} &
-	\multirow{2}{*}{\rotatebox[origin=c]{-90}{\textsc{wei}}} &
-	\multirow{2}{*}{\rotatebox[origin=c]{-90}{\textsc{con}}} &
-	\multirow{2}{*}{\rotatebox[origin=c]{-90}{\textsc{nor}}} &
-	\multirow{2}{*}{\rotatebox[origin=c]{-90}{\textsc{nc}}}
-
-	& & & &
-
-	\\
-
-	&&&&&&&&&&&&&&&&&&&&&&&
-	\\\hline\hline
-
-	\csvreader[head to column names,
-	           late after line=\csvifoddrow{\\}{\\\rowcolor{gray!10!white}},
-	           late after last line = \\\hline]
-	{results/kNN.csv}{}%
-	{
-
-	\ereg & \ewei & \ecwei & \enwei & \encwei &
-	\eregr & \eweir & \ecweir & \enweir & \encweir &
-	\eregos & \eweios & \ecweios & \enweios & \encweios & 
-	\eregros & \eweiros & \ecweiros & \enweiros & \encweiros &
-	\os & \us & \reg &
-
-	\multicolumn{1}{l|}{\emph{\dataset}}
-
-	}%
-\end{tabular}
-\caption{Balanced accuracy scores obtained using \textsc{knn} as a base classifier}
+	\restable{kNN}{k\textsc{nn}}
 \end{sidewaystable}
@@
 \begin{sidewaystable}
-\scriptsize
-\centering
-\setlength{\tabcolsep}{3.5pt}
-\def\arraystretch{1.15}
-\begin{tabular}{@{}|ccccc|ccccc||ccccc|ccccc||ccc|r|}\hline%
-
-\multicolumn{10}{|c||}{\multirow{2}{*}{\bfseries Without oversampled set}} &
-\multicolumn{10}{ c||}{\multirow{2}{*}{\bfseries With oversampled set}} &
-\multirow{5}{*}{\rotatebox[origin=c]{-90}{\bfseries OS}} &
-\multirow{5}{*}{\rotatebox[origin=c]{-90}{\bfseries US}} &
-\multirow{5}{*}{\rotatebox[origin=c]{-90}{\bfseries Full}} &
-\multirow{5}{*}{\rotatebox[origin=c]{-90}{\bfseries Dataset}}
-
-\\
-\multicolumn{10}{|c||}{}&
-\multicolumn{10}{c||}{}&
-\multicolumn{3}{c|}{}&
-
-	 \\
-
-	\multicolumn{5}{|c|}{\bfseries All members} &
-	\multicolumn{5}{c||}{\bfseries Reduced members} &
-	\multicolumn{5}{c|}{\bfseries All members} &
-	\multicolumn{5}{c||}{\bfseries Reduced members} 
-	& & & & \\
-
-	\multirow{2}{*}{\rotatebox[origin=c]{-90}{\textsc{reg}}} &
-	\multirow{2}{*}{\rotatebox[origin=c]{-90}{\textsc{wei}}} &
-	\multirow{2}{*}{\rotatebox[origin=c]{-90}{\textsc{con}}} &
-	\multirow{2}{*}{\rotatebox[origin=c]{-90}{\textsc{nor}}} &
-	\multirow{2}{*}{\rotatebox[origin=c]{-90}{\textsc{nc}}} &
-
-	\multirow{2}{*}{\rotatebox[origin=c]{-90}{\textsc{reg}}} &
-	\multirow{2}{*}{\rotatebox[origin=c]{-90}{\textsc{wei}}} &
-	\multirow{2}{*}{\rotatebox[origin=c]{-90}{\textsc{con}}} &
-	\multirow{2}{*}{\rotatebox[origin=c]{-90}{\textsc{nor}}} &
-	\multirow{2}{*}{\rotatebox[origin=c]{-90}{\textsc{nc}}} &
-
-	\multirow{2}{*}{\rotatebox[origin=c]{-90}{\textsc{reg}}} &
-	\multirow{2}{*}{\rotatebox[origin=c]{-90}{\textsc{wei}}} &
-	\multirow{2}{*}{\rotatebox[origin=c]{-90}{\textsc{con}}} &
-	\multirow{2}{*}{\rotatebox[origin=c]{-90}{\textsc{nor}}} &
-	\multirow{2}{*}{\rotatebox[origin=c]{-90}{\textsc{nc}}} &
-
-	\multirow{2}{*}{\rotatebox[origin=c]{-90}{\textsc{reg}}} &
-	\multirow{2}{*}{\rotatebox[origin=c]{-90}{\textsc{wei}}} &
-	\multirow{2}{*}{\rotatebox[origin=c]{-90}{\textsc{con}}} &
-	\multirow{2}{*}{\rotatebox[origin=c]{-90}{\textsc{nor}}} &
-	\multirow{2}{*}{\rotatebox[origin=c]{-90}{\textsc{nc}}}
-
-	& & & &
-
-	\\
-
-	&&&&&&&&&&&&&&&&&&&&&&&
-	\\\hline\hline
-
-	\csvreader[head to column names,
-	           late after line=\csvifoddrow{\\}{\\\rowcolor{gray!10!white}},
-	           late after last line = \\\hline]
-	{results/DTC.csv}{}%
-	{
-
-	\ereg & \ewei & \ecwei & \enwei & \encwei &
-	\eregr & \eweir & \ecweir & \enweir & \encweir &
-	\eregos & \eweios & \ecweios & \enweios & \encweios & 
-	\eregros & \eweiros & \ecweiros & \enweiros & \encweiros &
-	\os & \us & \reg &
-
-	\multicolumn{1}{l|}{\emph{\dataset}}
-
-	}%
-\end{tabular}
-\caption{Balanced accuracy scores obtained using \textsc{dtc} as a base classifier}
+	\restable{DTC}{\textsc{dtc}}
 \end{sidewaystable}
 
-Sub-figures can be created using \verb|\subfigure|, which is
-defined by the \textsf{jmlr} class. The optional argument allows
-you to provide a subcaption. The label should be placed in the
-mandatory argument of \verb|\subfigure|. You can reference the
-entire figure, for example \figureref{fig:subfigex}, or you can
-reference part of the figure using \verb|\figureref|, for example
-\figureref{fig:circle}. Alternatively you can reference the
-subfigure using \verb|\subfigref|, for example
-\subfigref{fig:circle,fig:square} in \figureref{fig:subfigex}.
+Tabela zbiorcza zwycięstw w zależności od parametrów (z grupowaniem).
 
-\begin{figure}[htbp]
-\floatconts
-  {fig:subfigex}
-  {\caption{An Example With Sub-Figures.}}
-  {%
-    \subfigure[A Circle]{\label{fig:circle}%
-      \includegraphics[width=0.2\linewidth]{images/circle}}%
-    \qquad
-    \subfigure[A Square]{\label{fig:square}%
-      \includegraphics[width=0.2\linewidth]{images/square}}
+Interpretacja wyników, czyli co zostało należycie uprawdopodobnione.
+
+%%%
+%%% Conclusions
+%%%
+\section{Conclusions}
+\label{sec:intro}
+Co zostało zaproponowane.
+
+Na co pozwala taka metoda.
+
+Do jakich rezultatów doprowadziła.
+
+Jakie są plany na przyszłość (czyli co robisz w wakacje).
+
+%%%
+%%% Acknowledgements and references
+%%%
+\acks{
+	Acknowledgements go here.
 }
-\end{figure}
-
-By default, the sub-figures are aligned on the baseline.
-This can be changed using the second optional argument
-of \verb|\subfigure|. This may be \texttt{t} (top), \texttt{c}
-(centered) or \texttt{b} (bottom). For example, the subfigures
-\subfigref{fig:circle2,fig:square2} in \figureref{fig:subfigex2}
-both have \verb|[c]| as the second optional argument.
-
-\begin{figure}[htbp]
-\floatconts
-  {fig:subfigex2}
-  {\caption{Another Example With Sub-Figures.}}
-  {%
-    \subfigure[A Small Circle][c]{\label{fig:circle2}%
-      \includegraphics[width=0.1\linewidth]{images/circle}}%
-    \qquad
-    \subfigure[A Square][c]{\label{fig:square2}%
-      \includegraphics[width=0.2\linewidth]{images/square}}
-  }
-\end{figure}
-
-\subsection{Sub-Tables}
-\label{sec:subtables}
-There is an analogous command \verb|\subtable| for sub-tables.
-It has the same syntax as \verb|\subfigure| described above.
-You can reference the table using \verb|\tableref|, for example
-\tableref{tab:subtabex} or you can reference part of the table,
-for example \tableref{tab:ab}. Alternatively you can reference the
-subtable using \verb|\subtabref|, for example
-\subtabref{tab:ab,tab:cd} in \tableref{tab:subtabex}.
-
-\begin{table}[htbp]
-\floatconts
- {tab:subtabex}
- {\caption{An Example With Sub-Tables}}
- {%
-   \subtable{%
-     \label{tab:ab}%
-     \begin{tabular}{cc}
-     \bfseries A & \bfseries B\\
-     1 & 2
-     \end{tabular}
-   }\qquad
-   \subtable{%
-     \label{tab:cd}%
-     \begin{tabular}{cc}
-     \bfseries C & \bfseries D\\
-     3 & 4\\
-     5 & 6
-     \end{tabular}
-   }
- }
-\end{table}
-
-By default, the sub-tables are aligned on the top.
-This can be changed using the second optional argument
-of \verb|\subtable|. This may be \texttt{t} (top), \texttt{c}
-(centered) or \texttt{b} (bottom). For example, the sub-tables
-\subtabref{tab:ab2,tab:cd2} in \tableref{tab:subtabex2}
-both have \verb|[c]| as the second optional argument.
-
-\begin{table}[htbp]
-\floatconts
- {tab:subtabex2}
- {\caption{Another Example With Sub-Tables}}
- {%
-   \subtable[][c]{%
-     \label{tab:ab2}%
-     \begin{tabular}{cc}
-     \bfseries A & \bfseries B\\
-     1 & 2
-     \end{tabular}
-   }\qquad
-   \subtable[][c]{%
-     \label{tab:cd2}%
-     \begin{tabular}{cc}
-     \bfseries C & \bfseries D\\
-     3 & 4\\
-     5 & 6
-     \end{tabular}
-   }
- }
-\end{table}
-
-\subsection{Algorithms}
-\label{sec:algorithms}
-
-Enumerated textual algorithms can be displayed using the
-\texttt{algorithm} environment. Within this environment, use
-use an \texttt{enumerate} or nested \texttt{enumerate} environments.
-For example, see \algorithmref{alg:gauss}. Note that algorithms
-float like figures and tables.
-
-\begin{algorithm}[htbp]
-\floatconts
-{alg:gauss}% label
-{\caption{The Gauss-Seidel Algorithm}}
-{% contents
-\begin{enumerate}
-  \item For $k=1$ to maximum number of iterations
-    \begin{enumerate}
-      \item For $i=1$ to $n$
-        \begin{enumerate}
-        \item $x_i^{(k)} = 
-          \frac{b_i - \sum_{j=1}^{i-1}a_{ij}x_j^{(k)}
-          - \sum_{j=i+1}^{n}a_{ij}x_j^{(k-1)}}{a_{ii}}$
-        \item If $\|\vec{x}^{(k)}-\vec{x}^{(k-1)} < \epsilon\|$,
-          where $\epsilon$ is a specified stopping criteria, stop.
-      \end{enumerate}
-    \end{enumerate}
-\end{enumerate}
-}
-\end{algorithm}
-
-You can use \verb|\caption| and \verb|\label| without using
-\verb|\floatconts| (as in \algorithmref{alg:moore}).
-
-If you'd rather have the same numbering throughout the algorithm
-but still want the convenient indentation of nested 
-\texttt{enumerate} environments, you can use the
-\texttt{enumerate*} environment provided by the \textsf{jmlr}
-class. For example, see \algorithmref{alg:moore}.
-
-\begin{algorithm}
-\caption{Moore's Shortest Path}\label{alg:moore}
-Given a connected graph $G$, where the length of each edge is 1:
-\begin{enumerate*}
-  \item Set the label of vertex $s$ to 0
-  \item Set $i=0$
-  \begin{enumerate*}
-    \item \label{step:locate}Locate all unlabelled vertices 
-          adjacent to a vertex labelled $i$ and label them $i+1$
-    \item If vertex $t$ has been labelled,
-    \begin{enumerate*}
-      \item[] the shortest path can be found by backtracking, and 
-      the length is given by the label of $t$.
-    \end{enumerate*}
-    otherwise
-    \begin{enumerate*}
-      \item[] increment $i$ and return to step~\ref{step:locate}
-    \end{enumerate*}
-  \end{enumerate*}
-\end{enumerate*}
-\end{algorithm}
-
-Pseudo code can be displayed using the \texttt{algorithm2e}
-environment. This is defined by the \textsf{algorithm2e} package
-(which is automatically loaded) so check the \textsf{algorithm2e}
-documentation for further details.\footnote{Either \texttt{texdoc
-algorithm2e} or \url{http://www.ctan.org/pkg/algorithm2e}}
-For an example, see \algorithmref{alg:net}.
-
-\begin{algorithm2e}
-\caption{Computing Net Activation}
-\label{alg:net}
- % older versions of algorithm2e have \dontprintsemicolon instead
- % of the following:
- %\DontPrintSemicolon
- % older versions of algorithm2e have \linesnumbered instead of the
- % following:
- %\LinesNumbered
-\KwIn{$x_1, \ldots, x_n, w_1, \ldots, w_n$}
-\KwOut{$y$, the net activation}
-$y\leftarrow 0$\;
-\For{$i\leftarrow 1$ \KwTo $n$}{
-  $y \leftarrow y + w_i*x_i$\;
-}
-\end{algorithm2e}
-
-\section{Description Lists}
-
-The \textsf{jmlr} class also provides a description-like 
-environment called \texttt{altdescription}. This has an
-argument that should be the widest label in the list. Compare:
-\begin{description}
-\item[add] A method that adds two variables.
-\item[differentiate] A method that differentiates a function.
-\end{description}
-with
-\begin{altdescription}{differentiate}
-\item[add] A method that adds two variables.
-\item[differentiate] A method that differentiates a function.
-\end{altdescription}
-
-\section{Theorems, Lemmas etc}
-\label{sec:theorems}
-
-The following theorem-like environments are predefined by
-the \textsf{jmlr} class: \texttt{theorem}, \texttt{example},
-\texttt{lemma}, \texttt{proposition}, \texttt{remark}, 
-\texttt{corollary}, \texttt{definition}, \texttt{conjecture}
-and \texttt{axiom}. You can use the \texttt{proof} environment
-to display the proof if need be, as in \theoremref{thm:eigenpow}.
-
-\begin{theorem}[Eigenvalue Powers]\label{thm:eigenpow}
-If $\lambda$ is an eigenvalue of $\vec{B}$ with eigenvector
-$\vec{\xi}$, then $\lambda^n$ is an eigenvalue of $\vec{B}^n$
-with eigenvector $\vec{\xi}$.
-\begin{proof}
-Let $\lambda$ be an eigenvalue of $\vec{B}$ with eigenvector
-$\xi$, then
-\begin{align*}
-\vec{B}\vec{\xi} &= \lambda\vec{\xi}
-\intertext{premultiply by $\vec{B}$:}
-\vec{B}\vec{B}\vec{\xi} &= \vec{B}\lambda\vec{\xi}\\
-\Rightarrow \vec{B}^2\vec{\xi} &= \lambda\vec{B}\vec{\xi}\\
-&= \lambda\lambda\vec{\xi}\qquad
-\text{since }\vec{B}\vec{\xi}=\lambda\vec{\xi}\\
-&= \lambda^2\vec{\xi}
-\end{align*}
-Therefore true for $n=2$. Now assume true for $n=k$:
-\begin{align*}
-\vec{B}^k\vec{\xi} &= \lambda^k\vec{\xi}
-\intertext{premultiply by $\vec{B}$:}
-\vec{B}\vec{B}^k\vec{\xi} &= \vec{B}\lambda^k\vec{\xi}\\
-\Rightarrow \vec{B}^{k+1}\vec{\xi} &= \lambda^k\vec{B}\vec{\xi}\\
-&= \lambda^k\lambda\vec{\xi}\qquad
-\text{since }\vec{B}\vec{\xi}=\lambda\vec{\xi}\\
-&= \lambda^{k+1}\vec{\xi}
-\end{align*}
-Therefore true for $n=k+1$. Therefore, by induction, true for all
-$n$.
-\end{proof}
-\end{theorem}
-
-\begin{lemma}[A Sample Lemma]\label{lem:sample}
-This is a lemma.
-\end{lemma}
-
-\begin{remark}[A Sample Remark]\label{rem:sample}
-This is a remark.
-\end{remark}
-
-\begin{corollary}[A Sample Corollary]\label{cor:sample}
-This is a corollary.
-\end{corollary}
-
-\begin{definition}[A Sample Definition]\label{def:sample}
-This is a definition.
-\end{definition}
-
-\begin{conjecture}[A Sample Conjecture]\label{con:sample}
-This is a conjecture.
-\end{conjecture}
-
-\begin{axiom}[A Sample Axiom]\label{ax:sample}
-This is an axiom.
-\end{axiom}
-
-\begin{example}[An Example]\label{ex:sample}
-This is an example.
-\end{example}
-
-\section{Color vs Grayscale}
-\label{sec:color}
-
-It's helpful if authors supply grayscale versions of their
-images in the event that the article is to be incorporated into
-a black and white printed book. With external PDF, PNG or JPG
-graphic files, you just need to supply a grayscale version of the
-file. For example, if the file is called \texttt{myimage.png},
-then the gray version should be \texttt{myimage-gray.png} or
-\texttt{myimage-gray.pdf} or \texttt{myimage-gray.jpg}. You don't
-need to modify your code. The \textsf{jmlr} class checks for
-the existence of the grayscale version if it is print mode 
-(provided you have used \verb|\includegraphics| and haven't
-specified the file extension).
-
-You can use \verb|\ifprint| to determine which mode you are in.
-For example, in \figureref{fig:nodes}, the 
-\ifprint{dark gray}{purple} ellipse represents an input and the
-\ifprint{light gray}{yellow} ellipse represents an output.
-Another example: {\ifprint{\bfseries}{\color{red}}important text!}
-
-You can use the class option \texttt{gray} to see how the
-document will appear in gray scale mode. \textcolor{blue}{Colored
-text} will automatically be converted to gray scale.
-
-The \textsf{jmlr} class loads the \textsf{xcolor}
-package, so you can also define your own colors. For example:
-\ifprint
-  {\definecolor{myred}{gray}{0.5}}%
-  {\definecolor{myred}{rgb}{0.5,0,0}}%
-\textcolor{myred}{XYZ}.
-
-The \textsf{xcolor} class is loaded with the \texttt{x11names}
-option, so you can use any of the x11 predefined colors (listed
-in the \textsf{xcolor} documentation\footnote{either 
-\texttt{texdoc xcolor} or \url{http://www.ctan.org/pkg/xcolor}}).
-
-\section{Citations and Bibliography}
-\label{sec:cite}
-
-The \textsf{jmlr} class automatically loads \textsf{natbib}.
-This sample file has the citations defined in the accompanying
-BibTeX file \texttt{jmlr-sample.bib}. For a parenthetical
-citation use \verb|\citep|. For example
-\citep{guyon-elisseeff-03}. For a textual citation use
-\verb|\citet|. For example \citet{guyon2007causalreport}.
-Both commands may take a comma-separated list, for example
-\citet{guyon-elisseeff-03,guyon2007causalreport}.
-
-These commands have optional arguments and have a starred
-version. See the \textsf{natbib} documentation for further
-details.\footnote{Either \texttt{texdoc natbib} or
-\url{http://www.ctan.org/pkg/natbib}}
-
-The bibliography is displayed using \verb|\bibliography|.
-
-\acks{Acknowledgements go here.}
-
 \bibliography{bibliography}
 
-\appendix
-
-\section{First Appendix}\label{apd:first}
-
-This is the first appendix.
-
-\section{Second Appendix}\label{apd:second}
-
-This is the second appendix.
-
 \end{document}

### 2018-07-08 figures/ensemble_scheme.tex
Scheme.

\frame{\begin{picture}(100,100)
\put(25,50){\dashbox{.5}(10,10){$C$}}
\put(50,50){\dashbox{.5}(10,10){$B$}}
\end{picture}}

### 2018-07-08 samples.tex
Scheme.

\documentclass[pmlr]{jmlr}
\input{_head}
%TODO: Max 14 pages
%TODO: No personal information or reference to the authors should be introduced in the submitted paper.
%TODO: Submissions will be evaluated concerning their technical quality, relevance, significance, originality and clarity.

\title
[Fusers in homogenous ensemble of subsampled majority class]
{
	Fusers in homogenous ensemble of subsampled majority class for highly imbalanced data classification%\titlebreak
}

\begin{document}

\maketitle

\begin{abstract}
This is the abstract for this article.
\end{abstract}
\begin{keywords}
classification, classifier ensemble, undersampling, imbalanced data
\end{keywords}

%%%
%%% Introduction
%%%
\section{Conclusions}
\label{sec:intro}

This is a sample article that uses the \textsf{jmlr} class with
the \texttt{wcp} class option.  Please follow the guidelines in
this sample document as it can help to reduce complications when
combining the articles into a book. Please avoid using obsolete
commands, such as \verb|\rm|, and obsolete packages, such as
\textsf{epsfig}.\footnote{See
\url{http://www.ctan.org/pkg/l2tabu}}

Please also ensure that your document will compile with PDF\LaTeX.
If you have an error message that's puzzling you, first check for it
at the UK TUG FAQ
\url{http://www.tex.ac.uk/cgi-bin/texfaq2html?label=man-latex}.  If
that doesn't help, create a minimal working example (see
\url{http://theoval.cmp.uea.ac.uk/~nlct/latex/minexample/}) and post
to somewhere like TeX on StackExchange
(\url{http://tex.stackexchange.com/}) or the LaTeX Community Forum
(\url{http://www.latex-community.org/forum/}).

\begin{note}
This is an numbered theorem-like environment that was defined in
this document's preamble.
\end{note}

\subsection{Sub-sections}

Sub-sections are produced using \verb|\subsection|.

\subsubsection{Sub-sub-sections}

Sub-sub-sections are produced using \verb|\subsubsection|.

\paragraph{Sub-sub-sub-sections}

Sub-sub-sub-sections are produced using \verb|\paragraph|.
These are unnumbered with a running head.

\subparagraph{Sub-sub-sub-sub-sections}

Sub-sub-sub-sub-sections are produced using \verb|\subparagraph|.
These are unnumbered with a running head.

\section{Cross-Referencing}

Always use \verb|\label| and \verb|\ref| (or one of the commands
described below) when cross-referencing.  For example, the next
section is Section~\ref{sec:math}. The \textsf{jmlr} class
provides some convenient cross-referencing commands:
\verb|\sectionref|, \verb|\equationref|, \verb|\tableref|,
\verb|\figureref|, \verb|\algorithmref|, \verb|\theoremref|,
\verb|\lemmaref|, \verb|\remarkref|, \verb|\corollaryref|,
\verb|\definitionref|, \verb|\conjectureref|, \verb|\axiomref|,
\verb|\exampleref| and \verb|\appendixref|. The argument of these
commands may either be a single label or a comma-separated list
of labels. Examples:

Referencing sections: \sectionref{sec:math} or
\sectionref{sec:intro,sec:math} or
\sectionref{sec:intro,sec:math,sec:tables,sec:figures}.

Referencing equations: \equationref{eq:trigrule} or
\equationref{eq:trigrule,eq:df} or
\equationref{eq:trigrule,eq:f,eq:df,eq:y}.

Referencing tables: \tableref{tab:operatornames} or
\tableref{tab:operatornames,tab:example} or
\tableref{tab:operatornames,tab:example,tab:example-booktabs}.

Referencing figures: \figureref{fig:nodes} or
\figureref{fig:nodes,fig:teximage} or
\figureref{fig:nodes,fig:teximage,fig:subfigex} or
\figureref{fig:circle,fig:square}.

Referencing algorithms: \algorithmref{alg:gauss} or
\algorithmref{alg:gauss,alg:moore} or
\algorithmref{alg:gauss,alg:moore,alg:net}.

Referencing theorem-like environments: \theoremref{thm:eigenpow},
\lemmaref{lem:sample}, \remarkref{rem:sample}, 
\corollaryref{cor:sample}, \definitionref{def:sample},
\conjectureref{con:sample}, \axiomref{ax:sample} and
\exampleref{ex:sample}.

Referencing appendices: \appendixref{apd:first} or
\appendixref{apd:first,apd:second}.

\section{Equations}
\label{sec:math}

The \textsf{jmlr} class loads the \textsf{amsmath} package, so
you can use any of the commands and environments defined there.
(See the \textsf{amsmath} documentation for further
details.\footnote{Either \texttt{texdoc amsmath} or
\url{http://www.ctan.org/pkg/amsmath}})

Unnumbered single-lined equations should be displayed using
\verb|\[| and \verb|\]|. For example:
\[E = m c^2\]
Numbered single-line equations should be displayed using the
\texttt{equation} environment. For example:
\begin{equation}\label{eq:trigrule}
\cos^2\theta + \sin^2\theta \equiv 1
\end{equation}
This can be referenced using \verb|\label| and \verb|\equationref|.
For example, \equationref{eq:trigrule}.

Multi-lined numbered equations should be displayed using the
\texttt{align} environment.\footnote{For reasons why you 
shouldn't use the obsolete \texttt{eqnarray} environment, see
Lars Madsen, \emph{Avoid eqnarray!} TUGboat 33(1):21--25, 2012.} For example:
\begin{align}
f(x) &= x^2 + x\label{eq:f}\\
f'(x) &= 2x + 1\label{eq:df}
\end{align}
Unnumbered multi-lined equations should be displayed using the
\texttt{align*} environment. For example:
\begin{align*}
f(x) &= (x+1)(x-1)\\
&= x^2 - 1
\end{align*}
If you want to mix numbered with unnumbered lines use the
align environment and suppress unwanted line numbers with
\verb|\nonumber|. For example:
\begin{align}
y &= x^2 + 3x - 2x + 1\nonumber\\
&= x^2 + x + 1\label{eq:y}
\end{align}
An equation that is too long to fit on a single line can be
displayed using the \texttt{split} environment. 
Text can be embedded in an equation using \verb|\text| or
\verb|\intertext| (as used in \theoremref{thm:eigenpow}).
See the \textsf{amsmath} documentation for further details.

\subsection{Operator Names}
\label{sec:op}

Predefined operator names are listed in \tableref{tab:operatornames}.
For additional operators, either use \verb|\operatorname|,
for example $\operatorname{var}(X)$ or declare it with
\verb|\DeclareMathOperator|, for example
\begin{verbatim}
\DeclareMathOperator{\var}{var}
\end{verbatim}
and then use this new command. If you want limits that go above and
below the operator (like \verb|\sum|) use the starred versions
(\verb|\operatorname*| or \verb|\DeclareMathOperator*|).

\begin{table}[htbp]
\floatconts
  {tab:operatornames}%
  {\caption{Predefined Operator Names (taken from 
   \textsf{amsmath} documentation)}}%
  {%
\begin{tabular}{rlrlrlrl}
\cs{arccos} & $\arccos$ &  \cs{deg} & $\deg$ &  \cs{lg} & $\lg$ &  \cs{projlim} & $\projlim$ \\
\cs{arcsin} & $\arcsin$ &  \cs{det} & $\det$ &  \cs{lim} & $\lim$ &  \cs{sec} & $\sec$ \\
\cs{arctan} & $\arctan$ &  \cs{dim} & $\dim$ &  \cs{liminf} & $\liminf$ &  \cs{sin} & $\sin$ \\
\cs{arg} & $\arg$ &  \cs{exp} & $\exp$ &  \cs{limsup} & $\limsup$ &  \cs{sinh} & $\sinh$ \\
\cs{cos} & $\cos$ &  \cs{gcd} & $\gcd$ &  \cs{ln} & $\ln$ &  \cs{sup} & $\sup$ \\
\cs{cosh} & $\cosh$ &  \cs{hom} & $\hom$ &  \cs{log} & $\log$ &  \cs{tan} & $\tan$ \\
\cs{cot} & $\cot$ &  \cs{inf} & $\inf$ &  \cs{max} & $\max$ &  \cs{tanh} & $\tanh$ \\
\cs{coth} & $\coth$ &  \cs{injlim} & $\injlim$ &  \cs{min} & $\min$ \\
\cs{csc} & $\csc$ &  \cs{ker} & $\ker$ &  \cs{Pr} & $\Pr$
\end{tabular}\par
\begin{tabular}{rlrl}
\cs{varlimsup} & $\varlimsup$ 
& \cs{varinjlim} & $\varinjlim$\\
\cs{varliminf} & $\varliminf$ 
& \cs{varprojlim} & $\varprojlim$
\end{tabular}
}
\end{table}

\section{Vectors and Sets}
\label{sec:vec}

Vectors should be typeset using \cs{vec}. For example $\vec{x}$.
The \textsf{jmlr} class also provides \cs{set} to typeset a
set. For example $\set{S}$.

\section{Floats}
\label{sec:floats}

Floats, such as figures, tables and algorithms, are moving
objects and are supposed to float to the nearest convenient
location. Please don't force them to go in a particular place. In
general it's best to use the \texttt{htbp} specifier and don't
put the figure or table in the middle of a paragraph (that is
make sure there's a paragraph break above and below the float).
Floats are supposed to have a little extra space above and below
them to make them stand out from the rest of the text. This extra
spacing is put in automatically and shouldn't need modifying.

To ensure consistency, please \emph{don't} try changing the format of the caption by doing
something like:
\begin{verbatim}
\caption{\textit{A Sample Caption.}}
\end{verbatim}
or
\begin{verbatim}
\caption{\em A Sample Caption.}
\end{verbatim}
You can, of course, change the font for individual words or 
phrases, for example:
\begin{verbatim}
\caption{A Sample Caption With Some \emph{Emphasized Words}.}
\end{verbatim}

\subsection{Tables}
\label{sec:tables}

Tables should go in the \texttt{table} environment. Within this
environment use \verb|\floatconts| (defined by \textsf{jmlr})
to set the caption correctly and center the table contents.

\begin{table}[htbp]
 % The first argument is the label.
 % The caption goes in the second argument, and the table contents
 % go in the third argument.
\floatconts
  {tab:example}%
  {\caption{An Example Table}}%
  {\begin{tabular}{ll}
  \bfseries Dataset & \bfseries Result\\
  Data1 & 0.12345\\
  Data2 & 0.67890\\
  Data3 & 0.54321\\
  Data4 & 0.09876
  \end{tabular}}
\end{table}

If you want horizontal rules you can use the \textsf{booktabs}
package which provides the commands \verb|\toprule|, 
\verb|\midrule| and \verb|\bottomrule|. For example, see
\tableref{tab:example-booktabs}.

\begin{table}[hbtp]
\floatconts
  {tab:example-booktabs}
  {\caption{A Table With Horizontal Lines}}
  {\begin{tabular}{ll}
  \toprule
  \bfseries Dataset & \bfseries Result\\
  \midrule
  Data1 & 0.12345\\
  Data2 & 0.67890\\
  Data3 & 0.54321\\
  Data4 & 0.09876\\
  \bottomrule
  \end{tabular}}
\end{table}

If you want vertical lines as well, you can't use the
\textsf{booktabs} commands as there'll be some unwanted gaps.
Instead you can use \LaTeX's \verb|\hline|, but the rows may
appear a bit cramped.  You can add extra space above or below a
row using \verb|\abovestrut| and \verb|\belowstrut|. For example,
see \tableref{tab:example-hline}.

\begin{table}[htbp]
\floatconts
  {tab:example-hline}
  {\caption{A Table With Horizontal and Vertical Lines}}%
  {%
    \begin{tabular}{|l|l|}
    \hline
    \abovestrut{2.2ex}\bfseries Dataset & \bfseries Result\\\hline
    \abovestrut{2.2ex}Data1 & 0.12345\\
    Data2 & 0.67890\\
    Data3 & 0.54321\\
    \belowstrut{0.2ex}Data4 & 0.09876\\\hline
    \end{tabular}
  }
\end{table}

If you want to align numbers on their decimal point, you can
use the \textsf{siunitx} package. For example, see
\tableref{tab:example-siunitx}. For further details see the
\textsf{siunitx} documentation\footnote{Either \texttt{texdoc
siunitx} or \url{http://www.ctan.org/pkg/siunitx}}.

\begin{table}[htbp]
\floatconts
  {tab:example-siunitx}
  {\caption{A Table With Numbers Aligned on the Decimal Point}}
  {\begin{tabular}{lS[tabformat=3.5]}
  \bfseries Dataset & {\bfseries Result}\\
  Data1 & 0.12345\\
  Data2 & 10.6789\\
  Data3 & 50.543\\
  Data4 & 200.09876
  \end{tabular}}
\end{table}

If the table is too wide, you can adjust the inter-column
spacing by changing the value of \verb|\tabcolsep|. For
example:
\begin{verbatim}
\setlength{\tabcolsep}{3pt}
\end{verbatim}
If the table is very wide but not very long, you can use the
\texttt{sidewaystable} environment defined in the
\textsf{rotating} package (so use \verb|\usepackage{rotating}|).
If the table is too long to fit on a page, you should use the
\texttt{longtable} environment defined in the \textsf{longtable}
package (so use \verb|\usepackage{longtable}|).

\subsection{Figures}
\label{sec:figures}

Figures should go in the \texttt{figure} environment. Within this
environment, use \verb|\floatconts| to correctly position the
caption and center the image. Use \verb|\includegraphics|
for external graphics files but omit the file extension. Do not
use \verb|\epsfig| or \verb|\psfig|. If you want to scale the
image, it's better to use a fraction of the line width rather
than an explicit length. For example, see \figureref{fig:nodes}.

\begin{figure}[htbp]
 % Caption and label go in the first argument and the figure contents
 % go in the second argument
\floatconts
  {fig:nodes}
  {\caption{Example Image}}
  {\includegraphics[width=0.5\linewidth]{images/nodes}}
\end{figure}

If your image is made up of \LaTeX\ code (for example, commands
provided by the \textsf{pgf} package) you can include it using
\cs{includeteximage} (defined by the \textsf{jmlr} class). This
can be scaled and rotated in the same way as \cs{includegraphics}.
For example, see \figureref{fig:teximage}.

\begin{figure}[htbp]
\floatconts
  {fig:teximage}
  {\caption{Image Created Using \LaTeX\ Code}}
  {\includeteximage[angle=45]{images/teximage}}
\end{figure}

If the figure is too wide to fit on the page, you can use the
\texttt{sidewaysfigure} environment defined in the
\textsf{rotating} package.

Don't use \verb|\graphicspath|. If the images are contained in
a subdirectory, specify this when you include the image, for
example \verb|\includegraphics{figures/mypic}|.

\subsubsection{Sub-Figures}
\label{sec:subfigures}

\begin{sidewaystable}
\scriptsize
\centering
\setlength{\tabcolsep}{3.5pt}
\def\arraystretch{1.15}
\begin{tabular}{@{}|ccccc|ccccc||ccccc|ccccc||ccc|r|}\hline%

\multicolumn{10}{|c||}{\multirow{2}{*}{\bfseries Without oversampled set}} &
\multicolumn{10}{ c||}{\multirow{2}{*}{\bfseries With oversampled set}} &
\multirow{5}{*}{\rotatebox[origin=c]{-90}{\bfseries OS}} &
\multirow{5}{*}{\rotatebox[origin=c]{-90}{\bfseries US}} &
\multirow{5}{*}{\rotatebox[origin=c]{-90}{\bfseries Full}} &
\multirow{5}{*}{\rotatebox[origin=c]{-90}{\bfseries Dataset}}

\\
\multicolumn{10}{|c||}{}&
\multicolumn{10}{c||}{}&
\multicolumn{3}{c|}{}&

	 \\

	\multicolumn{5}{|c|}{\bfseries All members} &
	\multicolumn{5}{c||}{\bfseries Reduced members} &
	\multicolumn{5}{c|}{\bfseries All members} &
	\multicolumn{5}{c||}{\bfseries Reduced members} 
	& & & & \\

	\multirow{2}{*}{\rotatebox[origin=c]{-90}{\textsc{reg}}} &
	\multirow{2}{*}{\rotatebox[origin=c]{-90}{\textsc{wei}}} &
	\multirow{2}{*}{\rotatebox[origin=c]{-90}{\textsc{con}}} &
	\multirow{2}{*}{\rotatebox[origin=c]{-90}{\textsc{nor}}} &
	\multirow{2}{*}{\rotatebox[origin=c]{-90}{\textsc{nc}}} &

	\multirow{2}{*}{\rotatebox[origin=c]{-90}{\textsc{reg}}} &
	\multirow{2}{*}{\rotatebox[origin=c]{-90}{\textsc{wei}}} &
	\multirow{2}{*}{\rotatebox[origin=c]{-90}{\textsc{con}}} &
	\multirow{2}{*}{\rotatebox[origin=c]{-90}{\textsc{nor}}} &
	\multirow{2}{*}{\rotatebox[origin=c]{-90}{\textsc{nc}}} &

	\multirow{2}{*}{\rotatebox[origin=c]{-90}{\textsc{reg}}} &
	\multirow{2}{*}{\rotatebox[origin=c]{-90}{\textsc{wei}}} &
	\multirow{2}{*}{\rotatebox[origin=c]{-90}{\textsc{con}}} &
	\multirow{2}{*}{\rotatebox[origin=c]{-90}{\textsc{nor}}} &
	\multirow{2}{*}{\rotatebox[origin=c]{-90}{\textsc{nc}}} &

	\multirow{2}{*}{\rotatebox[origin=c]{-90}{\textsc{reg}}} &
	\multirow{2}{*}{\rotatebox[origin=c]{-90}{\textsc{wei}}} &
	\multirow{2}{*}{\rotatebox[origin=c]{-90}{\textsc{con}}} &
	\multirow{2}{*}{\rotatebox[origin=c]{-90}{\textsc{nor}}} &
	\multirow{2}{*}{\rotatebox[origin=c]{-90}{\textsc{nc}}}

	& & & &

	\\

	&&&&&&&&&&&&&&&&&&&&&&&
	\\\hline\hline

	\csvreader[head to column names,
	           late after line=\csvifoddrow{\\}{\\\rowcolor{gray!10!white}},
	           late after last line = \\\hline]
	{results/GNB.csv}{}%
	{

	\ereg & \ewei & \ecwei & \enwei & \encwei &
	\eregr & \eweir & \ecweir & \enweir & \encweir &
	\eregos & \eweios & \ecweios & \enweios & \encweios & 
	\eregros & \eweiros & \ecweiros & \enweiros & \encweiros &
	\os & \us & \reg &

	\multicolumn{1}{l|}{\emph{\dataset}}

	}%
\end{tabular}
\caption{Balanced accuracy scores obtained using \textsc{gnb} as a base classifier}
\end{sidewaystable}

\begin{sidewaystable}
\scriptsize
\centering
\setlength{\tabcolsep}{3.5pt}
\def\arraystretch{1.15}
\begin{tabular}{@{}|ccccc|ccccc||ccccc|ccccc||ccc|r|}\hline%

\multicolumn{10}{|c||}{\multirow{2}{*}{\bfseries Without oversampled set}} &
\multicolumn{10}{ c||}{\multirow{2}{*}{\bfseries With oversampled set}} &
\multirow{5}{*}{\rotatebox[origin=c]{-90}{\bfseries OS}} &
\multirow{5}{*}{\rotatebox[origin=c]{-90}{\bfseries US}} &
\multirow{5}{*}{\rotatebox[origin=c]{-90}{\bfseries Full}} &
\multirow{5}{*}{\rotatebox[origin=c]{-90}{\bfseries Dataset}}

\\
\multicolumn{10}{|c||}{}&
\multicolumn{10}{c||}{}&
\multicolumn{3}{c|}{}&

	 \\

	\multicolumn{5}{|c|}{\bfseries All members} &
	\multicolumn{5}{c||}{\bfseries Reduced members} &
	\multicolumn{5}{c|}{\bfseries All members} &
	\multicolumn{5}{c||}{\bfseries Reduced members} 
	& & & & \\

	\multirow{2}{*}{\rotatebox[origin=c]{-90}{\textsc{reg}}} &
	\multirow{2}{*}{\rotatebox[origin=c]{-90}{\textsc{wei}}} &
	\multirow{2}{*}{\rotatebox[origin=c]{-90}{\textsc{con}}} &
	\multirow{2}{*}{\rotatebox[origin=c]{-90}{\textsc{nor}}} &
	\multirow{2}{*}{\rotatebox[origin=c]{-90}{\textsc{nc}}} &

	\multirow{2}{*}{\rotatebox[origin=c]{-90}{\textsc{reg}}} &
	\multirow{2}{*}{\rotatebox[origin=c]{-90}{\textsc{wei}}} &
	\multirow{2}{*}{\rotatebox[origin=c]{-90}{\textsc{con}}} &
	\multirow{2}{*}{\rotatebox[origin=c]{-90}{\textsc{nor}}} &
	\multirow{2}{*}{\rotatebox[origin=c]{-90}{\textsc{nc}}} &

	\multirow{2}{*}{\rotatebox[origin=c]{-90}{\textsc{reg}}} &
	\multirow{2}{*}{\rotatebox[origin=c]{-90}{\textsc{wei}}} &
	\multirow{2}{*}{\rotatebox[origin=c]{-90}{\textsc{con}}} &
	\multirow{2}{*}{\rotatebox[origin=c]{-90}{\textsc{nor}}} &
	\multirow{2}{*}{\rotatebox[origin=c]{-90}{\textsc{nc}}} &

	\multirow{2}{*}{\rotatebox[origin=c]{-90}{\textsc{reg}}} &
	\multirow{2}{*}{\rotatebox[origin=c]{-90}{\textsc{wei}}} &
	\multirow{2}{*}{\rotatebox[origin=c]{-90}{\textsc{con}}} &
	\multirow{2}{*}{\rotatebox[origin=c]{-90}{\textsc{nor}}} &
	\multirow{2}{*}{\rotatebox[origin=c]{-90}{\textsc{nc}}}

	& & & &

	\\

	&&&&&&&&&&&&&&&&&&&&&&&
	\\\hline\hline

	\csvreader[head to column names,
	           late after line=\csvifoddrow{\\}{\\\rowcolor{gray!10!white}},
	           late after last line = \\\hline]
	{results/kNN.csv}{}%
	{

	\ereg & \ewei & \ecwei & \enwei & \encwei &
	\eregr & \eweir & \ecweir & \enweir & \encweir &
	\eregos & \eweios & \ecweios & \enweios & \encweios & 
	\eregros & \eweiros & \ecweiros & \enweiros & \encweiros &
	\os & \us & \reg &

	\multicolumn{1}{l|}{\emph{\dataset}}

	}%
\end{tabular}
\caption{Balanced accuracy scores obtained using \textsc{knn} as a base classifier}
\end{sidewaystable}

\begin{sidewaystable}
\scriptsize
\centering
\setlength{\tabcolsep}{3.5pt}
\def\arraystretch{1.15}
\begin{tabular}{@{}|ccccc|ccccc||ccccc|ccccc||ccc|r|}\hline%

\multicolumn{10}{|c||}{\multirow{2}{*}{\bfseries Without oversampled set}} &
\multicolumn{10}{ c||}{\multirow{2}{*}{\bfseries With oversampled set}} &
\multirow{5}{*}{\rotatebox[origin=c]{-90}{\bfseries OS}} &
\multirow{5}{*}{\rotatebox[origin=c]{-90}{\bfseries US}} &
\multirow{5}{*}{\rotatebox[origin=c]{-90}{\bfseries Full}} &
\multirow{5}{*}{\rotatebox[origin=c]{-90}{\bfseries Dataset}}

\\
\multicolumn{10}{|c||}{}&
\multicolumn{10}{c||}{}&
\multicolumn{3}{c|}{}&

	 \\

	\multicolumn{5}{|c|}{\bfseries All members} &
	\multicolumn{5}{c||}{\bfseries Reduced members} &
	\multicolumn{5}{c|}{\bfseries All members} &
	\multicolumn{5}{c||}{\bfseries Reduced members} 
	& & & & \\

	\multirow{2}{*}{\rotatebox[origin=c]{-90}{\textsc{reg}}} &
	\multirow{2}{*}{\rotatebox[origin=c]{-90}{\textsc{wei}}} &
	\multirow{2}{*}{\rotatebox[origin=c]{-90}{\textsc{con}}} &
	\multirow{2}{*}{\rotatebox[origin=c]{-90}{\textsc{nor}}} &
	\multirow{2}{*}{\rotatebox[origin=c]{-90}{\textsc{nc}}} &

	\multirow{2}{*}{\rotatebox[origin=c]{-90}{\textsc{reg}}} &
	\multirow{2}{*}{\rotatebox[origin=c]{-90}{\textsc{wei}}} &
	\multirow{2}{*}{\rotatebox[origin=c]{-90}{\textsc{con}}} &
	\multirow{2}{*}{\rotatebox[origin=c]{-90}{\textsc{nor}}} &
	\multirow{2}{*}{\rotatebox[origin=c]{-90}{\textsc{nc}}} &

	\multirow{2}{*}{\rotatebox[origin=c]{-90}{\textsc{reg}}} &
	\multirow{2}{*}{\rotatebox[origin=c]{-90}{\textsc{wei}}} &
	\multirow{2}{*}{\rotatebox[origin=c]{-90}{\textsc{con}}} &
	\multirow{2}{*}{\rotatebox[origin=c]{-90}{\textsc{nor}}} &
	\multirow{2}{*}{\rotatebox[origin=c]{-90}{\textsc{nc}}} &

	\multirow{2}{*}{\rotatebox[origin=c]{-90}{\textsc{reg}}} &
	\multirow{2}{*}{\rotatebox[origin=c]{-90}{\textsc{wei}}} &
	\multirow{2}{*}{\rotatebox[origin=c]{-90}{\textsc{con}}} &
	\multirow{2}{*}{\rotatebox[origin=c]{-90}{\textsc{nor}}} &
	\multirow{2}{*}{\rotatebox[origin=c]{-90}{\textsc{nc}}}

	& & & &

	\\

	&&&&&&&&&&&&&&&&&&&&&&&
	\\\hline\hline

	\csvreader[head to column names,
	           late after line=\csvifoddrow{\\}{\\\rowcolor{gray!10!white}},
	           late after last line = \\\hline]
	{results/DTC.csv}{}%
	{

	\ereg & \ewei & \ecwei & \enwei & \encwei &
	\eregr & \eweir & \ecweir & \enweir & \encweir &
	\eregos & \eweios & \ecweios & \enweios & \encweios & 
	\eregros & \eweiros & \ecweiros & \enweiros & \encweiros &
	\os & \us & \reg &

	\multicolumn{1}{l|}{\emph{\dataset}}

	}%
\end{tabular}
\caption{Balanced accuracy scores obtained using \textsc{dtc} as a base classifier}
\end{sidewaystable}

Sub-figures can be created using \verb|\subfigure|, which is
defined by the \textsf{jmlr} class. The optional argument allows
you to provide a subcaption. The label should be placed in the
mandatory argument of \verb|\subfigure|. You can reference the
entire figure, for example \figureref{fig:subfigex}, or you can
reference part of the figure using \verb|\figureref|, for example
\figureref{fig:circle}. Alternatively you can reference the
subfigure using \verb|\subfigref|, for example
\subfigref{fig:circle,fig:square} in \figureref{fig:subfigex}.

\begin{figure}[htbp]
\floatconts
  {fig:subfigex}
  {\caption{An Example With Sub-Figures.}}
  {%
    \subfigure[A Circle]{\label{fig:circle}%
      \includegraphics[width=0.2\linewidth]{images/circle}}%
    \qquad
    \subfigure[A Square]{\label{fig:square}%
      \includegraphics[width=0.2\linewidth]{images/square}}
  }
\end{figure}

By default, the sub-figures are aligned on the baseline.
This can be changed using the second optional argument
of \verb|\subfigure|. This may be \texttt{t} (top), \texttt{c}
(centered) or \texttt{b} (bottom). For example, the subfigures
\subfigref{fig:circle2,fig:square2} in \figureref{fig:subfigex2}
both have \verb|[c]| as the second optional argument.

\begin{figure}[htbp]
\floatconts
  {fig:subfigex2}
  {\caption{Another Example With Sub-Figures.}}
  {%
    \subfigure[A Small Circle][c]{\label{fig:circle2}%
      \includegraphics[width=0.1\linewidth]{images/circle}}%
    \qquad
    \subfigure[A Square][c]{\label{fig:square2}%
      \includegraphics[width=0.2\linewidth]{images/square}}
  }
\end{figure}

\subsection{Sub-Tables}
\label{sec:subtables}
There is an analogous command \verb|\subtable| for sub-tables.
It has the same syntax as \verb|\subfigure| described above.
You can reference the table using \verb|\tableref|, for example
\tableref{tab:subtabex} or you can reference part of the table,
for example \tableref{tab:ab}. Alternatively you can reference the
subtable using \verb|\subtabref|, for example
\subtabref{tab:ab,tab:cd} in \tableref{tab:subtabex}.

\begin{table}[htbp]
\floatconts
 {tab:subtabex}
 {\caption{An Example With Sub-Tables}}
 {%
   \subtable{%
     \label{tab:ab}%
     \begin{tabular}{cc}
     \bfseries A & \bfseries B\\
     1 & 2
     \end{tabular}
   }\qquad
   \subtable{%
     \label{tab:cd}%
     \begin{tabular}{cc}
     \bfseries C & \bfseries D\\
     3 & 4\\
     5 & 6
     \end{tabular}
   }
 }
\end{table}

By default, the sub-tables are aligned on the top.
This can be changed using the second optional argument
of \verb|\subtable|. This may be \texttt{t} (top), \texttt{c}
(centered) or \texttt{b} (bottom). For example, the sub-tables
\subtabref{tab:ab2,tab:cd2} in \tableref{tab:subtabex2}
both have \verb|[c]| as the second optional argument.

\begin{table}[htbp]
\floatconts
 {tab:subtabex2}
 {\caption{Another Example With Sub-Tables}}
 {%
   \subtable[][c]{%
     \label{tab:ab2}%
     \begin{tabular}{cc}
     \bfseries A & \bfseries B\\
     1 & 2
     \end{tabular}
   }\qquad
   \subtable[][c]{%
     \label{tab:cd2}%
     \begin{tabular}{cc}
     \bfseries C & \bfseries D\\
     3 & 4\\
     5 & 6
     \end{tabular}
   }
 }
\end{table}

\subsection{Algorithms}
\label{sec:algorithms}

Enumerated textual algorithms can be displayed using the
\texttt{algorithm} environment. Within this environment, use
use an \texttt{enumerate} or nested \texttt{enumerate} environments.
For example, see \algorithmref{alg:gauss}. Note that algorithms
float like figures and tables.

\begin{algorithm}[htbp]
\floatconts
{alg:gauss}% label
{\caption{The Gauss-Seidel Algorithm}}
{% contents
\begin{enumerate}
  \item For $k=1$ to maximum number of iterations
    \begin{enumerate}
      \item For $i=1$ to $n$
        \begin{enumerate}
        \item $x_i^{(k)} = 
          \frac{b_i - \sum_{j=1}^{i-1}a_{ij}x_j^{(k)}
          - \sum_{j=i+1}^{n}a_{ij}x_j^{(k-1)}}{a_{ii}}$
        \item If $\|\vec{x}^{(k)}-\vec{x}^{(k-1)} < \epsilon\|$,
          where $\epsilon$ is a specified stopping criteria, stop.
      \end{enumerate}
    \end{enumerate}
\end{enumerate}
}
\end{algorithm}

You can use \verb|\caption| and \verb|\label| without using
\verb|\floatconts| (as in \algorithmref{alg:moore}).

If you'd rather have the same numbering throughout the algorithm
but still want the convenient indentation of nested 
\texttt{enumerate} environments, you can use the
\texttt{enumerate*} environment provided by the \textsf{jmlr}
class. For example, see \algorithmref{alg:moore}.

\begin{algorithm}
\caption{Moore's Shortest Path}\label{alg:moore}
Given a connected graph $G$, where the length of each edge is 1:
\begin{enumerate*}
  \item Set the label of vertex $s$ to 0
  \item Set $i=0$
  \begin{enumerate*}
    \item \label{step:locate}Locate all unlabelled vertices 
          adjacent to a vertex labelled $i$ and label them $i+1$
    \item If vertex $t$ has been labelled,
    \begin{enumerate*}
      \item[] the shortest path can be found by backtracking, and 
      the length is given by the label of $t$.
    \end{enumerate*}
    otherwise
    \begin{enumerate*}
      \item[] increment $i$ and return to step~\ref{step:locate}
    \end{enumerate*}
  \end{enumerate*}
\end{enumerate*}
\end{algorithm}

Pseudo code can be displayed using the \texttt{algorithm2e}
environment. This is defined by the \textsf{algorithm2e} package
(which is automatically loaded) so check the \textsf{algorithm2e}
documentation for further details.\footnote{Either \texttt{texdoc
algorithm2e} or \url{http://www.ctan.org/pkg/algorithm2e}}
For an example, see \algorithmref{alg:net}.

\begin{algorithm2e}
\caption{Computing Net Activation}
\label{alg:net}
 % older versions of algorithm2e have \dontprintsemicolon instead
 % of the following:
 %\DontPrintSemicolon
 % older versions of algorithm2e have \linesnumbered instead of the
 % following:
 %\LinesNumbered
\KwIn{$x_1, \ldots, x_n, w_1, \ldots, w_n$}
\KwOut{$y$, the net activation}
$y\leftarrow 0$\;
\For{$i\leftarrow 1$ \KwTo $n$}{
  $y \leftarrow y + w_i*x_i$\;
}
\end{algorithm2e}

\section{Description Lists}

The \textsf{jmlr} class also provides a description-like 
environment called \texttt{altdescription}. This has an
argument that should be the widest label in the list. Compare:
\begin{description}
\item[add] A method that adds two variables.
\item[differentiate] A method that differentiates a function.
\end{description}
with
\begin{altdescription}{differentiate}
\item[add] A method that adds two variables.
\item[differentiate] A method that differentiates a function.
\end{altdescription}

\section{Theorems, Lemmas etc}
\label{sec:theorems}

The following theorem-like environments are predefined by
the \textsf{jmlr} class: \texttt{theorem}, \texttt{example},
\texttt{lemma}, \texttt{proposition}, \texttt{remark}, 
\texttt{corollary}, \texttt{definition}, \texttt{conjecture}
and \texttt{axiom}. You can use the \texttt{proof} environment
to display the proof if need be, as in \theoremref{thm:eigenpow}.

\begin{theorem}[Eigenvalue Powers]\label{thm:eigenpow}
If $\lambda$ is an eigenvalue of $\vec{B}$ with eigenvector
$\vec{\xi}$, then $\lambda^n$ is an eigenvalue of $\vec{B}^n$
with eigenvector $\vec{\xi}$.
\begin{proof}
Let $\lambda$ be an eigenvalue of $\vec{B}$ with eigenvector
$\xi$, then
\begin{align*}
\vec{B}\vec{\xi} &= \lambda\vec{\xi}
\intertext{premultiply by $\vec{B}$:}
\vec{B}\vec{B}\vec{\xi} &= \vec{B}\lambda\vec{\xi}\\
\Rightarrow \vec{B}^2\vec{\xi} &= \lambda\vec{B}\vec{\xi}\\
&= \lambda\lambda\vec{\xi}\qquad
\text{since }\vec{B}\vec{\xi}=\lambda\vec{\xi}\\
&= \lambda^2\vec{\xi}
\end{align*}
Therefore true for $n=2$. Now assume true for $n=k$:
\begin{align*}
\vec{B}^k\vec{\xi} &= \lambda^k\vec{\xi}
\intertext{premultiply by $\vec{B}$:}
\vec{B}\vec{B}^k\vec{\xi} &= \vec{B}\lambda^k\vec{\xi}\\
\Rightarrow \vec{B}^{k+1}\vec{\xi} &= \lambda^k\vec{B}\vec{\xi}\\
&= \lambda^k\lambda\vec{\xi}\qquad
\text{since }\vec{B}\vec{\xi}=\lambda\vec{\xi}\\
&= \lambda^{k+1}\vec{\xi}
\end{align*}
Therefore true for $n=k+1$. Therefore, by induction, true for all
$n$.
\end{proof}
\end{theorem}

\begin{lemma}[A Sample Lemma]\label{lem:sample}
This is a lemma.
\end{lemma}

\begin{remark}[A Sample Remark]\label{rem:sample}
This is a remark.
\end{remark}

\begin{corollary}[A Sample Corollary]\label{cor:sample}
This is a corollary.
\end{corollary}

\begin{definition}[A Sample Definition]\label{def:sample}
This is a definition.
\end{definition}

\begin{conjecture}[A Sample Conjecture]\label{con:sample}
This is a conjecture.
\end{conjecture}

\begin{axiom}[A Sample Axiom]\label{ax:sample}
This is an axiom.
\end{axiom}

\begin{example}[An Example]\label{ex:sample}
This is an example.
\end{example}

\section{Color vs Grayscale}
\label{sec:color}

It's helpful if authors supply grayscale versions of their
images in the event that the article is to be incorporated into
a black and white printed book. With external PDF, PNG or JPG
graphic files, you just need to supply a grayscale version of the
file. For example, if the file is called \texttt{myimage.png},
then the gray version should be \texttt{myimage-gray.png} or
\texttt{myimage-gray.pdf} or \texttt{myimage-gray.jpg}. You don't
need to modify your code. The \textsf{jmlr} class checks for
the existence of the grayscale version if it is print mode 
(provided you have used \verb|\includegraphics| and haven't
specified the file extension).

You can use \verb|\ifprint| to determine which mode you are in.
For example, in \figureref{fig:nodes}, the 
\ifprint{dark gray}{purple} ellipse represents an input and the
\ifprint{light gray}{yellow} ellipse represents an output.
Another example: {\ifprint{\bfseries}{\color{red}}important text!}

You can use the class option \texttt{gray} to see how the
document will appear in gray scale mode. \textcolor{blue}{Colored
text} will automatically be converted to gray scale.

The \textsf{jmlr} class loads the \textsf{xcolor}
package, so you can also define your own colors. For example:
\ifprint
  {\definecolor{myred}{gray}{0.5}}%
  {\definecolor{myred}{rgb}{0.5,0,0}}%
\textcolor{myred}{XYZ}.

The \textsf{xcolor} class is loaded with the \texttt{x11names}
option, so you can use any of the x11 predefined colors (listed
in the \textsf{xcolor} documentation\footnote{either 
\texttt{texdoc xcolor} or \url{http://www.ctan.org/pkg/xcolor}}).

\section{Citations and Bibliography}
\label{sec:cite}

The \textsf{jmlr} class automatically loads \textsf{natbib}.
This sample file has the citations defined in the accompanying
BibTeX file \texttt{jmlr-sample.bib}. For a parenthetical
citation use \verb|\citep|. For example
\citep{guyon-elisseeff-03}. For a textual citation use
\verb|\citet|. For example \citet{guyon2007causalreport}.
Both commands may take a comma-separated list, for example
\citet{guyon-elisseeff-03,guyon2007causalreport}.

These commands have optional arguments and have a starred
version. See the \textsf{natbib} documentation for further
details.\footnote{Either \texttt{texdoc natbib} or
\url{http://www.ctan.org/pkg/natbib}}

The bibliography is displayed using \verb|\bibliography|.

\acks{Acknowledgements go here.}

\bibliography{bibliography}

\appendix

\section{First Appendix}\label{apd:first}

This is the first appendix.

\section{Second Appendix}\label{apd:second}

This is the second appendix.

\end{document}

### 2018-07-08 article.tex
Gotów scheme.

@@
 
-\begin{figure}[htbp]
+\begin{figure}[!h]
 \floatconts
@@
   {\caption{Scheme of using k-Fold division in ensemble construction}}
-  {\includeteximage[angle=0]{figures/ensemble_scheme}}
+  {\input{figures/ensemble_scheme}}
 \end{figure}
@@
 Proponowane metody decyzyjne.
+
+W konstrukcji reguły decyzyjnej opieramy się na wsparciu dla klasy pozytywnej.
 

### 2018-07-08 figures/ensemble_scheme.tex
Gotów scheme.

@@
-\frame{\begin{picture}(100,100)
-\put(25,50){\dashbox{.5}(10,10){$C$}}
-\put(50,50){\dashbox{.5}(10,10){$B$}}
-\end{picture}}
+\begin{tikzpicture}%[font=\sffamily\small]
+\tikzset{el/.style={draw, rectangle, minimum width = 1cm, minimum height=1cm}}
+
+%\draw[step=.5cm,gray!30!white,very thin] (-4,-13) grid (7,1.5);
+
+\node[rectangle, fill=red!10!white, minimum width=3cm, minimum height=8cm]
+ at (5,-3) {};
+
+% Original training set with division
+\node[el, minimum width=6cm](its) at (0,0) {Imbalanced training set};
+\node[el, text width=.5cm] (minc) at (-2.5, -1.5) {\tiny Min. class};
+\node[el, minimum width = 4.5cm] (majc) at (.75, -1.5) {\tiny Majority class};
+
+% Pre-methods
+\node[el, thick, minimum width = 4.5cm, minimum height = .5cm] (kfold) at (.75, -2.5)
+{\scriptsize \textsc{shuffled k-fold division}};
+\node[el, thick, minimum width = 2cm, minimum height = .5cm] (oversampling) at (5, -2.5)
+{\tiny \textsc{oversampling}};
+
+% Processed training sets
+\node[el, text width=.5cm] (majc0) at (-1, -3.5) {\tiny Maj. \#0};
+\node[el, text width=.5cm] (majc1) at (.5, -3.5) {\tiny Maj. \#1};
+\node[el, text width=.5cm] (majck) at (2.5, -3.5) {\tiny Maj. \#k};
+\node[el, text width=.5cm] (minc0) at (-1, -4.5) {\tiny Min. class};
+\node[el, text width=.5cm] (minc1) at (.5, -4.5) {\tiny Min. class};
+\node[el, text width=.5cm] (minck) at (2.5, -4.5) {\tiny Min. class};
+
+\node[el, minimum width = 2cm, minimum height=2cm, text width=1.75cm] (osts) at (5, -4)
+{\scriptsize Oversampled training set};
+
+% Member classifiers
+\node[el] (c0) at (-1, -6) {$\Psi_1$};
+\node[el] (c1) at (.5, -6) {$\Psi_2$};
+\node[el] (ck) at (2.5, -6) {$\Psi_k$};
+\node[el, minimum width=2cm] (co) at (5, -6) {$\Psi_{os}$};
+
+% Testing
+\node[el, minimum width=7.5cm](testset) at (2.25,-8) {Testing set};
+
+\node[el] (s0) at (-1, -9.5) {$s_1$};
+\node[el] (s1) at (.5, -9.5) {$s_2$};
+\node[el] (sk) at (2.5, -9.5) {$s_k$};
+\node[el, minimum width=2cm] (so) at (5, -9.5) {$s_{os}$};
+
+\node[el, minimum width=7.5cm, minimum height = .5, thick](fuser) at (2.25,-10.75)
+{\textsc{fuser}};
+
+\node[el, minimum width=7.5cm](dec) at (2.25,-11.75)
+{Decisions};
+
+% Lines and sections
+\draw [dashed] (3.5,1) -- (3.5,-7);
+\node[text width = 2.75cm] at (5,.5)
+{\tiny \bfseries Extending pool with oversampling};
+\node[text width = 2cm] at (-2.25,-6.75)
+{\tiny \bfseries Learning};
+\node[text width = 2cm] at (-2.25,-7.25)
+{\tiny \bfseries Classification};
+
+\draw [dashed] (-3.5,-7) -- (6.5,-7);
+
+% Connections
+\draw[->] (its) -| (oversampling);
+\draw[->] (-2.5,-.5) -- (minc);
+\draw[->] (.75,-.5) -- (majc);
+\draw[->] (majc) -- (kfold);
+
+\draw[->] (-1,-2.75) -- (majc0);
+\draw[->] (.5,-2.75) -- (majc1);
+\draw[->] (2.5,-2.75) -- (majck);
+
+\draw[->] (minc.south) |- (minc0.west);
+\draw[<->] (minc0) -- (minc1);
+\draw[<->] (minc1) -- (minck);
+\node[text width = 1cm] at (1.7,-4)
+{\bfseries . . .};
+
+\draw[->] (oversampling) -- (osts);
+
+\draw[->] (minc0) -- (c0);
+\draw[->] (minc1) -- (c1);
+\draw[->] (minck) -- (ck);
+\draw[->] (osts) -- (co);
+
+\draw[->] (c0) -- (-1,-7.5);
+\draw[->] (c1) -- (.5,-7.5);
+\draw[->] (ck) -- (2.5,-7.5);
+\draw[->] (co) -- (5,-7.5);
+
+\draw[->] (-1,-8.5) -- (s0);
+\draw[->] (.5,-8.5) -- (s1);
+\draw[->] (2.5,-8.5) -- (sk);
+\draw[->] (5,-8.5) -- (so);
+
+\draw[->] (s0) -- (-1,-10.5);
+\draw[->] (s1) -- (.5,-10.5);
+\draw[->] (sk) -- (2.5,-10.5);
+\draw[->] (so) -- (5,-10.5);
+\draw[->] (fuser) -- (dec);
+
+\end{tikzpicture}

### 2018-07-08 article.tex
Analiza.

@@
 
+\begin{algorithm}
+\caption{Training classifier ensemble from multiple balanced training datasets separated from one imbalanced dataset of binary problem}\label{alg:moore}
+Given a dataset $DS$:
+\begin{enumerate*}
+	\item Divide $DS$ into subsets of minority- $MinC$ and majority-class $MajC$
+	\item Calculate imbalanced ratio $IR$ as the proportion of the number of patterns in $MinC$ and $MajC$ 
+	\item Establish $k$ by rounding $IR$ to nearest integer
+	\item Perform a \emph{shuffled k-fold division} of $MajC$ to produce a set of subsets $MajC_1, MajC_2, \ldots, MajC_k$ 
+	\item For every $i$ in range to $k$
+	\begin{enumerate*}
+		\item Join $MajC_i$ with $MinC$ to prepare a training set $TS_i$,
+		\item Train classifier $\Psi_i$ on $TS_i$ and add it into ensemble
+	\end{enumerate*}
+\end{enumerate*}
+\end{algorithm}
+
 Idea k-foldowego podziału klasy większościowej. Wyznaczanie wartości k jako zaokrąglonego IR. Atut w postaci wykorzystania wszystkich wzorców, gdzie tworzymy komitet k zbalansowanych zbiorów.
@@
 \begin{itemize}
-	\item - akumulacja wsparć,
-	\item - akumulacja ważona po członkach komitetu, gdzie waga to BAC dla zbioru uczącego,
-	\item - akumulacja ważona po wzorcach, przez kontrast,
-	\item - akumulacja znormalizowanych wag członków,
-	\item - iloczyn znormalizowanych wag i kontrastu
+	\item - reg akumulacja wsparć,
+	\item - wei akumulacja ważona po członkach komitetu, gdzie waga to BAC dla zbioru uczącego,
+	\item - con akumulacja ważona po wzorcach, przez kontrast,
+	\item - nor akumulacja znormalizowanych wag członków,
+	\item - nci iloczyn znormalizowanych wag i kontrastu
 \end{itemize}
@@
 
-Wybrane zbiory danych.
+For the experimental evaluation of the proposed method, a collection of data sets made available with \textsc{keel} \citep{alcala2011keel} was used, focusing on a section containing highly unbalanced data, with \textsc{ir} greater than 9 \citep{fernandez2009hierarchical}.
+From among the available datasets, 40 were selected presenting only binary problems with quantitative attributes.
+A review of selected datasets, including information on their number of features, the number of patterns in each class and the unbalance ratio is presented in Table 1.
+
+\begin{table}[!h]
+\footnotesize
+\centering
+\setlength{\tabcolsep}{3.5pt}
+\def\arraystretch{1}
+\begin{tabular}{@{}|rl|c|ccc|c|}\hline%
+
+\multirow{2}{*}{\bfseries \#} &
+\multirow{2}{*}{\bfseries Dataset} &
+\multirow{2}{*}{\bfseries Features} &
+\multicolumn{3}{c|}{\bfseries Samples} &
+\multirow{2}{*}{\bfseries \textsc{ir}} 	
+\\
+
+& & & 
+\multicolumn{1}{c}{\textsc{all}} & 
+\multicolumn{1}{c}{\textsc{maj}} & 
+\multicolumn{1}{c|}{\textsc{min}} &
+
+	\\\hline\hline
+
+	\csvreader[head to column names,
+	           late after line=\csvifoddrow{\\}{\\\rowcolor{gray!10!white}},
+	           late after last line = \\\hline]
+	{results/datasets.csv}{}%
+	{
+
+	\idx & \multicolumn{1}{l|}{\emph{\dbname}} & \features & 
+	\multicolumn{1}{c}{\samples} & 
+	\multicolumn{1}{c}{\majority} & 
+	\multicolumn{1}{c|}{\minority} & \ir
+
+	}%
+\end{tabular}
+\caption{Summary of imbalanced datasets chosen for evaluation}
+\end{table}
+
+As may be observed after the Table analysis, the experiments will be based on data sets with relatively small spatiality (up to \oldstylenums{13} dimensions), with imbalance ratio from \oldstylenums9 to even \oldstylenums{40}.
 
@@
 Stąd bierzemy GNB, kNN i DT, przy domyślnych parametrach z sklearn.
+
+\begin{itemize}
+	\item \emph{Gaussian Naive Bayes} (\textsc{gnb}) ---
+	\item \emph{k-Nearest Neighbors} (k\textsc{nn}) ---
+	\item \emph{Decision Tree Classifier} (\textsc{dtc}) ---
+\end{itemize}
 

### 2018-07-08 figures/ensemble_scheme.tex
Analiza.

@@
 \node[el, minimum width=6cm](its) at (0,0) {Imbalanced training set};
-\node[el, text width=.5cm] (minc) at (-2.5, -1.5) {\tiny Min. class};
-\node[el, minimum width = 4.5cm] (majc) at (.75, -1.5) {\tiny Majority class};
+\node[el, text width=.75cm] (minc) at (-2.5, -1.5) {\tiny $MinC$};
+\node[el, minimum width = 4.5cm] (majc) at (.75, -1.5) {\tiny $MajC$};
 
 % Pre-methods
-\node[el, thick, minimum width = 4.5cm, minimum height = .5cm] (kfold) at (.75, -2.5)
+\node[el, thick, minimum width = 4.5cm, minimum height = .5cm, rounded corners=2mm] (kfold) at (.75, -2.5)
 {\scriptsize \textsc{shuffled k-fold division}};
-\node[el, thick, minimum width = 2cm, minimum height = .5cm] (oversampling) at (5, -2.5)
+\node[el, thick, minimum width = 2cm, minimum height = .5cm, rounded corners=2mm] (oversampling) at (5, -2.5)
 {\tiny \textsc{oversampling}};
@@
 % Processed training sets
-\node[el, text width=.5cm] (majc0) at (-1, -3.5) {\tiny Maj. \#0};
-\node[el, text width=.5cm] (majc1) at (.5, -3.5) {\tiny Maj. \#1};
-\node[el, text width=.5cm] (majck) at (2.5, -3.5) {\tiny Maj. \#k};
-\node[el, text width=.5cm] (minc0) at (-1, -4.5) {\tiny Min. class};
-\node[el, text width=.5cm] (minc1) at (.5, -4.5) {\tiny Min. class};
-\node[el, text width=.5cm] (minck) at (2.5, -4.5) {\tiny Min. class};
+\node[el, text width=.75cm] (majc0) at (-1, -3.5) {\tiny$MajC_0$};
+\node[el, text width=.75cm] (majc1) at (.5, -3.5) {\tiny$MajC_1$};
+\node[el, text width=.75cm] (majck) at (2.5, -3.5) {\tiny$MajC_k$};
+\node[el, text width=.75cm] (minc0) at (-1, -4.5) {\tiny$MinC$};
+\node[el, text width=.75cm] (minc1) at (.5, -4.5) {\tiny$MinC$};
+\node[el, text width=.75cm] (minck) at (2.5, -4.5) {\tiny$MinC$};
+\node[text width = 1cm] at (1.65,-4)
+{\bfseries . . .};
 
@@
 % Member classifiers
-\node[el] (c0) at (-1, -6) {$\Psi_1$};
-\node[el] (c1) at (.5, -6) {$\Psi_2$};
-\node[el] (ck) at (2.5, -6) {$\Psi_k$};
-\node[el, minimum width=2cm] (co) at (5, -6) {$\Psi_{os}$};
+\node[el, rounded corners=5mm] (c0) at (-1, -6) {$\Psi_1$};
+\node[el, rounded corners=5mm] (c1) at (.5, -6) {$\Psi_2$};
+\node[el, rounded corners=5mm] (ck) at (2.5, -6) {$\Psi_k$};
+\node[el, minimum width=2cm, rounded corners=5mm] (co) at (5, -6) {$\Psi_{os}$};
+
+\node[text width = 1cm] at (1.65,-6)
+{\bfseries . . .};
 
@@
 \node[el, minimum width=2cm] (so) at (5, -9.5) {$s_{os}$};
+\node[text width = 1cm] at (1.65,-9.5)
+{\bfseries . . .};
 
-\node[el, minimum width=7.5cm, minimum height = .5, thick](fuser) at (2.25,-10.75)
+\node[el, minimum width=7.5cm, minimum height = .5, thick, rounded corners=2mm](fuser) at (2.25,-10.75)
 {\textsc{fuser}};
@@
 \draw[<->] (minc1) -- (minck);
-\node[text width = 1cm] at (1.7,-4)
-{\bfseries . . .};
 

### 2018-07-08 analyze.py

@@ -1,0 +1,54 @@
+"""
+Comparison of processed datasets.
+"""
+
+import csv
+import helper as h
+import numpy as np
+
+# Numer porządkowy
+# Nazwa zbioru
+# Liczba atrybutów
+# Liczba wzorców
+# W tym większościowych
+# W tym mniejszościowych
+# IR
+header = [
+    'idx', 'dbname', 'features', 'samples', 'majority', 'minority', 'ir'
+]
+datasets = h.datasets_for_groups([
+    "imb_IRhigherThan9p1",
+    "imb_IRhigherThan9p2",
+    #"imb_IRlowerThan9",
+])
+
+csvfile = open('results/datasets.csv', 'w')
+writer = csv.writer(csvfile, delimiter=',')
+writer.writerow(header)
+
+for i, dataset in enumerate(datasets):
+    dbname = dataset[1].replace("_", "-")
+    #print(dbname)
+
+    # Load and analyze dataset
+    X, y, _, _ = h.load_dataset(dataset)
+    classes, c_counts = np.unique(y, return_counts=True)
+    majority_c = 0 if c_counts[0] > c_counts[1] else 1
+    minority_c = 1 - majority_c
+
+    n_samples = len(y)
+    n_features = X.shape[1]
+    n_majority = np.sum(y==majority_c)
+    n_minority = np.sum(y==minority_c)
+    IR = n_majority / n_minority
+
+    #print("%i samples (%i maj / %i min)" % (
+    #    n_samples, n_majority, n_minority
+    #))
+    #print("IR = %.2f" % IR)
+
+    row = [i+1, dbname, n_features, n_samples, n_majority, n_minority, "%.2f" % IR]
+    print(row)
+    writer.writerow(row)
+
+csvfile.close()

### 2018-07-09 article.tex
Bib.

@@
 \title
-[Fusers in homogenous ensemble of undersampled majority class]
+[Homogenous ensemble of undersampled majority class]
 {
-	Fusers in homogenous ensemble of undersampled majority class for highly imbalanced data classification%\titlebreak
+	Homogenous ensemble of undersampled majority class for highly imbalanced data binary classification%\titlebreak
 }
@@
 
-Additionally, in incremental learning, if the majority-class objects outnumber greatly the minority class, the latter can be completely ignored \cite{He:2009}.
-The aforementioned issues are reasons why most existing classification methods for imbalanced data are restricted to the \textit{offline} learning only, i.e., a case where the entire data set is provided prior to the analysis.
-
-Most of the classification algorithms assume that there are no significant disproportions among instances from different classes.
+%Most of the classification algorithms assume that there are no significant disproportions among instances from different classes.
 Nevertheless, in many practical tasks, we may observe that instances from one class (so-called \textit{majority class}) significantly outnumber the objects from remaining classes (\textit{minority class}).
@@
 
-\begin{figure}[!h]
-\floatconts
-  {fig:east}
-  {\caption{Easy separable imbalance dataset}}
-  {\includegraphics[clip=true, trim = 11 11 11 11, width=0.25\linewidth]{figures/easy}}
-\end{figure}
+%\begin{figure}[!h]
+%\floatconts
+%  {fig:east}
+%  {\caption{Easy separable imbalance dataset}}
+%  {\includegraphics[clip=true, trim = 11 11 11 11, width=0.25\linewidth]{figures/easy}}
+%\end{figure}
 
-In this project we will focus on binary imbalanced problems, because this setup is the one most frequently studied in the literature and most commonly meet in practical problems, e.g.,\textit{fault detection} or \textit{spam filtering}.
+%In this project we will focus on binary imbalanced problems, because this setup is the one most frequently studied in the literature and most commonly meet in practical problems, e.g.,\textit{fault detection} or \textit{spam filtering}.
 Therefore, another important issue is proposing an appropriate quality measure that would be adequate for imbalanced data classification \cite{Elazmeh:2006}.
 
-In case of imbalanced data classification the disproportion between the different classes is not the sole issue of learning difficulties.
+%In case of imbalanced data classification the disproportion between the different classes is not the sole issue of learning difficulties.
 One may easily came up with an example where the instance distributions from different classes are well-separated, as depicted in Fig.\ref{fig:easy}.
 
-Proposing a efficient classifier for such a task is not a challenge.
+%Proposing a efficient classifier for such a task is not a challenge.
 Unfortunately, instances from the minority class often form clusters of an unknown structure that are scattered \cite{Napierala:2012}.
@@
 
-Methods for imbalanced data classification can be divided into three main groups \cite{Lopez:2012}.
+%Methods for imbalanced data classification can be divided into three main groups \cite{Lopez:2012}.
 
-\begin{figure}[!h]
-\floatconts
-  {fig:subfigex}
-  {\caption{Examples of data preprocessing methods.}}
-  {%
-    \subfigure[Original dataset]{\label{fig:circle}%
-    \includegraphics[clip=true, width=.25\linewidth,
-    				 trim = 11 141 141 11]
-    {figures/preprocessing}}%
-    \qquad
-    \subfigure[\textsc{smote}]{\label{fig:circle}%
-    \includegraphics[clip=true, width=.25\linewidth,
-    				 trim = 141 141 11 11]
-    {figures/preprocessing}}%
+%\begin{figure}[!h]
+%\floatconts
+%  {fig:subfigex}
+%  {\caption{Examples of data preprocessing methods.}}
+%  {%
+%    \subfigure[Original dataset]{\label{fig:circle}%
+%    \includegraphics[clip=true, width=.25\linewidth,
+%    				 trim = 11 141 141 11]
+%    {figures/preprocessing}}%
+%    \qquad
+%    \subfigure[\textsc{smote}]{\label{fig:circle}%
+%    \includegraphics[clip=true, width=.25\linewidth,
+%    				 trim = 141 141 11 11]
+%    {figures/preprocessing}}%
 
-    \subfigure[\textsc{adasyn}]{\label{fig:circle}%
-    \includegraphics[clip=true, width=.25\linewidth,
-    				 trim = 11 11 141 141]
-    {figures/preprocessing}}%
-    \qquad
-    \subfigure[Undersampling]{\label{fig:circle}%
-    \includegraphics[clip=true, width=.25\linewidth,
-    				 trim = 141 11 11 141]
-    {figures/preprocessing}}%
-  }
-\end{figure}
+%    \subfigure[\textsc{adasyn}]{\label{fig:circle}%
+%    \includegraphics[clip=true, width=.25\linewidth,
+%    				 trim = 11 11 141 141]
+%    {figures/preprocessing}}%
+%    \qquad
+%    \subfigure[Undersampling]{\label{fig:circle}%
+%    \includegraphics[clip=true, width=.25\linewidth,
+%    				 trim = 141 11 11 141]
+%    {figures/preprocessing}}%
+%  }
+%\end{figure}
 
-\noindent\textbf{ Data preprocessing methods}.
+%\noindent\textbf{ Data preprocessing methods}.
 This approach focuses on reducing the number of objects in majority class (\emph{undersampling}) or generating new objects of the minority class (\textit{oversampling}).
@@
 
-These mechanisms have the objective of balancing the quantity of instances from considered classes.
+%These mechanisms have the objective of balancing the quantity of instances from considered classes.
 For oversampling, new instances are random copies of existing ones or are generated in a guided manner.
@@
 
-\begin{figure}[htbp]
-\floatconts
-  {fig:subfigex}
-  {\caption{Example of wrong \textsc{smote} oversampling.}}
-  {%
-    \subfigure[Original dataset]{\label{fig:circle}%
-    \includegraphics[clip=true, width=.25\linewidth,
-    				 trim = 11 11 141 11]
-    {figures/wrong_smote}}%
-    \qquad
-    \subfigure[\textsc{smote}]{\label{fig:circle}%
-    \includegraphics[clip=true, width=.25\linewidth,
-    				 trim = 141 11 11 11]
-    {figures/wrong_smote}}%
-  }
-\end{figure}
+%\begin{figure}[htbp]
+%\floatconts
+%  {fig:subfigex}
+%  {\caption{Example of wrong \textsc{smote} oversampling.}}
+%  {%
+%    \subfigure[Original dataset]{\label{fig:circle}%
+%    \includegraphics[clip=true, width=.25\linewidth,
+%    				 trim = 11 11 141 11]
+%    {figures/wrong_smote}}%
+%    \qquad
+%    \subfigure[\textsc{smote}]{\label{fig:circle}%
+%    \includegraphics[clip=true, width=.25\linewidth,
+%    				 trim = 141 11 11 11]
+%    {figures/wrong_smote}}%
+%  }
+%\end{figure}
 
-W WYPADKU UNDERSAMPLINGU NIE WYSTEPUJE RYZYKO NIESŁUSZNEGO ROZSZERZENIA PRZESTRZENI WZORCÓW KLASY MNIEJSZOŚCIOWEJ, CO MA MIEJSCE W CHOĆBY SMOTE.
+%W WYPADKU UNDERSAMPLINGU NIE WYSTEPUJE RYZYKO NIESŁUSZNEGO ROZSZERZENIA PRZESTRZENI WZORCÓW KLASY MNIEJSZOŚCIOWEJ, CO MA MIEJSCE W CHOĆBY SMOTE.
 
-Several modifications of \textsc{smote} have been proposed that are able to identify the instances to be copied in a more intelligent fashion such as \emph{Borderline}\textsc{smote} \cite{Han:2005}.
+%Several modifications of \textsc{smote} have been proposed that are able to identify the instances to be copied in a more intelligent fashion such as \emph{Borderline}\textsc{smote} \cite{Han:2005}.
 It generates new instances from the minority class close to the decision border.
@@
 
-\noindent\textbf{ Inbuilt mechanisms.} In this approach existing classification algorithms are adapted for imbalanced problems ensuring balanced accuracy for instances from both classes.
+%\noindent\textbf{ Inbuilt mechanisms.} In this approach existing classification algorithms are adapted for imbalanced problems ensuring balanced accuracy for instances from both classes.
 Two of the most popular areas of research of this methods are using one-class classification  \cite{Japkowicz:1995}, usually known as learning without counterexamples, where the goal is to learn the minority class decision areas and because of the frequently assumed regular, closed shape of the decision borders is adequate to the clusters created by minority classes \cite{Krawczyk:2014ins}.
@@
 Unfortunately such methods can cause a reverse bias towards the minority class.
-Worth noting are methods based on ensemble classification \cite{Wozniak:2014}, like \emph{\textsc{smote}Boost} \cite{Chawla:2003} and \emph{AdaBoost.NC} \cite{Wang:2010}%, or \emph{Multi-objective Genetic Programing Ensemble} \cite{Bhowan:2013}.
 
-\noindent\textbf{Hybrid methods.} They combine the advantages of methods using data pre-processing with the classification methods.
+%Worth noting are methods based on ensemble classification \cite{Wozniak:2014}, like \emph{\textsc{smote}Boost} \cite{Chawla:2003} and \emph{AdaBoost.NC} \cite{Wang:2010}%, or \emph{Multi-objective Genetic Programing Ensemble} \cite{Bhowan:2013}.
+
+%\noindent\textbf{Hybrid methods.} They combine the advantages of methods using data pre-processing with the classification methods.
 The most popular category is the hybridisation of \emph{under-} and \emph{oversampling} with ensemble classifiers \cite{Galar:2012}.
@@
 The main contributions of this work are:
+\begin{itemize}
+	\item metoda konstrukcji komitetu na k-fold,
+	\item propozycje reguł decyzyjnych,
+	\item metoda pruningu dostosowującego regułę decyzyjną do zbioru testowego
+	\item implementacja i ewaluacja eksperymentalna
+\end{itemize}
 
+\vspace{5em}
 %%%
-%%% Introduction
+%%% Method
 %%%
@@
 \label{sec:intro}
+\subsection{Establishing ensemble}
 
-Zaawansowane metody oversamplingu nie są możliwe do zastosowania przy sytuacji, gdzie w zbiorze uczącym znajduje się zaledwie kilka wzorców.
+Complex oversampling methods, such as \textsc{smote} or \textsc{adasyn}, despite the large possibilities in most of the imbalanced problems, are not applicable to extreme situations where the minority class is represented by only a few samples, which makes it impossible to designate the nearest neighbors to create a new synthetic object.
+This could lead to the use of \emph{undersampling} in such problems, but it is characterized, due to high randomness, by a strong instability in a situation of high \textsc{ir} (\emph{imbalance ratio}), which does not allow for the development of a reliable solution.
 
-\begin{algorithm}
+A popular answer to the above-mentioned problem are the ensemble methods of \emph{Bagging} or \emph{Boosting}, characterized by random sampling with replacement of the training set, breaking a large problem, into a set of smaller problems.
+This work proposes a basic method, which also breaks the imbalanced task, but with ensuring the use of all the patterns available in the data set, but without a risk of overlapping.
+Its description can be found in Algorithm 1.
+
+\begin{algorithm}[!h]
 \caption{Training classifier ensemble from multiple balanced training datasets separated from one imbalanced dataset of binary problem}\label{alg:moore}
@@
 
-Idea k-foldowego podziału klasy większościowej. Wyznaczanie wartości k jako zaokrąglonego IR. Atut w postaci wykorzystania wszystkich wzorców, gdzie tworzymy komitet k zbalansowanych zbiorów.
+After dividing the dataset with imbalanced binary problem into separated minority ($MinC$) and majority class ($MajC$), we are calculating the \textsc{ir} (\emph{imbalanced ratio}) between given classes.
+Rounding \textsc{ir} to the nearest integer value $k$ allows us to find the optimal division coefficient of the majority class samples in the context of maximizing the balance between the $MinC$ and any $MajC_i$ subsets while ensuring that all $MajC$ patterns are used in learning process with no overlapping between the individual $MajC_i$'s.
+Each of $k$ classifiers $\Psi_i$ is trained on union of $MinC$ and $MajC_i$ sets.
 
-\begin{figure}[!h]
-\floatconts
-  {fig:teximage}
-  {\caption{Scheme of using k-Fold division in ensemble construction}}
-  {\input{figures/ensemble_scheme}}
-\end{figure}
+\paragraph{Extending pool with oversampling} As an extension of the method of classifier ensemble construction, it is also proposed to extend its pool by a model learned on an additional data set, which is a full set of data subjected to \emph{oversampling}.
+It is worth testing if the knowledge gained from this method may be a valuable contribution to the ensemble decision.
+Due to impossibility to use \textsc{smote} or \textsc{adasyn} for oversampling the minority class with only few instances, only its basic variant will be used.
+
+%%% Fuser
+\subsection{Fuser design}
+
+In addition to ensuring the diversity of the classifiers pool, which we achieve by a homogenous committee built on disjoint subsets of the majority class supplemented by minority patterns, the key aspect of the hybrid classification system is the appropriate design of its \emph{fuser} -- the element responsible for making decisions based on the answers of the base classifiers.
+
+There are two groups of solutions here.
+The first are based on component \emph{decisions} of the committee, most often employing the \emph{majority voting} to produce a final decision.
+The decision rules proposed in this work are, however, part of the second group, where the \emph{fuser} is carried out by \emph{averaging} (or \emph{accumulating}) the \emph{support vectors} received from the members of a pool.
+
+\begin{note}
+It should be remembered that in such methods, it is necessary to use a \emph{probabilistic classification model}, which also requires \emph{quantitative} and not \emph{qualitative data}.
+\end{note}
+
+Five fusers were proposed:
+
+\begin{enumerate}
+	\item \textbf{\textsc{reg}} --- regular accumulation of support, without weighing the members of the committee.
+	\item \textbf{\textsc{wei}} --- accumulation weighted after members of the committee.
+
+The weight of the classifier in the pool is its quality achieved for the training set.
+We can not use here the measure of \emph{accuracy}, which does not fit with the task of the imbalanced classification, so we decided on a \emph{balanced accuracy} \citep{brodersen2010balanced}.
+
+	\item \textbf{\textsc{nor}} --- same as \textbf{\textsc{wei}}, but with normalization of weights,
+
+Aby premiować klasyfikatory o wyższej mocy dyskryminacyjnej, wagi są poddawane normalizacji standardowej
+
+	\item - con akumulacja ważona po wzorcach, przez kontrast,
+	\item - nci iloczyn znormalizowanych wag i kontrastu
+\end{enumerate}
 
@@
 
-\begin{itemize}
-	\item - reg akumulacja wsparć,
-	\item - wei akumulacja ważona po członkach komitetu, gdzie waga to BAC dla zbioru uczącego,
-	\item - con akumulacja ważona po wzorcach, przez kontrast,
-	\item - nor akumulacja znormalizowanych wag członków,
-	\item - nci iloczyn znormalizowanych wag i kontrastu
-\end{itemize}
+Duża skala niezbalansowania to duża wielkość komitetu (ilustracja zależności na wykresie). Przyda się więc przycinanie (pruning).
 
-Duża skala niezbalansowania to duża wielkość komitetu (ilustracja zależności na wykresie). Przyda się więc przycinanie (pruning).
+%%% Pruning
+\subsection{Ensemble pruning}
 
@@
 
+\begin{figure}[!h]
+\floatconts
+  {fig:teximage}
+  {\caption{Scheme of using k-Fold division in ensemble construction}}
+  {\input{figures/ensemble_scheme}}
+\end{figure}
+
 %%%
@@
 
-For the experimental evaluation of the proposed method, a collection of data sets made available with \textsc{keel} \citep{alcala2011keel} was used, focusing on a section containing highly unbalanced data, with \textsc{ir} greater than 9 \citep{fernandez2009hierarchical}.
-From among the available datasets, 40 were selected presenting only binary problems with quantitative attributes.
+For the experimental evaluation of the proposed method, a collection of datasets made available with \textsc{keel} \citep{alcala2011keel} was used, focusing on a section containing highly unbalanced data, with \textsc{ir} greater than 9 \citep{fernandez2009hierarchical}.
+From among the available datasets, \oldstylenums{40} were selected presenting only binary problems with quantitative attributes.
 A review of selected datasets, including information on their number of features, the number of patterns in each class and the unbalance ratio is presented in Table 1.
@@
 
-As may be observed after the Table analysis, the experiments will be based on data sets with relatively small spatiality (up to \oldstylenums{13} dimensions), with imbalance ratio from \oldstylenums9 to even \oldstylenums{40}.
+As may be observed in the summary, the experiments are based on datasets with relatively small spatiality (up to \oldstylenums{13} dimensions), with imbalance ratio from \oldstylenums9 to even \oldstylenums{40}.
+The datasets provided by \textsc{keel}, to ensure easy comparison between results presented in various research, are already pre-divided into five parts, which forces the use of \emph{k-fold cross-validation} with $k = 5$ in experiments \citep{alpaydin2009introduction}.
 
-Wykorzystane klasyfikatory bazowe.
-Wyjaśnienie dlaczego odrzuciliśmy MLP (brak konwergencji na bardzo niewielkich zbiorach) i SVC (nie jest on naturalnie probabilistyczny, a jego probabilistyczna interpretacja jest silnie zakłamana przy niewielkich zbiorach danych).
-Stąd bierzemy GNB, kNN i DT, przy domyślnych parametrach z sklearn.
+In the task of imbalanced data classification, due to its strong bias towards majority class, the \emph{accuracy} measure is not a proper tool.
+For a reliable result, a measure of \emph{balanced accuracy} is given as test results.
+
+Both the implementation of the proposed method and the experimental environment have been constructed using the \emph{scikit-learn} library \citep{scikit-learn} in version \emph{0.20.dev0}\footnote{At the time of conducting research, only the development version of the package already has the implementation of \emph{balanced accuracy} measure.}.
+Among the available classification models, the \textsc{mlp} (\emph{Multilayer Perceptron}) and \textsc{svc} (\emph{Support Vector Machine}) were rejected.
+First one was not able to build a correct model due to the lack of convergence on the small datasets (minority class of data chosen for experiments is often represented by only two patterns in cross-validated folds) and second, whose probabilistic interpretation is measurable only with sufficiently large data sets, did not allow credible construction of a fuser.
+As base classifiers, the following algorithms were used:
 
 \begin{itemize}
-	\item \emph{Gaussian Naive Bayes} (\textsc{gnb}) ---
-	\item \emph{k-Nearest Neighbors} (k\textsc{nn}) ---
-	\item \emph{Decision Tree Classifier} (\textsc{dtc}) ---
+	\item \emph{Gaussian Naive Bayes} (\textsc{gnb}) \citep{gnb},
+	\item \emph{k-Nearest Neighbors} (k\textsc{nn}) --- with \oldstylenums{5} neighbors and \emph{Minkowski} metric,
+	\item \emph{Decision Tree Classifier} (\textsc{dtc}) --- with \emph{Gini} criterion \citep{loh2011classification}.
 \end{itemize}
 
-Powównawczo uczenie na pełnym zbiorze i zbiorach po pojedynczym under i oversamplingu.
+To provide a comparative result for the method presented in the following paper, each base classifier was also tested for the raw, imbalanced dataset and its under- and oversampled versions.
+Undersampling, due to high instability of results, was repeated five times on each fold.
+Used statistical analysis tool was a paired dependency between the classifier, which achieved the highest result and each of the others, calculated using the signed-rank \emph{Wilcoxon} test \citep{wilcoxon1945individual}.
 
-Undersampling, ze względu na niestabilność, powtórzony pięciokrotnie na każdym foldzie.
+Pełną implementację zaproponowanej metody i skrypt umożliwiający powtórzenie zaprezentowanych badań można odnaleźć w repozytorium abc.
 
-Zastosowana metoda podziału -- wymuszone przez KEEL k-fold CV (z k=5).
-
-Zastosowana miara jakości -- zbalansowana dokładność, wymierna w niezbalansowanych danych.
-
-Zastosowana analiza statystyczna -- parowa zależność pomiędzy klasyfikatorem z najwyższym rezultatem a pozostałymi w postaci testu Wilcoxona.
-
-Przygotowane oprogramowanie ze wskazaniem repozytorium.
+The full implementation of the proposed method and the script allowing the repetition of the presented research may be found in the git repository available at \url{url-removed-due-to-} \url{blind-review}.
 

### 2018-07-09 article.tex
Tables at the places.

@@
 \begin{abstract}
-This is the abstract for this article.
+pierwsza linia abstraktu\\
+pierwsza linia abstraktu\\
+pierwsza linia abstraktu\\
+pierwsza linia abstraktu\\
+pierwsza linia abstraktu\\
+pierwsza linia abstraktu\\
+pierwsza linia abstraktu\\
+pierwsza linia abstraktu
 \end{abstract}
@@
 
-%Most of the classification algorithms assume that there are no significant disproportions among instances from different classes.
-Nevertheless, in many practical tasks, we may observe that instances from one class (so-called \textit{majority class}) significantly outnumber the objects from remaining classes (\textit{minority class}).
-Most of traditional classifiers have a bias in favor of the majority class although more often the minority class is more interesting, because misidentification of an instance belonging to it is usually much more expensive than assigning an instance from majority class to minority one.
-A good example is an undetected fraud that would be more expensive than the cost of additional analysis of a correct transaction classified as fraudless transaction.
-Such a problem is known as imbalanced data classification \cite{Sun:2009,Wang:2017}, where an unequal number of instances from the examined classes plays a key role during the classifier learning.
-Various approaches have been proposed in the literature to tackle this challenging difficulty embedded in the nature of data.
-Usually, the researchers are focusing on maximizing the correct minority class classification.
-At the same time, performance on the majority class cannot be neglected.
+Most of existing classification models benefit from the assumption that there are no significant disparities between the classes of the considered problem.
+Nevertheless, in the real world, there are many situations in which the number of objects from one of the classes (called the \emph{majority class}) significantly exceeds the number of objects of the remaining classes (\emph{minority classes}), which often leads to decisions biased towards the \emph{majority class}.
+However, when considering cases such as spam filtering, medical tests or fraud detection, we may come to the conclusion that the cost of making an incorrect decision against a minority class is much greater than in other cases.
+The above-mentioned problem in the literature is called the \emph{imbalanced data classification} \citep{Wang:2017,Sun:2009}.
 
-%\begin{figure}[!h]
-%\floatconts
-%  {fig:east}
-%  {\caption{Easy separable imbalance dataset}}
-%  {\includegraphics[clip=true, trim = 11 11 11 11, width=0.25\linewidth]{figures/easy}}
-%\end{figure}
+Following work focuses on the binary classification of the highly imbalanced problems, with an \textsc{ir}(\emph{imbalanced ratio}) greater than \oldstylenums{9}, which is an important issue not only in the context of the construction of appropriate models, but even a proper quality measurement \citep{Elazmeh:2006}.
+One of the important problems is also the fact that the number of patterns in the \emph{minority class} may be so small that it will not allow to achieve the appropriate discriminatory power of the model, which may lead to its \emph{overfitting} \citep{Chen:2008}.
+Most of these problems are the subject of extensive research \citep{Bunkhumpornpat:2009,Chawla:2002}.
 
-%In this project we will focus on binary imbalanced problems, because this setup is the one most frequently studied in the literature and most commonly meet in practical problems, e.g.,\textit{fault detection} or \textit{spam filtering}.
-Therefore, another important issue is proposing an appropriate quality measure that would be adequate for imbalanced data classification \cite{Elazmeh:2006}.
+One of the possible approaches to solve such problems are \emph{inbuild mechanisms}, trying to adapt existing classification models to balance the accuracy between classes.
+Popular here is the learning approach without counter-examples, using \emph{one-class classification} \citep{Japkowicz:1995, Krawczyk:2014ins}, where the aim is to get to know the decision boundaries within minority classes.
+The solution may also be the \emph{cost sensitive solutions}, assuming the asymmetric loss function \citep{Lopez:2012,He:2009}.
 
-%In case of imbalanced data classification the disproportion between the different classes is not the sole issue of learning difficulties.
-One may easily came up with an example where the instance distributions from different classes are well-separated, as depicted in Fig.\ref{fig:easy}.
+Another approach, more connected with the following paper, is the group of \emph{data preprocessing methods}, which focuses on reducing the number of majority class objects (\emph{undersampling}) or generating patterns of minority class (\emph{oversampling}) to balance a dataset.
+Overview of methods from this group is presented in Figure \ref{fig:preproc}.
 
-%Proposing a efficient classifier for such a task is not a challenge.
-Unfortunately, instances from the minority class often form clusters of an unknown structure that are scattered \cite{Napierala:2012}.
-Additional complication comes from the fact that during learning, the number of intactness from the minority class may be not sufficient enough for the learning algorithm to acquire the appropriate generalization level, which in effect can cause \emph{overfitting} \cite{Chen:2008}.
-All those problems are a focus of intense research \cite{Chawla:2002,Bunkhumpornpat:2009,Kubat:1997}.
+\begin{figure}[!h]
+\floatconts
+  {fig:preproc}
+  {\caption{Examples of data preprocessing methods.}}
+  {%
+    \subfigure[Original dataset]{\label{fig:overs}%
+    \includegraphics[clip=true, width=.25\linewidth,
+    				 trim = 11 141 141 11]
+    {figures/preprocessing}}%
+    \qquad
+    \subfigure[\textsc{smote}]{\label{fig:smote}%
+    \includegraphics[clip=true, width=.25\linewidth,
+    				 trim = 141 141 11 11]
+    {figures/preprocessing}}%
 
-%Methods for imbalanced data classification can be divided into three main groups \cite{Lopez:2012}.
+    \subfigure[\textsc{adasyn}]{\label{fig:adasyn}%
+    \includegraphics[clip=true, width=.25\linewidth,
+    				 trim = 11 11 141 141]
+    {figures/preprocessing}}%
+    \qquad
+    \subfigure[Undersampling]{\label{fig:unders}%
+    \includegraphics[clip=true, width=.25\linewidth,
+    				 trim = 141 11 11 141]
+    {figures/preprocessing}}%
+  }
+\end{figure}
 
-%\begin{figure}[!h]
-%\floatconts
-%  {fig:subfigex}
-%  {\caption{Examples of data preprocessing methods.}}
-%  {%
-%    \subfigure[Original dataset]{\label{fig:circle}%
-%    \includegraphics[clip=true, width=.25\linewidth,
-%    				 trim = 11 141 141 11]
-%    {figures/preprocessing}}%
-%    \qquad
-%    \subfigure[\textsc{smote}]{\label{fig:circle}%
-%    \includegraphics[clip=true, width=.25\linewidth,
-%    				 trim = 141 141 11 11]
-%    {figures/preprocessing}}%
+These algorithms are addressing the task of balancing the number of objects within the problem classes.
+In the case of basic \emph{oversampling}, new objects are created as random copies of those already existing in the training set\footnote{Since the characteristics of the new patterns will be identical to those already present in the dataset, we can consider Figure \ref{fig:overs}, an illustration of the original dataset, also as the presentation of pattern distribution after oversampling.}.
+Currently, the most common kind of \emph{oversampling}  is \textsc{smote} \citep{Cha2002}, shown in Figure \ref{fig:smote}, creating new, synthetic objects based on $k$ averaged examples nearest to a random points from the space occupied by a minority class.
+An active version of \textsc{smote} is the \textsc{adasyn} algorithm \citep{He:2008}, shown in Figure \ref{fig:adasyn}, which takes into account the difficulty of synthetic samples.
+This approach allows to solve the problem of repeating samples in the training set, but can also lead to \emph{overfitting}, which is presented in Figure \ref{fig:wrongsmote}.
 
-%    \subfigure[\textsc{adasyn}]{\label{fig:circle}%
-%    \includegraphics[clip=true, width=.25\linewidth,
-%    				 trim = 11 11 141 141]
-%    {figures/preprocessing}}%
-%    \qquad
-%    \subfigure[Undersampling]{\label{fig:circle}%
-%    \includegraphics[clip=true, width=.25\linewidth,
-%    				 trim = 141 11 11 141]
-%    {figures/preprocessing}}%
-%  }
-%\end{figure}
+\begin{figure}[htbp]
+\floatconts
+  {fig:wrongsmote}
+  {\caption{Example of wrong \textsc{smote} oversampling.}}
+  {%
+    \subfigure[Original dataset]{\label{fig:circle}%
+    \includegraphics[clip=true, width=.25\linewidth,
+    				 trim = 11 11 141 11]
+    {figures/wrong_smote}}%
+    \qquad
+    \subfigure[\textsc{smote}]{\label{fig:circle}%
+    \includegraphics[clip=true, width=.25\linewidth,
+    				 trim = 141 11 11 11]
+    {figures/wrong_smote}}%
+  }
+\end{figure}
 
-%\noindent\textbf{ Data preprocessing methods}.
-This approach focuses on reducing the number of objects in majority class (\emph{undersampling}) or generating new objects of the minority class (\textit{oversampling}).
-The difference between \emph{under-} and \emph{oversampling} is presented in Fig.
-\ref{fig:over-under}.
+In the case of \emph{undersampling}, shown in Figure \ref{fig:unders}, in which we draw as many objects from the majority class as in the minority class, there is no risk of erroneous mixing of the distribution of classes.
 
-%These mechanisms have the objective of balancing the quantity of instances from considered classes.
-For oversampling, new instances are random copies of existing ones or are generated in a guided manner.
-The most popular method is \textsc{smote} \cite{Cha2002} algorithm, which creates new instances on a basis of existing ones by slightly modifying the values of their attributes.
-As a result, new artificial examples that are in compliance with the minority class distribution are generated.
-Other oversampling methods are \textsc{adasyn} \cite{He:2008}, in which a difficulty of an object for the classifying model is considered or \textsc{ramob}oost \cite{Chen:2010}.
-Unfortunately, methods such as \textsc{smote} may lead to changes in the characteristic of the minority class and in result to \emph{overfitting} the classifier, what was shown in Fig.
-\ref{fig:wrong_smote}.
-
-%\begin{figure}[htbp]
-%\floatconts
-%  {fig:subfigex}
-%  {\caption{Example of wrong \textsc{smote} oversampling.}}
-%  {%
-%    \subfigure[Original dataset]{\label{fig:circle}%
-%    \includegraphics[clip=true, width=.25\linewidth,
-%    				 trim = 11 11 141 11]
-%    {figures/wrong_smote}}%
-%    \qquad
-%    \subfigure[\textsc{smote}]{\label{fig:circle}%
-%    \includegraphics[clip=true, width=.25\linewidth,
-%    				 trim = 141 11 11 11]
-%    {figures/wrong_smote}}%
-%  }
-%\end{figure}
-
-%W WYPADKU UNDERSAMPLINGU NIE WYSTEPUJE RYZYKO NIESŁUSZNEGO ROZSZERZENIA PRZESTRZENI WZORCÓW KLASY MNIEJSZOŚCIOWEJ, CO MA MIEJSCE W CHOĆBY SMOTE.
-
-%Several modifications of \textsc{smote} have been proposed that are able to identify the instances to be copied in a more intelligent fashion such as \emph{Borderline}\textsc{smote} \cite{Han:2005}.
-It generates new instances from the minority class close to the decision border.
-\emph{Safe-Level} \textsc{smote} \citep{Bunkhumpornpat:2009} and \textsc{ln}-\textsc{smote} \cite{Maciejewski:2011} reduce the probability of generating synthetic instances of the minority class in areas where the predominant objects are that of the majority class.
-It is worth noticing that our team proposed two novel solutions to this problem: \textsc{rbo} \cite{koziarski2017radial} and \textsc{ccr} that enforce instances from the majority-class to be relocated from the areas where the minority-class instances are present \cite{Koziarski:2017amcs}.
-Methods of \emph{undersampling} are built around the idea of randomly removing the instances from the majority-class or removing them from the areas in such way that the  quality of the classifier is not disrupted using neighbor analysis.%\todo{W opisie metod przetwarzania wstępnego skupiamy się chyba wyłącznie na \emph{oversamplingu}.}\todo{Nie uwzględniłem czystego losowego \emph{oversamplingu}, bo skoro powtarza istniejące już obiekty, to ilustracja byłaby bezsensowna.}
-
-%\begin{figure}[hbt]
-%\centering
-%\includegraphics[width=.9\linewidth]{figures/smote}
-%\caption{Example of oversampling using \textsc{smote}}
-%\end{figure}
-
-%\noindent\textbf{ Inbuilt mechanisms.} In this approach existing classification algorithms are adapted for imbalanced problems ensuring balanced accuracy for instances from both classes.
-Two of the most popular areas of research of this methods are using one-class classification  \cite{Japkowicz:1995}, usually known as learning without counterexamples, where the goal is to learn the minority class decision areas and because of the frequently assumed regular, closed shape of the decision borders is adequate to the clusters created by minority classes \cite{Krawczyk:2014ins}.
-The disproportion between the number of instances in classes is then omitted.
-Another approach is the (\textit{cost sensitive}) classification, where the algorithm takes into account the asymmetrical loss function that assigns a higher cost to a misclassification of an instance form a minority class \cite{Krawczyk:2014,Lopez:2012,He:2009,Zhou:2006}.
-Unfortunately such methods can cause a reverse bias towards the minority class.
-
-%Worth noting are methods based on ensemble classification \cite{Wozniak:2014}, like \emph{\textsc{smote}Boost} \cite{Chawla:2003} and \emph{AdaBoost.NC} \cite{Wang:2010}%, or \emph{Multi-objective Genetic Programing Ensemble} \cite{Bhowan:2013}.
-
-%\noindent\textbf{Hybrid methods.} They combine the advantages of methods using data pre-processing with the classification methods.
-The most popular category is the hybridisation of \emph{under-} and \emph{oversampling} with ensemble classifiers \cite{Galar:2012}.
-This approach allows the data to be independently  processed for each of the base model.
-Algorithms formed on modifications of \emph{Bagging} and \emph{Boosting} \cite{Chawla:2003} enjoy wide popularity.
+The last group of methods to be mentioned are \emph{hybrid approaches}, combining \emph{over-} and \emph{undersampling} algorithms with \emph{ensemble classifiers} \citep{Galar:2012}.
+The \emph{Bagging} and \emph{Boosting} variants, such as \emph{AdaBoost.NC} \citep{Wang:2010} or \emph {SMOTEBoost} \citep{Chawla:2003}, have become particularly popular in this area.
 
@@
 \begin{itemize}
-	\item metoda konstrukcji komitetu na k-fold,
-	\item propozycje reguł decyzyjnych,
-	\item metoda pruningu dostosowującego regułę decyzyjną do zbioru testowego
-	\item implementacja i ewaluacja eksperymentalna
+	\item a method of establishing a homogenous ensemble using a \emph{k-fold undersampling} of majority class,
+	\item proposition of five fusers to generate ensemble decision,
+	\item a pruning method adjusting the decision rule to the \emph{testing set},
+	\item implementation and experimental evaluation of proposed method.
 \end{itemize}
 
-\vspace{5em}
 %%%
@@
 \begin{enumerate}
-	\item \textbf{\textsc{reg}} --- regular accumulation of support, without weighing the members of the committee.
-	\item \textbf{\textsc{wei}} --- accumulation weighted after members of the committee.
+	\item \textbf{\textsc{reg}} --- regular accumulation of support.
+
+A basic method without weighing the members of a committee.
+
+	\item \textbf{\textsc{wei}} --- accumulation weighted after members of a committee.
 
@@
 
-Aby premiować klasyfikatory o wyższej mocy dyskryminacyjnej, wagi są poddawane normalizacji standardowej
+To reward classifiers with a higher \emph{discriminative power}, weights are subjected to normalization by a \emph{MinMaxScaler}.
 
-	\item - con akumulacja ważona po wzorcach, przez kontrast,
-	\item - nci iloczyn znormalizowanych wag i kontrastu
-\end{enumerate}
+	\item \textbf{\textsc{con}} --- accumulation weighted by tested patterns.
 
-Wyliczanie wag. Accuracy się nie sprawdzi, więc BAC.
-
-Jeśli klasyfikujemy nie jeden wzorzec, a wiele, wagi mogą być też dla pojedynczych próbek, dla podbicia, a więc pojawia się KONTRAST.
-Mamy takie ładne ilustracje z badań, dodajmy rysunek chociaż jeden poglądowo.
+In order to reward classifiers with greater \emph{"certainty"} for given object, the decision for each pattern is weighted by the absolute difference between class support, for the needs of research called the \emph{contrast}.
+Individual classifiers in the pool do not have to be better or worse for each of the tested patterns.
+This is illustrated in Figure \ref{fig:contrast}, where we can see two cases of ensembles.
+There are tested patterns on the X axis and classifiers in the pool on the Y axis.
+A white square means the \emph{contrast} of 1, and therefore a \emph{sure} decision, and the black square the \emph{contrast} of 0, which describes the pattern that is exactly on the decision boundary.
 
@@
 \floatconts
-  {fig:subfigex}
-  {\caption{Rysunek.}}
+  {fig:contrast}
+  {\caption{Illustration of the \emph{contrast} in committees built on two different datasets.}}
   {%
-    \subfigure[O jaki ładny]{\label{fig:circle}%
+    \subfigure[Example of a \emph{"sure"} ensemble]{\label{fig:circle}%
     \includegraphics[width=.5\linewidth, trim = 0 100 0 100,clip=true]
     {figures/ecoli-0-1_vs_2-3-5}}%
-    \subfigure[A ten brzydki]{\label{fig:circle}%
+    \subfigure[Example of \emph{"unsure"} ensemble]{\label{fig:circle}%
     \includegraphics[width=.5\linewidth, trim = 0 100 0 100,clip=true]
@@
 
-Potencjał kontrastu dla danych strumieniowych.
+	\item \textbf{\textsc{nci}} --- accumulation by a product of normalized weights \textbf{\textsc{nor}} and a \emph{contrast} \textbf{\textsc{con}}.
+\end{enumerate}
 
-Proponowane metody decyzyjne.
-
-W konstrukcji reguły decyzyjnej opieramy się na wsparciu dla klasy pozytywnej.
-
-Duża skala niezbalansowania to duża wielkość komitetu (ilustracja zależności na wykresie). Przyda się więc przycinanie (pruning).
+The proposed method of constructing the committee makes its size directly dependent on the \textsc{ir}, which, given the highly unbalanced data (for example with \textsc{ir} greater than 40), leads to the construction of an extensive hybrid model.
+Therefore, the method of prunning it to a smaller size was also considered.
 
@@
 
-Wyjaśnienie podejścia do pruningu.
-Wyliczamy wzajemną zależność statystyczną (Wilcoxonem) pomiędzy wsparciami członków i grupujemy -- omijając kwestię 1z2 2z3 ale nie 1z3 -- je uśredniając wsparcia w obrębie grupy.
-Uśredniamy też wagi i tworzymy tak dwupoziomowy system fuzji (potrzebna ilustracja).
-
-Pruning też jest w kontekście klasyfikacji wielu wzorców na raz.
-
-Wyjaśnienie kwestii wspomnianej wcześniej i uzasadnienie pominięcia jej analizy.
+In typical methods of \emph{ensemble pruning}, it follows the phase of training the committee, for example, by eliminating the classifiers that achieve the lowest quality on the \emph{training} or separated \emph{validation set}.
+This paper proposes a method of \emph{response pruning} based on the assumption that during the testing phase we analyze not just a single test pattern, but the entire \emph{testing set}.
 
@@
 \floatconts
-  {fig:teximage}
+  {fig:scheme}
   {\caption{Scheme of using k-Fold division in ensemble construction}}
@@
 
+Ensemble, receiving a \emph{testing set}, generates \emph{support vectors} ($s_i$) for each classified object, so, with a binary problem, we can treat received support for one of the problem classes as values from the \emph{random variables} to analyze their mutual statistical dependence.
+
+In the proposed method, using the signed-rank test, we are \emph{clustering} the pool of $k$ (or $k+1$ on the \emph{oversampling} variation of a method) classifiers to $n$ groups (where $n\leq k$), to average the support and weight classes within groups to create a new set of supports from $s'_1$ to $s'_n$, passed later on to \emph{fuser}.
+
+The scheme of the full decision model of the proposed method is shown in Figure \ref{fig:scheme}.
+
+\begin{note}
+In the considered case of pruning, we ignore the possible situation in which the answer $\Psi_1$ is dependent on $\Psi_2$, the answer $\Psi_2$ is dependent on $ \Psi_3$, but $\Psi_1$ is not dependent on $\Psi_3$.
+This is an interesting issue that will be addressed in future research, but to simplify the proposal, a simplified approach has been used.
+\end{note}
+
 %%%
-%%% Introduction
+%%% Experiment design
 %%%
@@
 From among the available datasets, \oldstylenums{40} were selected presenting only binary problems with quantitative attributes.
-A review of selected datasets, including information on their number of features, the number of patterns in each class and the unbalance ratio is presented in Table 1.
+A review of selected datasets, including information on their number of features, the number of patterns in each class and the unbalance ratio is presented in Table \ref{tab:datasets}.
 
 \begin{table}[!h]
-\footnotesize
+%\vspace{-.5em}
+\centering
+\rotatebox{90}{
+\scriptsize
 \centering
 \setlength{\tabcolsep}{3.5pt}
-\def\arraystretch{1}
-\begin{tabular}{@{}|rl|c|ccc|c|}\hline%
+\def\arraystretch{1.1}
+\begin{tabular}{@{}|c|ccc|c|l|@{}}\hline%
 
-\multirow{2}{*}{\bfseries \#} &
-\multirow{2}{*}{\bfseries Dataset} &
+\multirow{2}{*}{\rotatebox[origin=c]{-90}{\bfseries \textsc{ir}}} &
+\multicolumn{3}{c|}{\bfseries Samples} &
 \multirow{2}{*}{\bfseries Features} &
-\multicolumn{3}{c|}{\bfseries Samples} &
-\multirow{2}{*}{\bfseries \textsc{ir}} 	
+\multicolumn{1}{c|}{\multirow{2}{*}{\rotatebox[origin=c]{-90}{\bfseries DS}}}
 \\
 
-& & & 
+&
 \multicolumn{1}{c}{\textsc{all}} & 
@@
 \multicolumn{1}{c|}{\textsc{min}} &
+&
 
@@
 
-	\idx & \multicolumn{1}{l|}{\emph{\dbname}} & \features & 
+	\ir &
 	\multicolumn{1}{c}{\samples} & 
 	\multicolumn{1}{c}{\majority} & 
-	\multicolumn{1}{c|}{\minority} & \ir
+	\multicolumn{1}{c|}{\minority} & 
+	\features & 
+	\multicolumn{1}{l|}{\emph{\dbname}}
 
 	}%
-\end{tabular}
-\caption{Summary of imbalanced datasets chosen for evaluation}
+\end{tabular}}
+\caption{Summary of imbalanced datasets chosen for evaluation}\label{tab:datasets}
 \end{table}
@@
 Used statistical analysis tool was a paired dependency between the classifier, which achieved the highest result and each of the others, calculated using the signed-rank \emph{Wilcoxon} test \citep{wilcoxon1945individual}.
-
-Pełną implementację zaproponowanej metody i skrypt umożliwiający powtórzenie zaprezentowanych badań można odnaleźć w repozytorium abc.
 

### 2018-07-09 figures/ensemble_scheme.tex
Tables at the places.

@@
 
-%\draw[step=.5cm,gray!30!white,very thin] (-4,-13) grid (7,1.5);
+%\draw[step=.5cm,gray!30!white,very thin] (-4,-15) grid (7,1.5);
 
@@
 \node[el] (sk) at (2.5, -9.5) {$s_k$};
-\node[el, minimum width=2cm] (so) at (5, -9.5) {$s_{os}$};
+\node[el, minimum width=2cm, fill=red!15!white] (so) at (5, -9.5) {$s_{os}$};
 \node[text width = 1cm] at (1.65,-9.5)
@@
 
-\node[el, minimum width=7.5cm, minimum height = .5, thick, rounded corners=2mm](fuser) at (2.25,-10.75)
+\node[el, minimum width=7.5cm, minimum height = .5, thick, rounded corners=2mm](pruner) at (2.25,-10.75)
+{\textsc{prunner}};
+
+\node[el] (s_0) at (-1, -12) {$s'_1$};
+\node[el] (s_1) at (.5, -12) {$s'_2$};
+\node[el] (s_n) at (5.5, -12) {$s'_n$};
+\node[text width = 1cm] at (3.15,-12)
+{\bfseries . . .};
+
+\node[el, minimum width=7.5cm, minimum height = .5, thick, rounded corners=2mm](fuser) at (2.25,-13.25)
 {\textsc{fuser}};
 
-\node[el, minimum width=7.5cm](dec) at (2.25,-11.75)
+\node[el, minimum width=7.5cm](dec) at (2.25,-14.25)
 {Decisions};
@@
 \draw[->] (so) -- (5,-10.5);
+
+\draw[->] (-1,-11) -- (s_0);
+\draw[->] (.5,-11) -- (s_1);
+\draw[->] (5.5,-11) -- (s_n);
+
+\draw[->] (s_0) -- (-1,-13);
+\draw[->] (s_1) -- (.5,-13);
+\draw[->] (s_n) -- (5.5,-13);
+
 \draw[->] (fuser) -- (dec);

### 2018-07-09 article.tex
Results.

@@
 	\item \emph{Gaussian Naive Bayes} (\textsc{gnb}) \citep{gnb},
-	\item \emph{k-Nearest Neighbors} (k\textsc{nn}) --- with \oldstylenums{5} neighbors and \emph{Minkowski} metric,
+	%\item \emph{k-Nearest Neighbors} (k\textsc{nn}) --- with \oldstylenums{5} neighbors and \emph{Minkowski} metric,
 	\item \emph{Decision Tree Classifier} (\textsc{dtc}) --- with \emph{Gini} criterion \citep{loh2011classification}.
@@
 
-\begin{sidewaystable}
-	\restable{kNN}{k\textsc{nn}}
-\end{sidewaystable}
+%\begin{sidewaystable}
+%	\restable{kNN}{k\textsc{nn}}
+%\end{sidewaystable}
 
@@
 Tabela zbiorcza zwycięstw w zależności od parametrów (z grupowaniem).
+
+\begin{table}[!h]
+%\vspace{-.5em}
+\centering
+\centering
+\setlength{\tabcolsep}{3.5pt}
+\def\arraystretch{1.1}
+\begin{tabular}{@{}|c|ccc|cc|cc|ccccc|@{}}\hline%
+clf & full & us & os & notos & wos & nopru & wpru & reg & wei & con & nor & nci\\\hline
+
+%\multirow{2}{*}{\rotatebox[origin=c]{-90}{\bfseries \textsc{ir}}} &
+%\multicolumn{3}{c|}{\bfseries Samples} &
+%\multirow{2}{*}{\bfseries Features} &
+%\multicolumn{1}{c|}{\multirow{2}{*}{\rotatebox[origin=c]{-90}{\bfseries DS}}}
+%\\
+
+%&
+%\multicolumn{1}{c}{\textsc{all}} & 
+%\multicolumn{1}{c}{\textsc{maj}} & 
+%\multicolumn{1}{c|}{\textsc{min}} &
+%&
+
+%	\\\hline\hline
+
+	\csvreader[head to column names,
+	           late after line=\csvifoddrow{\\}{\\\rowcolor{gray!10!white}},
+	           late after last line = \\\hline]
+	{results/summary.csv}{}%
+	{\clf &
+	\full & \us & \os &
+	\withoutos & \withos & 
+	\withoutpru & \withpru &
+	\reg & \wei & \con & \nor & \nci
+
+	}%
+\end{tabular}
+\caption{NAZWIJŻE TABELĘ}\label{tab:summary}
+\end{table}
 

### 2018-07-09 process.py

@@ -12,21 +12,21 @@ from imblearn import under_sampling, over_sampling, ensemble
 
 # Prepare experiments
 base_clfs = {
-    #"SVC" : svm.SVC(probability=True, gamma='scale'),
     "GNB" : naive_bayes.GaussianNB(),
-    "kNN" : neighbors.KNeighborsClassifier(),
+    #"kNN" : neighbors.KNeighborsClassifier(),
     "DTC" : tree.DecisionTreeClassifier(),
-    #"MLP" : neural_network.MLPClassifier(),
 }
 datasets = h.datasets_for_groups([
     "imb_IRhigherThan9p1",
     "imb_IRhigherThan9p2",
     #"imb_IRlowerThan9",
 ])
+
 header = ['dataset',
           'reg','regd',
           'us','usd',
           'os','osd',
+
           'ereg','eregd',
           'ewei','eweid',
           'ecwei','ecweid',
@@ -37,6 +37,7 @@ header = ['dataset',
           'ecweir','ecweird',
           'enweir','enweird',
           'encweir','encweird',
+
             'eregos','eregosd',
             'eweios','eweiosd',
             'ecweios','ecweiosd',
@@ -50,9 +51,13 @@ header = ['dataset',
 ]
 versions = 20
 
-for bclf in tqdm(base_clfs):
+summary = np.zeros((len(base_clfs), 23))
+
+for cid, bclf in enumerate(base_clfs):
+    print(cid, bclf)
     base_clf = base_clfs[bclf]
     csvfile = open('results/%s.csv' % bclf, 'w')
+
 
     writer = csv.writer(csvfile, delimiter=',')
     writer.writerow(header)
@@ -139,10 +144,26 @@ for bclf in tqdm(base_clfs):
                 leaders.append(i)
 
         #print(leaders)
+        summary[cid,leaders] += 1
 
         # Establish result row
         foo = [dataset[1].replace("_", "-")]
 
+        for i, bacv in enumerate(bacs):
+            c = ""
+            if i in leaders:
+                c = "\\cellcolor{green!25}"
+            else:
+                c = ""
+
+            if np.mean(bacv) >= 1:
+                foo += ["%s1" % (c)]
+            else:
+                foo += ["%s%s" % (c, ("%.3f" % np.mean(bacv))[1:])]
+            foo += [("%.3f" % np.std(bacv))[1:]]
+
+
+        """
[…]

### 2018-07-28 article.tex
Submitted version

@@
 \title
-[Homogenous ensemble of undersampled majority class]
+[Undersampled Majority Class Ensemble]
 {
-	Homogenous ensemble of undersampled majority class for highly imbalanced data binary classification%\titlebreak
+	\emph{Undersampled Majority Class Ensemble} for highly imbalanced binary classification%\titlebreak
 }
@@
 \begin{abstract}
-pierwsza linia abstraktu\\
-pierwsza linia abstraktu\\
-pierwsza linia abstraktu\\
-pierwsza linia abstraktu\\
-pierwsza linia abstraktu\\
-pierwsza linia abstraktu\\
-pierwsza linia abstraktu\\
-pierwsza linia abstraktu
+Following work tries to utilize an ensemble approach to solve a problem of highly imbalanced data classification.
+Paper contains a proposition of \textsc{umce} -- a multiple classifier system, based on \emph{k-fold division} of the \emph{majority class} to create a pool of classifiers breaking one \emph{imbalanced problem} into many balanced ones while ensuring the presence of all available samples in the training procedure.
+Algorithm, with five proposed fusers and a pruning method based on the statistical dependencies of the classifiers response on the testing set, was evaluated on the basis of the computer experiments carried out on the benchmark datasets and two different base classifiers.
 \end{abstract}
@@
 However, when considering cases such as spam filtering, medical tests or fraud detection, we may come to the conclusion that the cost of making an incorrect decision against a minority class is much greater than in other cases.
-The above-mentioned problem in the literature is called the \emph{imbalanced data classification} \citep{Wang:2017,Sun:2009}.
+The above-mentioned problem is called in the literature the \emph{imbalanced data classification} \citep{Wang:2017,Sun:2009}.
 
-Following work focuses on the binary classification of the highly imbalanced problems, with an \textsc{ir}(\emph{imbalanced ratio}) greater than \oldstylenums{9}, which is an important issue not only in the context of the construction of appropriate models, but even a proper quality measurement \citep{Elazmeh:2006}.
+Following work focuses on the binary classification of the highly imbalanced problems, with an \textsc{ir}(\emph{imbalanced ratio}) greater than \oldstylenums{9}, which is an important issue not only in the context of the construction of appropriate models, but even in a proper quality measurement \citep{Elazmeh:2006}.
 One of the important problems is also the fact that the number of patterns in the \emph{minority class} may be so small that it will not allow to achieve the appropriate discriminatory power of the model, which may lead to its \emph{overfitting} \citep{Chen:2008}.
@@
 One of the possible approaches to solve such problems are \emph{inbuild mechanisms}, trying to adapt existing classification models to balance the accuracy between classes.
-Popular here is the learning approach without counter-examples, using \emph{one-class classification} \citep{Japkowicz:1995, Krawczyk:2014ins}, where the aim is to get to know the decision boundaries within minority classes.
-The solution may also be the \emph{cost sensitive solutions}, assuming the asymmetric loss function \citep{Lopez:2012,He:2009}.
+Popular solution of this kind is the learning approach without counter-examples, using \emph{one-class classification} \citep{Japkowicz:1995, Krawczyk:2014ins}, where the aim is to get to know the decision boundaries within \emph{minority classes}.
+The solution may also be the \emph{cost sensitive solutions}, assuming the asymmetric \emph{loss function} \citep{Lopez:2012,He:2009}.
 
-Another approach, more connected with the following paper, is the group of \emph{data preprocessing methods}, which focuses on reducing the number of majority class objects (\emph{undersampling}) or generating patterns of minority class (\emph{oversampling}) to balance a dataset.
-Overview of methods from this group is presented in Figure \ref{fig:preproc}.
+Another approach, more connected with the scope of following paper, is the group of \emph{data preprocessing methods}, which focuses on reducing the number of \emph{majority class} objects (\emph{undersampling}) or generating patterns of \emph{minority class} (\emph{oversampling}) to balance a dataset.
+Graphical overview of methods from this group is presented in Figure \ref{fig:preproc}.
 
@@
 
-In the case of \emph{undersampling}, shown in Figure \ref{fig:unders}, in which we draw as many objects from the majority class as in the minority class, there is no risk of erroneous mixing of the distribution of classes.
+In the case of \emph{undersampling}, shown in Figure \ref{fig:unders}, in which we draw as many objects from the majority class as are present in the minority class, there is no risk of erroneous mixing of the classes distribution.
 
-The last group of methods to be mentioned are \emph{hybrid approaches}, combining \emph{over-} and \emph{undersampling} algorithms with \emph{ensemble classifiers} \citep{Galar:2012}.
+The last group of methods to be mentioned here are \emph{hybrid approaches}, combining \emph{over-} and \emph{undersampling} algorithms with \emph{ensemble classifiers} \citep{Galar:2012}.
 The \emph{Bagging} and \emph{Boosting} variants, such as \emph{AdaBoost.NC} \citep{Wang:2010} or \emph {SMOTEBoost} \citep{Chawla:2003}, have become particularly popular in this area.
@@
 \begin{itemize}
-	\item a method of establishing a homogenous ensemble using a \emph{k-fold undersampling} of majority class,
-	\item proposition of five fusers to generate ensemble decision,
-	\item a pruning method adjusting the decision rule to the \emph{testing set},
+	\item a method of establishing a homogenous \emph{ensemble} using a \emph{k-fold undersampling} of \emph{majority class},
+	\item proposition of five \emph{fusers} to generate \emph{ensemble} decision,
+	\item a \emph{pruning} method adjusting the decision rule to the \emph{testing set},
 	\item implementation and experimental evaluation of proposed method.
@@
 %%%
-\section{Homogenous ensemble based on undersampling the majority class}
+\section{\emph{Undersampled Majority Class Ensemble}}
 \label{sec:intro}
@@
 
-Complex oversampling methods, such as \textsc{smote} or \textsc{adasyn}, despite the large possibilities in most of the imbalanced problems, are not applicable to extreme situations where the minority class is represented by only a few samples, which makes it impossible to designate the nearest neighbors to create a new synthetic object.
+Complex oversampling methods, such as \textsc{smote} or \textsc{adasyn}, despite the large possibilities in most of the problems in imbalanced domain, are not applicable to extreme situations where the \emph{minority class} is represented by only a few samples, which makes it impossible to designate the nearest neighbors to create a new synthetic object.
 This could lead to the use of \emph{undersampling} in such problems, but it is characterized, due to high randomness, by a strong instability in a situation of high \textsc{ir} (\emph{imbalance ratio}), which does not allow for the development of a reliable solution.
 
-A popular answer to the above-mentioned problem are the ensemble methods of \emph{Bagging} or \emph{Boosting}, characterized by random sampling with replacement of the training set, breaking a large problem, into a set of smaller problems.
+A popular answer to the above-mentioned problem are the \emph{ensemble} methods of \emph{Bagging} or \emph{Boosting}, characterized by random sampling with replacement of the training set, breaking a large problem, into a set of smaller ones.
 This work proposes a basic method, which also breaks the imbalanced task, but with ensuring the use of all the patterns available in the data set, but without a risk of overlapping.
-Its description can be found in Algorithm 1.
+Its description may be found in Algorithm 1.
 
@@
 It is worth testing if the knowledge gained from this method may be a valuable contribution to the ensemble decision.
-Due to impossibility to use \textsc{smote} or \textsc{adasyn} for oversampling the minority class with only few instances, only its basic variant will be used.
+Due to impossibility of using \textsc{smote} or \textsc{adasyn} for oversampling the minority class with only few instances, only its basic variant will be employed.
 
@@
 The weight of the classifier in the pool is its quality achieved for the training set.
-We can not use here the measure of \emph{accuracy}, which does not fit with the task of the imbalanced classification, so we decided on a \emph{balanced accuracy} \citep{brodersen2010balanced}.
+We can not use here the measure of \emph{accuracy}, which does not fit with the task of the imbalanced classification, so a \emph{balanced accuracy} was chosen \citep{brodersen2010balanced}.
 
@@
 
-In typical methods of \emph{ensemble pruning}, it follows the phase of training the committee, for example, by eliminating the classifiers that achieve the lowest quality on the \emph{training} or separated \emph{validation set}.
+Typical methods of \emph{ensemble pruning} follow the phase of training the committee, for example, by eliminating the classifiers that achieve the lowest quality on the \emph{training} or separated \emph{validation set}.
 This paper proposes a method of \emph{response pruning} based on the assumption that during the testing phase we analyze not just a single test pattern, but the entire \emph{testing set}.
@@
   {fig:scheme}
-  {\caption{Scheme of using k-Fold division in ensemble construction}}
+  {\caption{Diagram of \emph{Undersampled Majority Class Ensemble} structure}}
   {\input{figures/ensemble_scheme}}
@@
 Among the available classification models, the \textsc{mlp} (\emph{Multilayer Perceptron}) and \textsc{svc} (\emph{Support Vector Machine}) were rejected.
-First one was not able to build a correct model due to the lack of convergence on the small datasets (minority class of data chosen for experiments is often represented by only two patterns in cross-validated folds) and second, whose probabilistic interpretation is measurable only with sufficiently large data sets, did not allow credible construction of a fuser.
+First one was not able to build a correct model due to the lack of convergence on the small datasets (minority class of data chosen for experiments is often represented by only two patterns in cross-validated folds) and second one, whose probabilistic interpretation is measurable only with sufficiently large data sets, did not allow credible construction of a fuser.
 As base classifiers, the following algorithms were used:
@@
 
-Przedstawienie tabel.
+The results of the conducted research, for individual base classifiers, are presented in Tables 2 and 3.
+They were divided to present in individual sections a \emph{balanced accuracy} achieved by particular variations of the method proposed in the following paper.
+In the first division stage, we show the impact of inclusion of the classifier built on the \emph{oversampled} dataset, in the second, the use of the proposed pruning method, and in the third -- employed \emph{fuser}.
+This gave 20 variations of the algorithm.
+
+The presented results were supplemented by a balanced accuracy achieved by the classifier built on a full, \emph{imbalanced dataset} (\textbf{Full}), a set after \emph{undersampling} (\textbf{US}) and an \emph{oversampling} (\textbf{OS}).
+The table cells marked in green indicate the best result for a dataset or the result statistically dependent on it, calculated in accordance with previously described assumptions of the experiments.
 
@@
 
-Tabela zbiorcza zwycięstw w zależności od parametrów (z grupowaniem).
+As we can see in Table 2, which presents the quality of classification using the \textsc{gnb} algorithm, there were only two datasets, where the lone best solution was to train the model on a full, imbalanced dataset, and one where the best solution were simple \emph{over-} or \emph{undersampling}.
+In the Table 3, showing the results for the \textsc{dtc} classifier, we are dealing with a similar situation in which, however, \emph{undersampling} never turns out to be the best in the tested pool of solutions.
+
+A clearer interpretation of the results may take place after the analysis of the Table 4, showing a summary of the results achieved by individual variations of the proposed method, presenting the number of datasets for which a given variation took part in the construction of the best solution.
 
@@
 \def\arraystretch{1.1}
-\begin{tabular}{@{}|c|ccc|cc|cc|ccccc|@{}}\hline%
-clf & full & us & os & notos & wos & nopru & wpru & reg & wei & con & nor & nci\\\hline
+\begin{tabular}{@{}|l|ccc||cc|cc|ccccc|@{}}\hline%
 
-%\multirow{2}{*}{\rotatebox[origin=c]{-90}{\bfseries \textsc{ir}}} &
-%\multicolumn{3}{c|}{\bfseries Samples} &
-%\multirow{2}{*}{\bfseries Features} &
-%\multicolumn{1}{c|}{\multirow{2}{*}{\rotatebox[origin=c]{-90}{\bfseries DS}}}
-%\\
+\multirow{2}{*}{\bfseries Classifier} & 
+\multirow{2}{*}{\bfseries Full} & 
+\multirow{2}{*}{\bfseries US} & 
+\multirow{2}{*}{\bfseries OS} &
 
-%&
-%\multicolumn{1}{c}{\textsc{all}} & 
-%\multicolumn{1}{c}{\textsc{maj}} & 
-%\multicolumn{1}{c|}{\textsc{min}} &
-%&
-
-%	\\\hline\hline
+\multicolumn{2}{c|}{\bfseries OSE} &
+\multicolumn{2}{c|}{\bfseries Pru.} &
+\multicolumn{5}{c|}{\bfseries Fuser} 
+%notos & wos & nopru & wpru & reg & wei & con & nor & nci
+ \\
+ &&&&
+ \textsc{no} & \textsc{yes} &
+ \textsc{no} & \textsc{yes} &
+ \textsc{reg} & \textsc{wei} & \textsc{con} & \textsc{nor} & \textsc{nci}
+ \\\hline\hline
 
@@
 \end{tabular}
-\caption{NAZWIJŻE TABELĘ}\label{tab:summary}
+\caption{Final summary of proposed method variations. %Values in cells are numbers of datasets, in which method reached the best score, or have been statistically dependent to the best score. 
+\\\emph{(OSE -- extending pool by oversampled dataset, Pru. -- usage of pruning)}}\label{tab:summary}
+\vspace{-2em}
 \end{table}
 
-Interpretacja wyników, czyli co zostało należycie uprawdopodobnione.
+As we may observe, both the extension of the classifier pool by the model built on the oversampled dataset as well as the proposed pruning method has a positive impact on the quality of the final solution.
+Among the fusers, the best performers are \textsc{nor} -- normalizing the calculated weights for the members of the committee and \textsc{nci} - complementing \textsc{nor} by the accumulated support with a stronger impact of the certainty of the decision.
+Even just the basic ensemble construction, in its simplest form without improvements and using the decision rule without weighting, allows to achieve better results than learning on a full dataset or basic under- or oversampling.
 
@@
 \label{sec:intro}
-Co zostało zaproponowane.
 
-Na co pozwala taka metoda.
+This paper presents \textsc{umce} (\emph{Undersampled Majority Class Ensemble}) -- a hybrid method for solving the problem of binary classification of datasets with a high \emph{imbalance ratio}, based on \emph{k-fold division} of the \emph{majority class} samples to create an \emph{ensemble} of classifiers breaking one \emph{imbalanced problem} into many balanced problems.
+The basic division method has been supplemented with a variant extending the pool with the \emph{oversampled} dataset and the \emph{post-pruning} method based on the analysis of the statistical dependencies of the classifiers response on the testing set.
+For the \emph{ensemble} it were also proposed five different \emph{fusers}.
 
-Do jakich rezultatów doprowadziła.
-
-Jakie są plany na przyszłość (czyli co robisz w wakacje).
+Computer experiments have shown, that this approach led to create a method solving targeted problem and able to outperform other possible basic solutions, proving that it may be employed for real-life appliance.
 
@@
 \acks{
-	Acknowledgements go here.
+	---\\
+	---\\
+	---
+	%This work was supported by the Polish National Science Center under the grant no.
+UMO- 2015/19/B/ST6/01597 and by the statutory fund of the Faculty of Electronics, Wroclaw University of Science and Technology.
 }

### 2018-07-28 paper/article.tex
Clean-up

--- 2018-07-28 article.tex
@@
 	           late after last line = \\\hline]
-	{results/datasets.csv}{}%
+	{datasets.csv}{}%
 	{
@@
 
-The full implementation of the proposed method and the script allowing the repetition of the presented research may be found in the git repository available at \url{url-removed-due-to-} \url{blind-review}.
+The full implementation of the proposed method, content of the following paper and the script allowing the repetition of the presented research may be found in the git repository\footnote{\url{https://github.com/w4k2/umce}}.
 
@@
 	           late after last line = \\\hline]
-	{results/summary.csv}{}%
+	{summary.csv}{}%
 	{\clf &

### 2018-07-28 analyze.py
Summary.

@@ -18,11 +18,10 @@ header = [
 ]
 datasets = h.datasets_for_groups([
     "imb_IRhigherThan9p1",
-    "imb_IRhigherThan9p2",
-    #"imb_IRlowerThan9",
+    "imb_IRhigherThan9p2"
 ])
 
-csvfile = open('results/datasets.csv', 'w')
+csvfile = open('csv/datasets.csv', 'w')
 writer = csv.writer(csvfile, delimiter=',')
 writer.writerow(header)
 

### 2018-07-28 method.py

@@ -93,12 +93,6 @@ class UndersampledEnsemble():
         self.nrweights = scaler.fit_transform(self.rweights.reshape(-1,1)).T[0]
         self.nrweights += .01
 
-        #print("Weights")
-        #print(self.weights)
-        #print(self.nweights)
-        #print(self.rweights)
-        #print(self.nrweights)
-
         # Contrasts
         self.contrast = np.abs(self.esc[:,:,0] - self.esc[:,:,1])
         self.rcontrast = np.abs(self.resc[:,:,0] - self.resc[:,:,1])

### 2018-07-28 process.py

@@ -13,20 +13,17 @@ from imblearn import under_sampling, over_sampling, ensemble
 # Prepare experiments
 base_clfs = {
     "GNB" : naive_bayes.GaussianNB(),
-    #"kNN" : neighbors.KNeighborsClassifier(),
     "DTC" : tree.DecisionTreeClassifier(),
 }
 datasets = h.datasets_for_groups([
     "imb_IRhigherThan9p1",
-    "imb_IRhigherThan9p2",
-    #"imb_IRlowerThan9",
+    "imb_IRhigherThan9p2"
 ])
 
 header = ['dataset',
           'reg','regd',
           'us','usd',
           'os','osd',
-
           'ereg','eregd',
           'ewei','eweid',
           'ecwei','ecweid',
@@ -37,17 +34,16 @@ header = ['dataset',
           'ecweir','ecweird',
           'enweir','enweird',
           'encweir','encweird',
-
-            'eregos','eregosd',
-            'eweios','eweiosd',
-            'ecweios','ecweiosd',
-            'enweios','enweiosd',
-            'encweios','encweiosd',
-            'eregros','eregrosd',
-            'eweiros','eweirosd',
-            'ecweiros','ecweirosd',
-            'enweiros','enweirosd',
-            'encweiros','encweirosd'
+          'eregos','eregosd',
+          'eweios','eweiosd',
+          'ecweios','ecweiosd',
+          'enweios','enweiosd',
+          'encweios','encweiosd',
+          'eregros','eregrosd',
+          'eweiros','eweirosd',
+          'ecweiros','ecweirosd',
+          'enweiros','enweirosd',
+          'encweiros','encweirosd'
 ]
 versions = 20
 
@@ -56,20 +52,16 @@ summary = np.zeros((len(base_clfs), 23))
 for cid, bclf in enumerate(base_clfs):
     print(cid, bclf)
     base_clf = base_clfs[bclf]
-    csvfile = open('results/%s.csv' % bclf, 'w')
+    csvfile = open('csv/%s.csv' % bclf, 'w')
 
 
     writer = csv.writer(csvfile, delimiter=',')
     writer.writerow(header)
     for dataset in tqdm(datasets):
-        #print(dataset)
         # Load dataset
         X, y, X_, y_ = h.load_dataset(dataset)
 
         # Prepare place for results
-        #r_bac = []
-        #os_bac = []
-        #us_bac = []
         bacs = [[] for i in range(versions+3)]
 
         # Iterate folds
[…]

### 2018-07-28 paper/article.tex
Summary.
Corrections.

@@
 \input{_head}
-%TODO: Max 14 pages
-%TODO: No personal information or reference to the authors should be introduced in the submitted paper.
-%TODO: Submissions will be evaluated concerning their technical quality, relevance, significance, originality and clarity.
 
@@
 
-Following work focuses on the binary classification of the highly imbalanced problems, with an \textsc{ir}(\emph{imbalanced ratio}) greater than \oldstylenums{9}, which is an important issue not only in the context of the construction of appropriate models, but even in a proper quality measurement \citep{Elazmeh:2006}.
+Following work focuses on the binary classification of the highly imbalanced problems, with an \textsc{ir} (\emph{imbalanced ratio}) greater than \oldstylenums{9}, which is an important issue not only in the context of the construction of appropriate models, but even in a proper quality measurement \citep{Elazmeh:2006}.
 One of the important problems is also the fact that the number of patterns in the \emph{minority class} may be so small that it will not allow to achieve the appropriate discriminatory power of the model, which may lead to its \emph{overfitting} \citep{Chen:2008}.
@@
   {%
-    \subfigure[Original dataset]{\label{fig:overs}%
+    \subfigure[Original dataset / Oversampling]{\label{fig:overs}%
     \includegraphics[clip=true, width=.25\linewidth,
@@
 
-\paragraph{Extending pool with oversampling} As an extension of the method of classifier ensemble construction, it is also proposed to extend its pool by a model learned on an additional data set, which is a full set of data subjected to \emph{oversampling}.
+\paragraph{Extending pool with oversampling} As an extension of the method of classifier ensemble construction, it is also proposed to expand its pool by a model learned on an additional data set, which is a full set of data subjected to \emph{oversampling}.
 It is worth testing if the knowledge gained from this method may be a valuable contribution to the ensemble decision.
@@
 The decision rules proposed in this work are, however, part of the second group, where the \emph{fuser} is carried out by \emph{averaging} (or \emph{accumulating}) the \emph{support vectors} received from the members of a pool.
+It should be remembered that in such methods, it is necessary to use a \emph{probabilistic classification model}, which also requires \emph{quantitative} and not \emph{qualitative data}, so we need to reject classification algorithms such as \emph{Support Vector Machines}, whose probabilistic interpretation becomes reliable only in cases of large training sets.
 
-\begin{note}
-It should be remembered that in such methods, it is necessary to use a \emph{probabilistic classification model}, which also requires \emph{quantitative} and not \emph{qualitative data}.
-\end{note}
-
-Five fusers were proposed:
+Five accumulative fusers were proposed to analyze:
 
@@
 This is illustrated in Figure \ref{fig:contrast}, where we can see two cases of ensembles.
-There are tested patterns on the X axis and classifiers in the pool on the Y axis.
+There are tested patterns on the \emph{X} axis and classifiers in the pool on the \emph{Y} axis.
 A white square means the \emph{contrast} of 1, and therefore a \emph{sure} decision, and the black square the \emph{contrast} of 0, which describes the pattern that is exactly on the decision boundary.
@@
 
-	\item \textbf{\textsc{nci}} --- accumulation by a product of normalized weights \textbf{\textsc{nor}} and a \emph{contrast} \textbf{\textsc{con}}.
+	\item \textbf{\textsc{nci}} --- accumulation weighted by a product of normalized weights and a \emph{contrast}.
 \end{enumerate}
 
-The proposed method of constructing the committee makes its size directly dependent on the \textsc{ir}, which, given the highly unbalanced data (for example with \textsc{ir} greater than 40), leads to the construction of an extensive hybrid model.
+The proposed method of constructing the committee makes its size directly dependent on the \textsc{ir}, which, given the highly unbalanced data (for example with \textsc{ir} greater than \oldstylenums{40}), leads to the construction of an extensive hybrid model.
 Therefore, the method of prunning it to a smaller size was also considered.
@@
 In the proposed method, using the signed-rank test, we are \emph{clustering} the pool of $k$ (or $k+1$ on the \emph{oversampling} variation of a method) classifiers to $n$ groups (where $n\leq k$), to average the support and weight classes within groups to create a new set of supports from $s'_1$ to $s'_n$, passed later on to \emph{fuser}.
+It is important to denote, that in the considered case of pruning, we ignore the possible situation in which the answer $\Psi_1$ is dependent on $\Psi_2$, the answer $\Psi_2$ is dependent on $ \Psi_3$, but $\Psi_1$ is not dependent on $\Psi_3$.
+This is an interesting issue that will be addressed in future research, but to clarify the proposal, a simplified approach has been used.
 
 The scheme of the full decision model of the proposed method is shown in Figure \ref{fig:scheme}.
-
-\begin{note}
-In the considered case of pruning, we ignore the possible situation in which the answer $\Psi_1$ is dependent on $\Psi_2$, the answer $\Psi_2$ is dependent on $ \Psi_3$, but $\Psi_1$ is not dependent on $\Psi_3$.
-This is an interesting issue that will be addressed in future research, but to simplify the proposal, a simplified approach has been used.
-\end{note}
 
@@
 
-For the experimental evaluation of the proposed method, a collection of datasets made available with \textsc{keel} \citep{alcala2011keel} was used, focusing on a section containing highly unbalanced data, with \textsc{ir} greater than 9 \citep{fernandez2009hierarchical}.
-From among the available datasets, \oldstylenums{40} were selected presenting only binary problems with quantitative attributes.
-A review of selected datasets, including information on their number of features, the number of patterns in each class and the unbalance ratio is presented in Table \ref{tab:datasets}.
+For the experimental evaluation of the proposed method, a collection of datasets made available with \textsc{keel} \citep{alcala2011keel} was used, focusing on a section containing highly unbalanced data, with \textsc{ir} greater than \oldstylenums{9} \citep{fernandez2009hierarchical}.
+From among the available datasets, \oldstylenums{40} were selected, presenting only binary problems with quantitative attributes.
+A review of selected datasets, including information on their number of features, the number of patterns in each class and the imbalance ratio is presented in Table \ref{tab:datasets}.
 
@@
 As may be observed in the summary, the experiments are based on datasets with relatively small spatiality (up to \oldstylenums{13} dimensions), with imbalance ratio from \oldstylenums9 to even \oldstylenums{40}.
-The datasets provided by \textsc{keel}, to ensure easy comparison between results presented in various research, are already pre-divided into five parts, which forces the use of \emph{k-fold cross-validation} with $k = 5$ in experiments \citep{alpaydin2009introduction}.
+The datasets provided by \textsc{keel}, to ensure easy comparison between results presented in various research, are already pre-divided into five parts, which forces the use of \emph{k-fold cross-validation} with \oldstylenums{5} folds in experiments \citep{alpaydin2009introduction}.
 
@@
 
-To provide a comparative result for the method presented in the following paper, each base classifier was also tested for the raw, imbalanced dataset and its under- and oversampled versions.
+To provide a comparative result for the method presented in the following paper, each base classifier was also tested for (\emph{i}) the raw, imbalanced dataset and its (\emph{ii}) under- and (\emph{iii}) oversampled versions.
 Undersampling, due to high instability of results, was repeated five times on each fold.
@@
 
-The full implementation of the proposed method, content of the following paper and the script allowing the repetition of the presented research may be found in the git repository\footnote{\url{https://github.com/w4k2/umce}}.
+The full implementation of the proposed method, content of the following paper and the script allowing to reconstruct the presented research may be found in the \emph{git} repository\footnote{\url{https://github.com/w4k2/umce}}.
 
@@
 
-The results of the conducted research, for individual base classifiers, are presented in Tables 2 and 3.
+The results of the conducted research, for individual base classifiers, are presented in Tables \ref{tab:GNB} and \ref{tab:DTC}.
 They were divided to present in individual sections a \emph{balanced accuracy} achieved by particular variations of the method proposed in the following paper.
-In the first division stage, we show the impact of inclusion of the classifier built on the \emph{oversampled} dataset, in the second, the use of the proposed pruning method, and in the third -- employed \emph{fuser}.
-This gave 20 variations of the algorithm.
+In the first division stage, we show the impact of inclusion of the classifier built on the \emph{oversampled} dataset, in the second, the use of the proposed \emph{pruning} method, and in the third -- employed \emph{fuser}.
+It gave the number of \oldstylenums{20} algorithm variations.
 
@@
 
-%\begin{sidewaystable}
-%	\restable{kNN}{k\textsc{nn}}
-%\end{sidewaystable}
-
 \begin{sidewaystable}
@@
 
-As we can see in Table 2, which presents the quality of classification using the \textsc{gnb} algorithm, there were only two datasets, where the lone best solution was to train the model on a full, imbalanced dataset, and one where the best solution were simple \emph{over-} or \emph{undersampling}.
-In the Table 3, showing the results for the \textsc{dtc} classifier, we are dealing with a similar situation in which, however, \emph{undersampling} never turns out to be the best in the tested pool of solutions.
+As we can see in Table \ref{tab:GNB}, which presents the quality of classification using the \textsc{gnb} algorithm, there were only two datasets, where the lone best solution was to train the model on a full, imbalanced dataset, and one where the best solution were simple \emph{over-} or \emph{undersampling}.
+In the Table \ref{tab:DTC}, showing the results for the \textsc{dtc} classifier, we are dealing with a similar situation in which, however, \emph{undersampling} never turns out to be the best in the tested pool of solutions.
 
-A clearer interpretation of the results may take place after the analysis of the Table 4, showing a summary of the results achieved by individual variations of the proposed method, presenting the number of datasets for which a given variation took part in the construction of the best solution.
+A clearer interpretation of the results may take place after the analysis of the Table \ref{tab:summary}, showing a summary of the results achieved by individual variations of the proposed method, presenting the number of datasets for which a given variation took part in the construction of the best solution.
 
 \begin{table}[!h]
-%\vspace{-.5em}
+
 \centering
@@
 	\reg & \wei & \con & \nor & \nci
+	}%
 
-	}%
 \end{tabular}
@@
 \\\emph{(OSE -- extending pool by oversampled dataset, Pru. -- usage of pruning)}}\label{tab:summary}
-\vspace{-2em}
+\label{tab:summary}
 \end{table}
@@
 \acks{
-	---\\
-	---\\
-	---
-	%This work was supported by the Polish National Science Center under the grant no.
+	This work was supported by the Polish National Science Center under the grant no.
 UMO- 2015/19/B/ST6/01597 and by the statutory fund of the Faculty of Electronics, Wroclaw University of Science and Technology.
